### 2016-11-16 rapport/paper.tex
Add files via upload

\documentclass[journal]{IEEEtran}
\usepackage{blindtext}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{graphicx}%
\usepackage{url}%
\usepackage{abstract}%
\usepackage{csquotes}
\usepackage{amsthm}
\usepackage{amssymb}

\hyphenation{op-tical net-works semi-conduc-tor}

\usepackage[backend=biber]{biblatex}%
\bibliography{biblio}% The name of your .bib file

\begin{document}
%
% paper titlesdsd
% can use linebreaks \\ within to get better formatting as desired
\title{Damage localization based on vibrations}

\author{Benjamin Fasquelle, Nicolas Pompidor and Jimmy Rogala}

\newtheorem{remark}{Remark}

% The paper headers
%\markboth{Project}{}

% make the title area
\maketitle

\begin{abstract}
abstract
\end{abstract}

\begin{IEEEkeywords}
Damage, Localization, Vibration, Health monitoring
\end{IEEEkeywords}

\IEEEpeerreviewmaketitle

\section{Introduction}

The process of implementing a damage identification strategy for aerospace,
 civil and mechanical engineering infrastructure is referred as a structural health monitoring (SHM) \cite{farrar2007introduction}.

In the most general terms, damage can be defined as changes in one system that negatively affect its current or future performance. 
In addition, a damage can only be observed by comparing two different states of the system,
 one of which is supposed to represent the initial state, and often undamaged, state.

Almost all industries want to detect damage in their infrastructure as quickly as possible whether 
 for the potential life-safety or economic impact.
Such detectetion requires these industries to perform some form of SHM.

Clearly, such damage identification has significant life-safety implications.
For instance, there are  no quantifiable methods to
 determine if buildings should be repaired after an earthquake yet.
SHM may one day provide the technology that can be used to significantly minimize
 the uncertainty associated with such post-earthquake damage assessments.
Thus additional catastrophes could be avoided.

Generally, the damage identification can be divided into four levels:
\begin{itemize}
\item detection: Is the structure damaged or not?
\item localization: Where is the damaged area located?
\item quantification: What is the extent of damage?
\item prediction: What is the remaining service life of the structure?
\end{itemize}
\vspace{2mm}

Traditional methods of damage detection based on visual inspections or experimental techniques such as radiography
 or ultrasound allow to obtain detailed information about a local damage state but requires to know area where it is located (and hope for easy access). 
These techniques may be costly, taking a long time to be performed and impractical to detect damage in large urban areas.
 Furthermore, they may fail if damage is not visibly evident. This is why other methods were invented.

(! A changer ? !) ->

The purpose of this work is the analysis of a particular data-driven damage localization method,
 namely the FRF interpolation method, and the development of a statistical extension of this method.
This paper is organized as follows. In section II we  present the existing methods (model-based and data driven methods), 
then in section III we detail the different models of vibrating structures and finally, in section IV we talk about the localization using FRF interpolation method and, finally,  its results in section V.

\section{State of the art}

The use of methods based on recorded responses proved to perform as valuable alternatives. 
The general idea for vibration-based damage identification is that the damage affects the physical properties (mass, damping, and stiffness) of the structure. 
And this will cause detectable changes in modal properties (natural frequencies, modal damping, and mode shapes). 
For instance, cracks cause reductions in stiffness. Therefore, by analyzing the physical properties of the structure a damage can be detected.
\\

Most of the different vibration based damage identification methods can be classified as data-driven or model-based.
 The model-based method assumes that a detailed numerical model of the structure is available for damage identification and, by vibration measurements, updates the model parameters.
 On another side, data-driven methods is based solely on the recorded response. This method is interesting for a real-time damage identification but unavailability of a numerical model often hinders the estimation of damage severity.
 A third group includes data-driven methods that use finite element (FE) information without model updating.

\subsection{Model-based methods}

In model-based methods, damage is identified through the updating of a finite element (FE) model.
 Most of the time, modal characteristics is the experimental data used for damage assessment through FE model updating.% which are extracted from measured response time histories using modal analysis techniques.
 Different types of modal data can be used. For changes in structural stiffness, model updating can be performed based only on natural frequencies or eigenvalues which are known to change in this case.
 Detailed informations about model-based methods can be found in references  %rajouter celles en-dessous
% C.-P. Fritzen, D. Jennewein, T. Kiefer, (1998). Damage detection based on model updating methods, Mechanical Systems and Signal Processing, 12(1): 163–186.
\cite{fritzen1998damage}
% Teughels A. and G. De Roeck. (2005). Damage detection and parameter identification by finite element model updating. Archives of Computational Methods in Engineering, 12(2):123-164.
\cite{teughels2005damage}
% Simoen E., De Roeck G., and Lombaert G. (2015). Dealing with uncertainty in model updating for damage assessment: a review. Mechanical Systems and Signal Processing, 56-57:123-149.
\cite{simoen2015dealing}

A REFORMULER EN DESSOUS

\subsection{Data driven methods}

Data driven method are inverse methods that use models based on experimental response data recorded on the structure instead of physical models
\cite{limongelli2016towards}.
 In these methods, the damage parameter $D$ is the variation of the damage feature $d$ between the inspection $I$ and the reference $R$ configurations: %Damage-sensitive features are extracted from data and their changes used to identify damage in the structures so the damage parameter D in these method is the variation of the damage feature f between the inspection I and the reference R configurations.
% référence TOWARDS EXTRACTION OF VIBRATION-BASED DAMAGE INDICATORS
% nom pdf : fact sheet template_vibration based_final.pdf

\begin{equation}
D=d_{I} - d_{R}
\end{equation}

Data-driven methods do not require a FE model  and may be applied with a limited number of available signals (both responses and excitations), making it an interesting method.
To extract the damage features, different signal-processing tools can be used. Therefore, depending on the tool,  data-driven methods can be classified in Fourier-based methods, Time series method and Time-variant methods.
A more detailed description of this methods can be found in references %rajouter celles en-dessous
% Fassois S.D. and Sakellariou J.S. (2007) Time-series methods for fault detection and identification in vibrating structures. Phil. Trans. R. Soc. A. 365, 411–448. doi:10.1098/rsta.2006.1929.
\cite{fassois2007time}
% Staszewski W. J.and Robertson A.N. (2007). Time–frequency and time–scale analyses for structural health monitoring. Phil. Trans. R. Soc. A. 365, 449–477. doi:10.1098/rsta.2006.1936.
\cite{staszewski2007time}.

\subsection{Combined data-driven and model-based methods}

A third group of methods for damage localization and quantification lies between the data-driven and model-based approaches.
 "This class is based on datadriven features from measurements of the reference and damaged states, which are confronted to a FE model of the structure to define damage indicators for the elements of the FE model,
 without updating its parameters" \cite{limongelli2016towards}. %rajouter référence au papier
% référence TOWARDS EXTRACTION OF VIBRATION-BASED DAMAGE INDICATORS
% nom pdf : fact sheet template_vibration based_final.pdf
% Maria Pina Limongelli, Eleni Chatzi, Michael D¨ohler, Geert Lombaert, Edwin Reynders
% https://hal.inria.fr/hal-01344178/document

\section{Models of vibrating structures}% or Physical models

\subsection{Finite element model}

The dynamic behaviour of a mechanical system consisting of $n$ masses connected
through springs and dampers is described by following matrix differential equation:
\begin{equation}
M \ddot{q}(t) + C \dot{q}(t) + K q(t) = f(t)
\label{fondamental}
\end{equation}
where $q(t)$ is the displacement vector at a continous time $t$, and $M, C, K \in \mathbb{R}^{n \times n}$, are the mass, damping and stiffness matrices.

For civil engineering structures, Equation (\ref{fondamental}) is obtained as the finite element approximation of the system with only $n$ dregrees of freedom.
The structure is divided in elements, and the global mass matrix $M$ and stiffness matrix $K$ are generated from the geometry and material
properties of the elements.
Due to the lack of identifiable or measurable material
constants that govern the global damping behaviour of a structure, it is generally
impossible to assemble the damping matrix C in the same way as M and K.

\subsection{Continous-time state-space model} %(model parameters and reduction):

From the Equation (\ref{fondamental}) and with the variable change $x =
\begin{pmatrix}
\dot{q} \\
q
\end{pmatrix}$, we obtain the state equation:
\begin{equation}
\dot{x}(t) = A_cx(t) + B_cf(t)
\end{equation}
 where
$A_c =
\begin{pmatrix}
0 & I \\
M^{-1}K & M^{-1}C
\end{pmatrix}$
and
$B_c=
\begin{pmatrix}
0 \\
M^{-1}
\end{pmatrix}$

In a practical vibration experiment, not all $n$ degrees of freedom of the structure are measured, but only
a subset. The observation equation is:
\begin{equation}
y(t) = C_cx(t) + D_cf(t)
\end{equation}

If it is assumed that all $n$ degrees of freedom are measured and that the sensors are accelerometers transducers, we have
$C_c =
\begin{pmatrix}
M^{-1}K & M^{-1}C
\end{pmatrix}$
and
$D_c=
\begin{pmatrix}
M^{-1}
\end{pmatrix}$

Thus, the classical continuous-time state-space model is:
\begin{equation}
\left\{
\begin{array}{ll}
\dot{x}(t) = A_cx(t) + B_cf(t) \\
y(t) = C_cx(t) + D_cf(t)
\end{array}
\right.
\end{equation}

\subsection{Discrete-time state-space model} %(impulses response)

Up to now all equations were expressed in continuous time, whereas in reality
measurements are taken at discrete time instants.
So this model need to be converted to discrete time.
Another reason is that it is needed for performing simulations.

Thus, we choose a certain fixed sampling period $\Delta t$, and the continuous-time equations are discretized and solved at all
discrete time instants $k$ with $t = k \Delta t, k \in \mathbb{N}$.

The discrete-time state-space model is:
\begin{equation}
\left\{
\begin{array}{ll}
x_{k+1} & = Ax_k + Bf_k \\
y_k & = Cx_k + Bf_k
\end{array}
\right.
\label{discrete}
\end{equation}
where
\begin{equation}
\begin{array}{ll}
A = exp(A_c \Delta t) \\
B= (A - I) A^{-1}_c B_c \\
C = C_c \\
D = D_c
\end{array}
\end{equation}

%Stockastic state-space models
%ARMA models
%Continuous time frequency-domain models
%Discrete time frequency-domain models

\section{Localization using FRF interpolation method}

This method is presented in \cite{dilena2015damage}.
The main hypothesis underlying the method is that a concentrated damage reflects in a loss of spatial regularity of the
vibrational profile of a structure, compared with the reference (undamaged) state.

In this section, we suppose that we have $n$ sensors, which are located along an axis $z$, and we denote them by
$\{z_l\}, l\in \{1 ... n\}$. We also suppose we have $N$ measures for each sensor.

For each sensor, we calculate the Frequency Response Function (FRF) from the acceleration's measures, at certain frequencies 
(which are $\frac{k}{N}, k \in \{0 ... N-1\}$).

Thus, for each frequency and each sensor, we have the transfer function value. Let us denote $H_R(z_l,f_i)$ the value of the transfer function for  the sensor $z_l$ at the frequency $f_i$.

Then, we calculate for each sensor $z_l$ the cubic polynomial spline interpolation of the transfer functions $H_R(z_k,f_i)$ measured at all 
the other instrumented locations $\{z_k\}, k\in \{1 ... n\}, k \neq l$: we denote it $H_S(z_l,f_i)$.

For these two transfer functions, we define the interpolation error $E(z_l,f_i)$ as the absolute value of the difference between recorded and interpolated FRFs:
\begin{equation}
E(z_l,f_i) = | H_R(z_l,f_i) - H_S(z_l,f_i) |
\end{equation}

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{images/interpolation.png}
  \caption{Interpolation error, from \cite{dilena2015damage}}
  \label{interpolation_error}
\end{figure}

Since we want to characterize each location $z_l$ with a scalar-valued error index, we introduce the norm of the error on the whole range of
frequencies:
\begin{equation}
E(z_l) = \sqrt{  \sum\limits_{i=1}^N  E^2(z_l,f_i) }
\label{error}
\end{equation}

Transfer function values obviously depend on the state of the structure. Hence, if the estimation of the error function
through Equation (\ref{error}) is repeated in the baseline (undamaged) and in the inspection (possibly damaged) configuration, then the
difference between the two values, denoted respectively by $E_0(z_l)$ and $E_d(z_l)$, can provide an indication about the existence of
degradation at location $z_l$:
\begin{equation}
\Delta E(z_l) = E_d(z_l) - E_0(z_l)
\end{equation}

An increase in the interpolation error between the reference configuration and the current configuration at a station $z_l$ , i.e.
$ \Delta E(z_l) > 0$, highlights a localized reduction of smoothness in the vibrational amplitude profile and, therefore, it is assumed
to be a symptom of a local variation of stiffness at $z_l$ associated with the occurrence of damage.

The above analysis has been developed in a deterministic context. Several sources, such as temperature, nonlinear
behavior, soil structure interaction and noise in recorded data, can induce variations of the interpolation error even if no
damage occurs.

Thus, once have to determine a threshold $E_T$, such as $ \Delta E(z_l)$ must be taller than $E_T$ to have a high probability of identification of a damage at location $z_l$. Indeed, as we can see in the Figure (\ref{proba}), the curves which represent the fact to have a damage or not have a share area: if the interpolation error $ \Delta E(z_l)$ is in this area, one can commit two errors:
\begin{itemize}
\item if it is in the area $P_f(z_l)$ under the graph of $p_{E,0}(z_l)$, once can detect a damage since there isn't one (false alarm).
\item if it is in the area $P_m(z_l)$ under the graph of $p_{E,d}(z_l)$, once can not detect a damage since there is one (missing alarm).
\end{itemize}

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{images/gaussiennes.png}
  \caption{Probabilities of false and missing alarm, from \cite{dilena2015damage}}
  \label{proba}
\end{figure}

\section{Simulation}

\subsection{Obtaining acceleration measures}

We have implemented a simulation to check this method of localization. We made this on the following system: $n$ masses, connected
through springs and dampers. We denote the masses $\{m_i\}_{i=1}^n$, the springs stifness $\{k_i\}_{i=1}^n$ and the dampers $\{c_i\}_{i=1}^n$ (see Figure (\ref{springs})).

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{images/ressorts.png}
  \caption{Masses connected through springs and dampers}
  \label{springs}
\end{figure}

For the simulation, we use the discrete-time state-space model (Equation (\ref{discrete})). First, we needed the matrices $M, C, K$. In this case, the matrices $M$ and $K$ are given by:
\begin{equation}
\begin{array}{l}
M = 
\begin{pmatrix} 
m_1\\ 
&\ddots\\ 
&&m_n
\end{pmatrix} 
\\
K = 
\begin{pmatrix} 
k_1 + k_2 & - k_1 \\ 
- k_1 &\ddots\\ 
& -k_i & k_i + k_{i+1} & -k_{i+1} \\
&&&\ddots& -k_n\\
&&& -k_n & k_n
\end{pmatrix} 
\end{array}
\end{equation}

As we have seen earlier, the damping matrix can't be determined by measures.
Thus, we do the same thing that in practical situations: we consider that we are in the case of Rayleigh damping: the damping 
matrix is a linear combination of the mass and stiffness matrix:
\begin{equation}
C = \alpha M + \beta K,\ \ \ \ \ \alpha, \beta \in \mathbb{R}_+
\end{equation}

With this matrices, we can calculate the matrices $A_c, B_c, C_c$ and $D_c$. To calculate the matrices $A, B$, we have to know the 
sampling period $\Delta t$. We need the frequencies of the system, because we have to respect the Nyquist–Shannon sampling theorem.
To determine the Nyquist frequency (here, it is the taller frequency of the system), we calculate the eigenvalues of $A_c$. Indeed, we have the link between the eigenvalues $\{\lambda_i\}_{i=1}^n$ and the frequencies of the system $\{f_i\}_{i=1}^n$:
\begin{equation}
\lambda_i = - \omega_i \xi_i \pm i \omega_i \sqrt{1 - \xi_i^2}
\end{equation}
where $\omega_i = 2 \pi f_i$ and $\xi_i$ is the damping ratio.

\begin{remark}
We can see that:\\
$|\lambda_i| = \sqrt{\omega_i^2 \xi_i^2 + \omega_i^2 (1 - \xi_i^2)} = \omega_i$
\end{remark}

\begin{remark}
The matrix $A_c$ has $2 \times n$ eigenvalues, but we obtain $n$ frequencies (each of them appears two times). 
\end{remark}

Now, we have the sampling period:
\begin{equation}
\Delta t = 2 \times max_{i \in \{1 ... n\} } f_i
\end{equation}

So we can calculate the matrices $A, B$ and make the simulation with the discrete-time state-space model (Equation (\ref{discrete})). To simulate the forces $f_k$, we use a white noise.

\subsection{Frequency Response Function}

The FRF correspond to the transfer function of the system. In frequency domain, if $F$ is the force that is apply on the system and $S$ is the response of this force, the FRF is given by:
\begin{equation}
H = \frac{S}{F}
\end{equation}

We want to calculate the FRF of the system, for each sensor localization. Here, we calculate an estimation of the FRF, called $H_1$ estimator. We suppose we have a vector of the forces $\{ f_k\}_{k=1}^N$ and a vector of the accelerations $\{ y_k\}_{k=1}^N$ for each sensor (the two vectors are size $N$). We need to be in frequency domain, so we calculate the discrete Fourier transform:
\begin{equation}
\begin{array}{ll}
F_n = \sum\limits_{k=1}^N f_k e^{-2i\pi kn/N} \ \ \ \ \ n \in \{1 ... N\} \\
Y_n = \sum\limits_{k=1}^N y_k e^{-2i\pi kn/N} \ \ \ \ \ n \in \{1 ... N\}
\end{array}
\end{equation}

Then we calculate the power spectra, i.e. the Auto Power spectra of the inputs and the outputs
and the Cross Power spectra between the inputs and outputs respectively given by:

\begin{equation}
\begin{array}{ll}
S_{ff}(n) = F_n F_n^H \ \ \ \ \ n \in \{1 ... N\} \\
S_{yf}(n) = Y_n F_n^H \ \ \ \ \ n \in \{1 ... N\}
\end{array}
\end{equation}
where $M^H$ is the Hermitian of the matrix $M$. Thus, the FRF is given by:
\begin{equation}
H_1(n) = S_{yf}(n) S_{ff}(n)^{-1}
\end{equation}

\begin{remark}
If we consider each sensor separately, $F_n$ and $Y_n$ are scalars, so we have:
\begin{equation}
\begin{array}{lll}
H_1(n) & = & S_{yf}(n) S_{ff}(n)^{-1} \\
& = & Y_n F_n^H (F_n F_n^H)^{-1} \\
& = & Y_n / F_n
\end{array}
\end{equation}
\end{remark}

\subsection{Interpolation}

\subsection{Result}

\section{Conclusion}

%\appendices
%\section{One appendix}
%some text for the appendix.

% use section* for acknowledgement
%\section*{Acknowledgment}
%The authors would like to thank...

%\begin{thebibliography}{1}
%
%\bibitem{IEEEhowto:kopka}
%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
%
%\end{thebibliography}

\nocite{*}
\printbibliography

\end{document}

### 2016-11-16 rapport/paper_v0.tex
Add files via upload

--- 2016-11-16 rapport/paper.tex
@@
 %
-% paper titlesdsd
+% paper title
 % can use linebreaks \\ within to get better formatting as desired
@@
 \author{Benjamin Fasquelle, Nicolas Pompidor and Jimmy Rogala}
-
-\newtheorem{remark}{Remark}
 
@@
 
-The process of implementing a damage identification strategy for aerospace,
- civil and mechanical engineering infrastructure is referred as a structural health monitoring (SHM) \cite{farrar2007introduction}.
-
-In the most general terms, damage can be defined as changes in one system that negatively affect its current or future performance. 
-In addition, a damage can only be observed by comparing two different states of the system,
- one of which is supposed to represent the initial state, and often undamaged, state.
-
-Almost all industries want to detect damage in their infrastructure as quickly as possible whether 
- for the potential life-safety or economic impact.
-Such detectetion requires these industries to perform some form of SHM.
-
-Clearly, such damage identification has significant life-safety implications.
-For instance, there are  no quantifiable methods to
- determine if buildings should be repaired after an earthquake yet.
-SHM may one day provide the technology that can be used to significantly minimize
- the uncertainty associated with such post-earthquake damage assessments.
-Thus additional catastrophes could be avoided.
-
-Generally, the damage identification can be divided into four levels:
+There are four levels for damage identification:
 \begin{itemize}
@@
 \end{itemize}
-\vspace{2mm}
-
-Traditional methods of damage detection based on visual inspections or experimental techniques such as radiography
- or ultrasound allow to obtain detailed information about a local damage state but requires to know area where it is located (and hope for easy access). 
-These techniques may be costly, taking a long time to be performed and impractical to detect damage in large urban areas.
- Furthermore, they may fail if damage is not visibly evident. This is why other methods were invented.
-
-(! A changer ? !) ->
-
-The purpose of this work is the analysis of a particular data-driven damage localization method,
- namely the FRF interpolation method, and the development of a statistical extension of this method.
-This paper is organized as follows. In section II we  present the existing methods (model-based and data driven methods), 
-then in section III we detail the different models of vibrating structures and finally, in section IV we talk about the localization using FRF interpolation method and, finally,  its results in section V.
 
 \section{State of the art}
-
-The use of methods based on recorded responses proved to perform as valuable alternatives. 
-The general idea for vibration-based damage identification is that the damage affects the physical properties (mass, damping, and stiffness) of the structure. 
-And this will cause detectable changes in modal properties (natural frequencies, modal damping, and mode shapes). 
-For instance, cracks cause reductions in stiffness. Therefore, by analyzing the physical properties of the structure a damage can be detected.
-\\
-
-Most of the different vibration based damage identification methods can be classified as data-driven or model-based.
- The model-based method assumes that a detailed numerical model of the structure is available for damage identification and, by vibration measurements, updates the model parameters.
- On another side, data-driven methods is based solely on the recorded response.
-This method is interesting for a real-time damage identification but unavailability of a numerical model often hinders the estimation of damage severity.
- A third group includes data-driven methods that use finite element (FE) information without model updating.
-
-\subsection{Model-based methods}
-
-In model-based methods, damage is identified through the updating of a finite element (FE) model.
- Most of the time, modal characteristics is the experimental data used for damage assessment through FE model updating.% which are extracted from measured response time histories using modal analysis techniques.
- Different types of modal data can be used.
-For changes in structural stiffness, model updating can be performed based only on natural frequencies or eigenvalues which are known to change in this case.
- Detailed informations about model-based methods can be found in references  %rajouter celles en-dessous
-% C.-P. Fritzen, D. Jennewein, T. Kiefer, (1998). Damage detection based on model updating methods, Mechanical Systems and Signal Processing, 12(1): 163–186.
-\cite{fritzen1998damage}
-% Teughels A. and G. De Roeck. (2005). Damage detection and parameter identification by finite element model updating. Archives of Computational Methods in Engineering, 12(2):123-164.
-\cite{teughels2005damage}
-% Simoen E., De Roeck G., and Lombaert G. (2015). Dealing with uncertainty in model updating for damage assessment: a review. Mechanical Systems and Signal Processing, 56-57:123-149.
-\cite{simoen2015dealing}
-
-A REFORMULER EN DESSOUS
-
-\subsection{Data driven methods}
-
-Data driven method are inverse methods that use models based on experimental response data recorded on the structure instead of physical models
-\cite{limongelli2016towards}.
- In these methods, the damage parameter $D$ is the variation of the damage feature $d$ between the inspection $I$ and the reference $R$ configurations: %Damage-sensitive features are extracted from data and their changes used to identify damage in the structures so the damage parameter D in these method is the variation of the damage feature f between the inspection I and the reference R configurations.
-% référence TOWARDS EXTRACTION OF VIBRATION-BASED DAMAGE INDICATORS
-% nom pdf : fact sheet template_vibration based_final.pdf
-
-\begin{equation}
-D=d_{I} - d_{R}
-\end{equation}
-
-Data-driven methods do not require a FE model  and may be applied with a limited number of available signals (both responses and excitations), making it an interesting method.
-To extract the damage features, different signal-processing tools can be used.
-Therefore, depending on the tool,  data-driven methods can be classified in Fourier-based methods, Time series method and Time-variant methods.
-A more detailed description of this methods can be found in references %rajouter celles en-dessous
-% Fassois S.D. and Sakellariou J.S. (2007) Time-series methods for fault detection and identification in vibrating structures. Phil. Trans. R. Soc. A. 365, 411–448. doi:10.1098/rsta.2006.1929.
-\cite{fassois2007time}
-% Staszewski W. J.and Robertson A.N. (2007). Time–frequency and time–scale analyses for structural health monitoring. Phil. Trans. R. Soc. A. 365, 449–477. doi:10.1098/rsta.2006.1936.
-\cite{staszewski2007time}.
-
-\subsection{Combined data-driven and model-based methods}
-
-A third group of methods for damage localization and quantification lies between the data-driven and model-based approaches.
- "This class is based on datadriven features from measurements of the reference and damaged states, which are confronted to a FE model of the structure to define damage indicators for the elements of the FE model,
- without updating its parameters" \cite{limongelli2016towards}. %rajouter référence au papier
-% référence TOWARDS EXTRACTION OF VIBRATION-BASED DAMAGE INDICATORS
-% nom pdf : fact sheet template_vibration based_final.pdf
-% Maria Pina Limongelli, Eleni Chatzi, Michael D¨ohler, Geert Lombaert, Edwin Reynders
-% https://hal.inria.fr/hal-01344178/document
 
@@
 
-The discrete-time state-space model is:
+The discret-time state-space model is:
 \begin{equation}
@@
 \right.
-\label{discrete}
 \end{equation}
@@
 
-\subsection{Obtaining acceleration measures}
-
-We have implemented a simulation to check this method of localization. We made this on the following system: $n$ masses, connected
-through springs and dampers. We denote the masses $\{m_i\}_{i=1}^n$, the springs stifness $\{k_i\}_{i=1}^n$ and the dampers $\{c_i\}_{i=1}^n$ (see Figure (\ref{springs})).
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.4\textwidth]{images/ressorts.png}
-  \caption{Masses connected through springs and dampers}
-  \label{springs}
-\end{figure}
-
-For the simulation, we use the discrete-time state-space model (Equation (\ref{discrete})). First, we needed the matrices $M, C, K$. In this case, the matrices $M$ and $K$ are given by:
-\begin{equation}
-\begin{array}{l}
-M = 
-\begin{pmatrix} 
-m_1\\ 
-&\ddots\\ 
-&&m_n
-\end{pmatrix} 
-\\
-K = 
-\begin{pmatrix} 
-k_1 + k_2 & - k_1 \\ 
-- k_1 &\ddots\\ 
-& -k_i & k_i + k_{i+1} & -k_{i+1} \\
-&&&\ddots& -k_n\\
-&&& -k_n & k_n
-\end{pmatrix} 
-\end{array}
-\end{equation}
-
-As we have seen earlier, the damping matrix can't be determined by measures.
-Thus, we do the same thing that in practical situations: we consider that we are in the case of Rayleigh damping: the damping 
-matrix is a linear combination of the mass and stiffness matrix:
-\begin{equation}
-C = \alpha M + \beta K,\ \ \ \ \ \alpha, \beta \in \mathbb{R}_+
-\end{equation}
-
-With this matrices, we can calculate the matrices $A_c, B_c, C_c$ and $D_c$. To calculate the matrices $A, B$, we have to know the 
-sampling period $\Delta t$. We need the frequencies of the system, because we have to respect the Nyquist–Shannon sampling theorem.
-To determine the Nyquist frequency (here, it is the taller frequency of the system), we calculate the eigenvalues of $A_c$.
-Indeed, we have the link between the eigenvalues $\{\lambda_i\}_{i=1}^n$ and the frequencies of the system $\{f_i\}_{i=1}^n$:
-\begin{equation}
-\lambda_i = - \omega_i \xi_i \pm i \omega_i \sqrt{1 - \xi_i^2}
-\end{equation}
-where $\omega_i = 2 \pi f_i$ and $\xi_i$ is the damping ratio.
-
-\begin{remark}
-We can see that:\\
-$|\lambda_i| = \sqrt{\omega_i^2 \xi_i^2 + \omega_i^2 (1 - \xi_i^2)} = \omega_i$
-\end{remark}
-
-\begin{remark}
-The matrix $A_c$ has $2 \times n$ eigenvalues, but we obtain $n$ frequencies (each of them appears two times). 
-\end{remark}
-
-Now, we have the sampling period:
-\begin{equation}
-\Delta t = 2 \times max_{i \in \{1 ... n\} } f_i
-\end{equation}
-
-So we can calculate the matrices $A, B$ and make the simulation with the discrete-time state-space model (Equation (\ref{discrete})). To simulate the forces $f_k$, we use a white noise.
-
-\subsection{Frequency Response Function}
-
-The FRF correspond to the transfer function of the system. In frequency domain, if $F$ is the force that is apply on the system and $S$ is the response of this force, the FRF is given by:
-\begin{equation}
-H = \frac{S}{F}
-\end{equation}
-
-We want to calculate the FRF of the system, for each sensor localization.
-Here, we calculate an estimation of the FRF, called $H_1$ estimator.
-We suppose we have a vector of the forces $\{ f_k\}_{k=1}^N$ and a vector of the accelerations $\{ y_k\}_{k=1}^N$ for each sensor (the two vectors are size $N$).
-We need to be in frequency domain, so we calculate the discrete Fourier transform:
-\begin{equation}
-\begin{array}{ll}
-F_n = \sum\limits_{k=1}^N f_k e^{-2i\pi kn/N} \ \ \ \ \ n \in \{1 ... N\} \\
-Y_n = \sum\limits_{k=1}^N y_k e^{-2i\pi kn/N} \ \ \ \ \ n \in \{1 ... N\}
-\end{array}
-\end{equation}
-
-Then we calculate the power spectra, i.e. the Auto Power spectra of the inputs and the outputs
-and the Cross Power spectra between the inputs and outputs respectively given by:
-
-\begin{equation}
-\begin{array}{ll}
-S_{ff}(n) = F_n F_n^H \ \ \ \ \ n \in \{1 ... N\} \\
-S_{yf}(n) = Y_n F_n^H \ \ \ \ \ n \in \{1 ... N\}
-\end{array}
-\end{equation}
-where $M^H$ is the Hermitian of the matrix $M$. Thus, the FRF is given by:
-\begin{equation}
-H_1(n) = S_{yf}(n) S_{ff}(n)^{-1}
-\end{equation}
-
-\begin{remark}
-If we consider each sensor separately, $F_n$ and $Y_n$ are scalars, so we have:
-\begin{equation}
-\begin{array}{lll}
-H_1(n) & = & S_{yf}(n) S_{ff}(n)^{-1} \\
-& = & Y_n F_n^H (F_n F_n^H)^{-1} \\
-& = & Y_n / F_n
-\end{array}
-\end{equation}
-\end{remark}
-
-\subsection{Interpolation}
-
-\subsection{Result}
+%Thus, we consider that we are in the case of Rayleigh damping: the damping 
+%matrix is a linear combination of the mass and stiffness matrix:
 

### 2016-11-16 simu_one_sensor.py

@@ -1,0 +1,306 @@
+################################################
+############# import ###########################
+################################################
+
+
+
+import numpy as np
+import math
+import cmath
+import scipy.linalg
+from scipy.stats import norm
+
+
+################################################
+############# functions ########################
+################################################
+
+
+
+def matrix_M(mass):#make the mass matrix
+	return np.diag(mass)
+
+def matrix_K(stiffness):#make the stiffness matrix
+	n = len(stiffness)
+	K = np.diag(stiffness)
+	for i in range(n-1):
+		K[i][i] += stiffness[i+1]
+		K[i+1][i] = stiffness[i+1]
+		K[i][i+1] = stiffness[i+1]
+	return K
+
+def matrix_C(M,K,a,b):#make the C matrix
+	return a*M + b*K
+
+
+def write_F(forces):
+	f = open("F.txt",'w')
+	for m in forces:
+		p = 0#power
+		if (m > 0):
+			f.write(" ")
+			nb = 9
+		else:
+			nb = 10
+		if abs(m) > 0.1:
+			while( abs(m) > 10 ):
+				m /= 10
+				p += 1
+			f.write( "  " + str(m)[:nb] + "e+0" + str(p) + '\n')
+		elif m == 0:
+			f.write( "  " + "0.0000000" + "e+0" + str(p) + '\n')
+		else:
+			while( abs(m) < 0.1 ):
+				m *= 10
+				p += 1
+			f.write( "  " + str(m)[:nb] + "e-0" + str(p) + '\n')
+	f.close()
+
+
+
+
+def write_Y(measures):
+	f = open("Y.txt",'w')
+	for acc in measures:
+		for m in acc:
+			p = 0#power
+			if (m > 0):
+				f.write(" ")
+				nb = 9
+			else:
+				nb = 10
+			if abs(m) > 0.1:
+				while( abs(m) > 10 ):
+					m /= 10
+					p += 1
+				f.write( "  " + str(m)[:nb] + "e+0" + str(p) + '\t')
+			elif m == 0:
+				f.write( "   " + "0.0000000" + "e+0" + str(p) + '\t')
+			else:
+				while( abs(m) < 0.1 ):
+					m *= 10
+					p += 1
[…]

### 2016-11-28 exp.py
maj experience

@@ -7,7 +7,7 @@ import numpy
 
 def printRef(ref,inf,sup):
     n = len(ref)
-    delta = 1
+    delta = 3
     plt.ion()
     for i in range(n):
     	if (i%50 == 0):
@@ -19,7 +19,7 @@ def printRef(ref,inf,sup):
 
 def printAll(ref,inf,sup,undamaged, damaged):
     n = len(ref)
-    delta = 1
+    delta = 3
     plt.ion()
     for i in range(n):
     	if (i%50 == 0):

### 2016-11-28 interpolation.py

@@ -114,11 +114,11 @@ def create_ref(frf_list_ref):
 	for i in range(nb_frf):
 		for j in range(nb_sensor):
 			for k in range(nb_freq):
-				frf_average[k][j] += frf_list_ref[i][j][k]
+				frf_average[k][j] = frf_average[k][j] + frf_list_ref[i][j][k]
 	
-	for x in frf_average:
-		for y in x:
-			y /= 10
+	for i in range(nb_freq):
+		for j in range(nb_sensor):
+			frf_average[i][j] =  frf_average[i][j] / nb_frf
 	
 	std_dev = [ [0 for i in range(nb_sensor) ] for k in range(nb_freq) ]
 	for i in range(nb_frf):
@@ -126,9 +126,9 @@ def create_ref(frf_list_ref):
 			for k in range(nb_freq):
 				std_dev[k][j] += (frf_list_ref[i][j][k] - frf_average[k][j])**2
 				
-	for x in std_dev:
-		for y in x:
-			y /= 10
+	for i in range(nb_freq):
+		for j in range(nb_sensor):
+			std_dev[i][j] =  std_dev[i][j] / nb_frf
 	
 	frf_inf = [ [0 for i in range(nb_sensor) ] for k in range(nb_freq) ]
 	frf_sup = [ [0 for i in range(nb_sensor) ] for k in range(nb_freq) ]

### 2016-11-28 main.py

@@ -94,12 +94,17 @@ def frf_multiple_capter_simu_ref(inFile=None, fichier_sampl = "f_sampl_ref.txt")
     #acc, measures, f_sampl = simu.simulation(pos,mass,stiffness,forces,1,"F_ref.txt","Y_ref.txt", fichier_sampl)
     
     #donnes de la simu
-    forces = parser.get("F_ref.txt")[:]
-    measures = parser.get("Y_ref.txt")[:]
+    #forces = parser.get("F_ref.txt")[:]
+    #measures = parser.get("Y_ref.txt")[:]
     #
     res = []
     for i in range(10):
-    	m = measures[i*10000:(i+1)*10000]
+    	#m = measures[i*10000:(i+1)*10000]
+    	#simu: a activer seulement si on veut de nouvelles donnees
+    	forces = simu.white_noise(10000,CAPTVALUE)
+    	acc, m, f_sampl = simu.simulation(pos,mass,stiffness,forces,1,"F_ref.txt","Y_ref.txt", fichier_sampl)
+    	
+    	
     	frf_sensor = [ [] for k in range(CAPTVALUE) ]
     	for j in range(CAPTVALUE):
     	    frf_sensor[j] = (frf.frf(tool.get_lines(forces,j),tool.get_lines(m,j)))

### 2016-11-28 simu.py

@@ -215,6 +215,7 @@ def simulation(pos,mass,stiffness,f, col, fichier_forces, fichier_acc, fichier_s
 	"""
 	
 	acc = [ [0 for k in range(2*n) ] ]
+	
 	measures = []
 	
 	for i in range(N):
@@ -260,7 +261,6 @@ def white_noise(n,nb_sensor):
 	for i in range(n):
 		noise += [ norm.rvs(size=nb_sensor, loc = mean, scale = standard_deviation) ]
 	return noise
-
 
 
 #print( norm.rvs(loc = mean, scale = standard_deviation, size = 5) )

### 2016-11-29 rapport/paper.tex
rapport

@@
 \begin{abstract}
-abstract
+%The surveillance of a structure, as a bridge, with a human presence is something we want automate.
+%A damage identification strategy  is referred as a structural health monitoring (SHM).
+%The SHM can be divided into four levels: detection, localization, quantification and prediction.
+%We present the existing methods for the detection and the localization of damage, then we detail one of them, namely the Frequency Response Function interpolating method.
+%We also analyse this method with a simulation of a spring–mass system.
 \end{abstract}
@@
 
-In the most general terms, damage can be defined as changes in one system that negatively affect its current or future performance. 
-In addition, a damage can only be observed by comparing two different states of the system,
- one of which is supposed to represent the initial state, and often undamaged, state.
+In the most general terms, damage can be defined as changes in a system that negatively affect its current or future performance. 
+In general, a damage can be observed by comparing two different states of the system,
+ one of which is supposed to represent the initial often undamaged state.
 
@@
  for the potential life-safety or economic impact.
-Such detectetion requires these industries to perform some form of SHM.
+Such detection requires these industries to perform some form of SHM.
 
@@
 
-Generally, the damage identification can be divided into four levels:
+Generally, the damage identification can be divided into four levels \cite{peeters2000system}:
 \begin{itemize}
@@
 These techniques may be costly, taking a long time to be performed and impractical to detect damage in large urban areas.
- Furthermore, they may fail if damage is not visibly evident. This is why other methods were invented.
-
-(! A changer ? !) ->
+ Furthermore, they may fail if damage is not visibly evident. This is why other global methods were developed that are automated
+ and based on sensor measurements.
 
 The purpose of this work is the analysis of a particular data-driven damage localization method,
- namely the FRF interpolation method, and the development of a statistical extension of this method.
+ namely the FRF interpolation method \cite{dilena2015damage}, and the development of a statistical extension of this method.
 This paper is organized as follows. In section II we  present the existing methods (model-based and data driven methods), 
@@
 The use of methods based on recorded responses proved to perform as valuable alternatives. 
-The general idea for vibration-based damage identification is that the damage affects the physical properties (mass, damping, and stiffness) of the structure. 
-And this will cause detectable changes in modal properties (natural frequencies, modal damping, and mode shapes). 
+The general idea for vibration-based damage identification is that the damage affects the physical properties (mass, damping, and stiffness) of the structure, and this will cause detectable changes in modal properties (natural frequencies, modal damping, and mode shapes).
 For instance, cracks cause reductions in stiffness. Therefore, by analyzing the physical properties of the structure a damage can be detected.
@@
 Most of the different vibration based damage identification methods can be classified as data-driven or model-based.
- The model-based method assumes that a detailed numerical model of the structure is available for damage identification and, by vibration measurements, updates the model parameters.
- On another side, data-driven methods is based solely on the recorded response.
-This method is interesting for a real-time damage identification but unavailability of a numerical model often hinders the estimation of damage severity.
+ The model-based methods assume that a detailed numerical model of the structure is available for damage identification and, by vibration measurements, updates the model parameters.
+ On another side, data-driven methods are based solely on the recorded response.
+These methods are interesting for a real-time damage identification but unavailability of a numerical model often hinders the estimation of damage severity.
  A third group includes data-driven methods that use finite element (FE) information without model updating.
@@
 % C.-P. Fritzen, D. Jennewein, T. Kiefer, (1998). Damage detection based on model updating methods, Mechanical Systems and Signal Processing, 12(1): 163–186.
-\cite{fritzen1998damage}
+\cite{fritzen1998damage},
 % Teughels A. and G. De Roeck. (2005). Damage detection and parameter identification by finite element model updating. Archives of Computational Methods in Engineering, 12(2):123-164.
-\cite{teughels2005damage}
+\cite{teughels2005damage} and
 % Simoen E., De Roeck G., and Lombaert G. (2015). Dealing with uncertainty in model updating for damage assessment: a review. Mechanical Systems and Signal Processing, 56-57:123-149.
-\cite{simoen2015dealing}
-
-A REFORMULER EN DESSOUS
+\cite{simoen2015dealing}.
 
@@
 
-Data driven method are inverse methods that use models based on experimental response data recorded on the structure instead of physical models
+Data driven methods are inverse methods that use models based on experimental response data recorded on the structure instead of physical models
 \cite{limongelli2016towards}.
@@
 
-Data-driven methods do not require a FE model  and may be applied with a limited number of available signals (both responses and excitations), making it an interesting method.
+Data-driven methods do not require a FE model  and may be applied with a limited number of available signals (both responses and excitations).
 To extract the damage features, different signal-processing tools can be used.
 Therefore, depending on the tool,  data-driven methods can be classified in Fourier-based methods, Time series method and Time-variant methods.
-A more detailed description of this methods can be found in references %rajouter celles en-dessous
+A more detailed description of these methods can be found in references %rajouter celles en-dessous
 % Fassois S.D. and Sakellariou J.S. (2007) Time-series methods for fault detection and identification in vibrating structures. Phil. Trans. R. Soc. A. 365, 411–448. doi:10.1098/rsta.2006.1929.
-\cite{fassois2007time}
+\cite{fassois2007time} and
 % Staszewski W. J.and Robertson A.N. (2007). Time–frequency and time–scale analyses for structural health monitoring. Phil. Trans. R. Soc. A. 365, 449–477. doi:10.1098/rsta.2006.1936.
 \cite{staszewski2007time}.
+The analyzed method in this paper belongs to this class.
 
@@
 
-The dynamic behaviour of a mechanical system consisting of $n$ masses connected
-through springs and dampers is described by following matrix differential equation:
+The dynamic behaviour of a mechanical system consisting of $n$ degrees of freedom is described by following matrix differential equation:
 \begin{equation}
@@
 properties of the elements.
-Due to the lack of identifiable or measurable material
-constants that govern the global damping behaviour of a structure, it is generally
-impossible to assemble the damping matrix C in the same way as M and K.
 
@@
 \begin{array}{ll}
-x_{k+1} & = Ax_k + Bf_k \\
-y_k & = Cx_k + Bf_k
+x_{k+1} & = A_dx_k + B_df_k \\
+y_k & = C_dx_k + B_df_k
 \end{array}
@@
 \begin{array}{ll}
-A = exp(A_c \Delta t) \\
-B= (A - I) A^{-1}_c B_c \\
-C = C_c \\
-D = D_c
+A_d = exp(A_c \Delta t) \\
+B_d= (A_d - I) A^{-1}_c B_c \\
+C_d = C_c \\
+D_d = D_c
 \end{array}
@@
 In this section, we suppose that we have $n$ sensors, which are located along an axis $z$, and we denote them by
-$\{z_l\}, l\in \{1 ... n\}$. We also suppose we have $N$ measures for each sensor.
+$\{z_l\}, l\in \{1 ... n\}$. We also suppose we have $N$ measurements for each sensor.
 
@@
 
+A detailled analysis of the statistical behaviour of the interpolation error is envisaged in the second part of this project.
+
 \section{Simulation}
@@
 
-As we have seen earlier, the damping matrix can't be determined by measures.
-Thus, we do the same thing that in practical situations: we consider that we are in the case of Rayleigh damping: the damping 
-matrix is a linear combination of the mass and stiffness matrix:
+Due to the lack of identifiable or measurable material
+constants that govern the global damping behaviour of a structure, it is generally
+impossible to assemble the damping matrix C in the same way as M and K.
+Thus, we do the same thing that in practical situations: we consider that we are in the case of Rayleigh, i.e. a linear combination of the mass and stiffness matrix:
 \begin{equation}
@@
 \begin{remark}
-The matrix $A_c$ has $2 \times n$ eigenvalues, but we obtain $n$ frequencies (each of them appears two times). 
+The matrix $A_c$ has $2 \times n$ eigenvalues, but we obtain $n$ frequencies (for each eigenvalues, another one is its conjugated complex). 
 \end{remark}
@@
 We want to calculate the FRF of the system, for each sensor localization.
-Here, we calculate an estimation of the FRF, called $H_1$ estimator.
+Here, we calculate an estimation of the FRF, called $H_1$ estimator \cite{cauberghe2004applied}.
 We suppose we have a vector of the forces $\{ f_k\}_{k=1}^N$ and a vector of the accelerations $\{ y_k\}_{k=1}^N$ for each sensor (the two vectors are size $N$).
@@
 
+Figure (\ref{frf_freq}) present results of the FRF on the simulation datas: here is the curve of the FRF (absolute value) for one sensor, in function of frequencies.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.3\textwidth]{images/FRF_freq.png}
+  \caption{FRF for one sensor, in function of frequencies}
+  \label{frf_freq}
+\end{figure}
+
 \section{Conclusion}

### 2016-11-29 exp.py

@@ -22,12 +22,15 @@ def printAll(ref,inf,sup,undamaged, damaged):
     delta = 3
     plt.ion()
     for i in range(n):
-    	if (i%50 == 0):
+    	if ((i%20 == 0) and (i>300)):
         	plt.plot(numpy.absolute(ref[i]), label = "Reference")
         	plt.plot(numpy.absolute(sup[i]))
         	plt.plot(numpy.absolute(inf[i]))
         	plt.plot(numpy.absolute(undamaged[i]), label = "Undamaged")
         	plt.plot(numpy.absolute(damaged[i]), label = "Damaged")
+        	plt.xlabel('Sensors')
+        	plt.ylabel('FRF')
+        	plt.legend()
         	plt.pause(delta)
         	plt.clf()
 

### 2016-11-29 interpolation.py

@@ -92,10 +92,13 @@ def interpolation_error(complex_list):
 def global_error(frf_list):
 	nb_sensor = len(frf_list[0])
 	error = [0 for i in range(nb_sensor) ]
+	i = 0
 	for frf in frf_list:
-		interpol = interpolation_error(frf)
-		for i in range(nb_sensor):
-			error[i] += interpol[i]**2
+		i += 1
+		if (i>350):
+			interpol = interpolation_error(frf)
+			for i in range(nb_sensor):
+				error[i] += interpol[i]**2
 	for i in range(nb_sensor):
 		error[i] = math.sqrt(error[i])
 	return error

### 2016-11-29 main.py

@@ -6,7 +6,7 @@ import parser
 #import simu_one_sensor as simu
 import simu
 
-CAPTVALUE = 10
+CAPTVALUE = 30
 
 def fibo(n):
     if n <= 1: return 1
@@ -39,13 +39,12 @@ def frf_multiple_capter_simu_undamaged(inFile=None, fichier_sampl = "f_sampl_und
     stiffness = [ 100 for k in range(CAPTVALUE) ]
     N = CAPTVALUE
     #simu: a activer seulement si on veut de nouvelles donnees
-    forces = simu.white_noise(10000,CAPTVALUE)
+    forces = simu.white_noise(100000,CAPTVALUE)
     acc, measures, f_sampl = simu.simulation(pos,mass,stiffness,forces,1,"F_undamaged.txt","Y_undamaged.txt", fichier_sampl)
     #donnes de la simu
     forces = parser.get("F_undamaged.txt")[:]
     measures = parser.get("Y_undamaged.txt")[:]
     #
-    
     res = []
     for i in range(CAPTVALUE):
         res.append(frf.frf(tool.get_lines(forces,i),tool.get_lines(measures,i)))
@@ -65,7 +64,7 @@ def frf_multiple_capter_simu_damaged(damage=5,inFile=None, fichier_sampl = "f_sa
     stiffness[damage] = 10
     N = CAPTVALUE
     #simu: a activer seulement si on veut de nouvelles donnees
-    forces = simu.white_noise(10000,CAPTVALUE)
+    forces = simu.white_noise(100000,CAPTVALUE)
     acc, measures, f_sampl = simu.simulation(pos,mass,stiffness,forces,1,"F_damaged.txt","Y_damaged.txt", fichier_sampl, damaged = "f_sampl_ref.txt")
     #donnes de la simu
     forces = parser.get("F_damaged.txt")[:]
@@ -101,7 +100,7 @@ def frf_multiple_capter_simu_ref(inFile=None, fichier_sampl = "f_sampl_ref.txt")
     for i in range(10):
     	#m = measures[i*10000:(i+1)*10000]
     	#simu: a activer seulement si on veut de nouvelles donnees
-    	forces = simu.white_noise(10000,CAPTVALUE)
+    	forces = simu.white_noise(100000,CAPTVALUE)
     	acc, m, f_sampl = simu.simulation(pos,mass,stiffness,forces,1,"F_ref.txt","Y_ref.txt", fichier_sampl)
     	
     	
[…]

### 2016-11-29 simu.py

@@ -318,3 +318,126 @@ f.close()
 
 
 
+
+
+def simulation_with_damage(pos,mass,stiffness,f):
+#pos: list of the positions of masses
+#mass: list of mass
+#stiffness: list of stiffness
+#f: forces
+
+#first, we make all matrixes
+
+	N = len(f)#ici,absolument 130 000 ou plus
+	n = len(mass)
+	M = matrix_M(mass)
+	K = matrix_K(stiffness)
+	C = matrix_C(M,K,0.005,0.005)
+	
+	Minv = np.linalg.inv(M)
+	MinvK = np.dot(Minv,K)
+	MinvC = np.dot(Minv,C)
+	
+	
+	I = np.eye(2*n)
+	A = np.zeros((2*n,2*n))
+	B = np.zeros((2*n,n))
+	C = np.zeros((n,2*n))
+	D = np.linalg.inv(M)
+	
+	
+	for i in range(n):
+		for j in range(n):
+			A[n+i][j] = - MinvK[i][j]
+			A[n+i][n+j] = - MinvC[i][j]
+			
+			B[n+i][j] = Minv[i][j]
+			
+			C[i][j] = - MinvK[i][j]
+			C[i][n+j] = - MinvC[i][j]
+			
+		A[i][n+i] = 1
+#now, we calculate the time of measure delta_t
+	
+	eigenvalues, eigenvectors = np.linalg.eig(A)
+
+	frq = []
+	for i in eigenvalues:
+		frq += [abs(i)/(2*math.pi)]
+	
+	max_frq = max(frq)
+	
+	omega_max = max_frq*(2*math.pi)
+	
+	f_sampl = (2.5)*max_frq  #Shannon
+
+	lambda_max = eigenvalues[ frq.index( max(frq) ) ]
+	
+	absorption = - (lambda_max.real) / omega_max
+	
+	absorption =  - eigenvalues.real / np.abs(eigenvalues)
+	
+	#print "Coefficient d'amortissement: "
+	#print absorption
+	
+	delta_t = 1/f_sampl
+	
+	#print "Frequence d'echantillonage (Hz): "
+	#print( f_sampl )
+	
+#simulation
+	
+	Ad = scipy.linalg.expm(delta_t*A)
+	Bd = np.dot((Ad - I), np.dot( np.linalg.inv(A) , B ) )
+	
+#matrices with damage
[…]

### 2016-11-29 exp.py
bug

@@ -2,7 +2,12 @@ import main
 import interpolation
 import matplotlib.pyplot as plt
 import numpy
+import parser
 
+
+###########################################################################################
+###########################     Print functions    ########################################
+###########################################################################################
 
 
 def printRef(ref,inf,sup):
@@ -36,6 +41,13 @@ def printAll(ref,inf,sup,undamaged, damaged):
 
 
 
+
+###########################################################################################
+###########################     Experience    #############################################
+###########################################################################################
+
+
+
 def freq_sampl(fichier_sampl):
 	f = open(fichier_sampl,'r')
 	freq = float(f.readline())
@@ -43,14 +55,25 @@ def freq_sampl(fichier_sampl):
 
 
 def experience():
-	frf_list_ref = main.frf_multiple_capter_simu_ref()
-	f_sampl_ref = freq_sampl("f_sampl_ref.txt")
+	#frf_list_ref = main.frf_multiple_capter_simu_ref()
+	frf_list_ref = [ [] for i in range(main.MAKEREF) ]
+	for i in range(main.MAKEREF):
+		frf_list_ref[i] = parser.get("FRF_ref" + str(i) + ".txt")
 	
-	frf_undamaged = numpy.transpose(main.frf_multiple_capter_simu_undamaged())
-	f_sampl_undamaged = freq_sampl("f_sampl_undamaged.txt")
 	
-	frf_damaged = numpy.transpose(main.frf_multiple_capter_simu_damaged())
-	f_sampl_damaged = freq_sampl("f_sampl_damaged.txt")
+	
+	frf_undamaged = numpy.transpose(main.frf_multiple_capter_simu_undamaged("FRF_undamaged.txt"))
+	frf_undamaged = numpy.transpose(parser.get("FRF_undamaged.txt"))
+	
+	
+	frf_damaged = numpy.transpose(main.frf_multiple_capter_simu_damaged("FRF_damaged.txt"))
+	frf_damaged = numpy.transpose(parser.get("FRF_damaged.txt"))
+	
+	
+	
+	#f_sampl_ref = freq_sampl("f_sampl_ref.txt")
+	#f_sampl_undamaged = freq_sampl("f_sampl_undamaged.txt")
+	#f_sampl_damaged = freq_sampl("f_sampl_damaged.txt")
 
 
 	print("*************************\n Average frf calcul \n *************************")
@@ -63,9 +86,9 @@ def experience():
[…]

### 2016-11-29 main.py

@@ -1,3 +1,8 @@
+###########################################################################################
+###########################     Imports    ################################################
+###########################################################################################
+
+
 import frf
 import matplotlib.pyplot as plt
 import numpy
@@ -6,7 +11,21 @@ import parser
 #import simu_one_sensor as simu
 import simu
 
-CAPTVALUE = 30
+###########################################################################################
+###########################     Variables    ##############################################
+###########################################################################################
+
+
+CAPTVALUE = 10
+SAMPLVALUE = 100000
+MAKEREF = 10
+
+
+
+###########################################################################################
+###########################     FRF calculs    ############################################
+###########################################################################################
+
 
 def fibo(n):
     if n <= 1: return 1
@@ -39,8 +58,8 @@ def frf_multiple_capter_simu_undamaged(inFile=None, fichier_sampl = "f_sampl_und
     stiffness = [ 100 for k in range(CAPTVALUE) ]
     N = CAPTVALUE
     #simu: a activer seulement si on veut de nouvelles donnees
-    forces = simu.white_noise(100000,CAPTVALUE)
-    acc, measures, f_sampl = simu.simulation(pos,mass,stiffness,forces,1,"F_undamaged.txt","Y_undamaged.txt", fichier_sampl)
+    forces = simu.white_noise(SAMPLVALUE,CAPTVALUE)
+    acc, measures, f_sampl = simu.simulation(pos,mass,stiffness,forces,"F_undamaged.txt","Y_undamaged.txt", fichier_sampl)
     #donnes de la simu
     forces = parser.get("F_undamaged.txt")[:]
     measures = parser.get("Y_undamaged.txt")[:]
@@ -53,7 +72,7 @@ def frf_multiple_capter_simu_undamaged(inFile=None, fichier_sampl = "f_sampl_und
     else:
         parser.writeValues(inFile,res)
         print("Values written in " + inFile)
-        return res
+        #return res
 
 
[…]

### 2016-11-29 simu.py

@@ -88,12 +88,11 @@ def write_Y(fichier, measures):
 
 
 
-def simulation(pos,mass,stiffness,f, col, fichier_forces, fichier_acc, fichier_sampl, damaged = ""):
+def simulation(pos,mass,stiffness,f, fichier_forces, fichier_acc, fichier_sampl, damaged = ""):
 #pos: list of the positions of masses
 #mass: list of mass
 #stiffness: list of stiffness
 #f: forces
-#col: sensor
 
 #return two lists:
 #	-the first with velocity and acceleration of each mass
@@ -201,19 +200,6 @@ def simulation(pos,mass,stiffness,f, col, fichier_forces, fichier_acc, fichier_s
 	Ad = scipy.linalg.expm(delta_t*A)
 	Bd = np.dot((Ad - I), np.dot( np.linalg.inv(A) , B ) )
 	
-	Bd_col = np.zeros(2*n)
-	D_col = np.zeros(n)
-	for i in range(2*n):
-		Bd_col[i] = Bd[i][col]
-	for i in range(n):
-		D_col[i] = D[i][col]
-	"""
-	print(Bd)
-	print(Bd_col)
-	print(D)
-	print(D_col)
-	"""
-	
 	acc = [ [0 for k in range(2*n) ] ]
 	
 	measures = []
@@ -238,9 +224,9 @@ def simulation(pos,mass,stiffness,f, col, fichier_forces, fichier_acc, fichier_s
 	#print(measures[N-1])
 	
 	write_Y(fichier_forces, f)
-	print("F.txt created")
+	#print("F.txt created")
 	write_Y(fichier_acc, measures)
-	print("Y.txt created")
+	#print("Y.txt created")
 	
 	return acc, measures, f_sampl
 

### 2016-11-30 exp.py
parser

@@ -56,18 +56,18 @@ def freq_sampl(fichier_sampl):
 
 def experience():
 	#frf_list_ref = main.frf_multiple_capter_simu_ref()
-	frf_list_ref = [ [] for i in range(main.MAKEREF) ]
-	for i in range(main.MAKEREF):
-		frf_list_ref[i] = parser.get("FRF_ref" + str(i) + ".txt")
+	frf_list_ref = [ parser.get2("FRF_ref" + str(i) + ".txt") for i in range(main.MAKEREF) ]
+	#for i in range(main.MAKEREF):
+	#	frf_list_ref[i] =
 	
 	
 	
-	frf_undamaged = numpy.transpose(main.frf_multiple_capter_simu_undamaged("FRF_undamaged.txt"))
-	frf_undamaged = numpy.transpose(parser.get("FRF_undamaged.txt"))
+	#frf_undamaged = numpy.transpose(main.frf_multiple_capter_simu_undamaged("FRF_undamaged.txt"))
+	frf_undamaged = numpy.transpose(parser.get2("FRF_undamaged.txt"))
 	
 	
-	frf_damaged = numpy.transpose(main.frf_multiple_capter_simu_damaged("FRF_damaged.txt"))
-	frf_damaged = numpy.transpose(parser.get("FRF_damaged.txt"))
+	#frf_damaged = numpy.transpose(main.frf_multiple_capter_simu_damaged("FRF_damaged.txt"))
+	frf_damaged = numpy.transpose(parser.get2("FRF_damaged.txt"))
 	
 	
 	

### 2016-11-30 main.py

@@ -19,6 +19,7 @@ import simu
 CAPTVALUE = 10
 SAMPLVALUE = 100000
 MAKEREF = 10
+DAMAGE = 5
 
 
 
@@ -75,12 +76,12 @@ def frf_multiple_capter_simu_undamaged(inFile=None, fichier_sampl = "f_sampl_und
         #return res
 
 
-def frf_multiple_capter_simu_damaged(damage=5,inFile=None, fichier_sampl = "f_sampl_damaged.txt"):
+def frf_multiple_capter_simu_damaged(inFile=None, fichier_sampl = "f_sampl_damaged.txt"):
     print("*************************\n Simulation for damaged state \n *************************")
     pos = [ k for k in range(CAPTVALUE) ]
     mass = [ 100 for k in range(CAPTVALUE) ]
     stiffness = [ 100 for k in range(CAPTVALUE) ]
-    stiffness[damage] = 10
+    stiffness[DAMAGE] = 10
     N = CAPTVALUE
     #simu: a activer seulement si on veut de nouvelles donnees
     forces = simu.white_noise(SAMPLVALUE,CAPTVALUE)

### 2016-11-30 exp.py
standard deviation

@@ -17,8 +17,8 @@ def printRef(ref,inf,sup):
     for i in range(n):
     	if (i%50 == 0):
         	plt.plot(numpy.absolute(ref[i]))
-        	plt.plot(numpy.absolute(sup[i]))
-        	plt.plot(numpy.absolute(inf[i]))
+        	plt.plot(sup[i])
+        	plt.plot(inf[i])
         	plt.pause(delta)
         	plt.clf()
 
@@ -57,9 +57,6 @@ def freq_sampl(fichier_sampl):
 def experience():
 	#frf_list_ref = main.frf_multiple_capter_simu_ref()
 	frf_list_ref = [ parser.get2("FRF_ref" + str(i) + ".txt") for i in range(main.MAKEREF) ]
-	#for i in range(main.MAKEREF):
-	#	frf_list_ref[i] =
-	
 	
 	
 	#frf_undamaged = numpy.transpose(main.frf_multiple_capter_simu_undamaged("FRF_undamaged.txt"))
@@ -68,13 +65,6 @@ def experience():
 	
 	#frf_damaged = numpy.transpose(main.frf_multiple_capter_simu_damaged("FRF_damaged.txt"))
 	frf_damaged = numpy.transpose(parser.get2("FRF_damaged.txt"))
-	
-	
-	
-	#f_sampl_ref = freq_sampl("f_sampl_ref.txt")
-	#f_sampl_undamaged = freq_sampl("f_sampl_undamaged.txt")
-	#f_sampl_damaged = freq_sampl("f_sampl_damaged.txt")
-
 
 	print("*************************\n Average frf calcul \n *************************")
 
@@ -86,6 +76,10 @@ def experience():
 	print("Nombre de capteur:" + str(nb_sensor))
 	print("Nombre de frequences:" + str(nb_freq))
 	
+	
+	#f_sampl_ref = freq_sampl("f_sampl_ref.txt")
+	#f_sampl_undamaged = freq_sampl("f_sampl_undamaged.txt")
+	#f_sampl_damaged = freq_sampl("f_sampl_damaged.txt")
 	#print("Frequence d'echantillonage reference: " + str( f_sampl_ref ) )
 	#print("Frequence d'echantillonage (undamaged): " + str( f_sampl_undamaged ) )
 	#print("Frequence d'echantillonage (damaged): " + str( f_sampl_damaged ) )
@@ -93,7 +87,7 @@ def experience():
 	
[…]

### 2016-11-30 interpolation.py

@@ -9,58 +9,12 @@ import parser
 import sys
 import json
 
-#d = parser.get(sys.argv[1])
 
-x =[1, 2, 3, 4, 5] #donnees
-y = [1.+9.j, 1.+2.j, 1.+3.j, 1.+25.j, 2] #donnees
-
-x2 =[1, 2, 3, 5] #donnees
-y2 = [1.+9.j, 1.+2.j, 1.+3.j, 2] #donnees
-
-#f = interp1d(x, y) #linear
-#f2 = interp1d(x,y, kind = 'quadratic')
-#f3 = interp1d(x2,y2, kind = 'cubic')
+###########################################################################################
+###########################     Interpolation error    ####################################
+###########################################################################################
 
 
-
-#t = f3(x)
-"""
-for j in x:
-	if(j>1 and j<len(x)) :  
-		print "Suppression du capteur : " + str(j)
-		x2 = list(x)
-		y2 = list(y)
-		del x2[j-1]
-		del y2[j-1]
-		f3 = interp1d(x2, y2, kind = 'cubic')
-		for i in x :
-			print "Erreur d'interpolation du capteur " + str(i) + " : " + str(np.absolute(y[i-1] - f3(i)))
-			print "\n"
-"""
-"""
-print "Pour x = 4, lineaire y = " + str(f(4)) + ", quadratique y = " + str(f2(4)) + " \net cubique = " + str(f3(4))
-
-
-
-
-
-r, i = [], []
-r2, i2 = [], []
-for k in t:
-	r += [ k.real ]
-	i += [ k.imag ]
-
-for k in y:
-	r2 += [ k.real ]
-	i2 += [ k.imag ]
-
-
-plt.plot(r)
-plt.plot(i)
-plt.plot(r2)
-plt.plot(i2)
-plt.show()
-"""
 
 #entree: liste de valeur de la FRF pour une frequence pour chaque capteur
 #sortie: liste des erreurs au carre (une erreur par capteur)
@@ -104,6 +58,11 @@ def global_error(frf_list):
 	return error
 
 
+###########################################################################################
+###########################     Reference calcul    #######################################
+###########################################################################################
+
+
 
[…]

### 2016-11-30 slides/slides.tex
slides

\documentclass{beamer}
  \usepackage[utf8]{inputenc}
  \usepackage{graphicx}
  \usepackage{array}
  \usepackage{url}
  \usetheme{Warsaw}

  \title{Damage localization based on vibrations}
  \author{Benjamin Fasquelle, Nicolas Pompidor and Jimmy Rogala}
  \institute{École Normale Supérieure de Rennes, département Informatique et Télécommunications}

  \begin{document}

%\AtBeginSection[]
%{
%  \begin{frame}<beamer>
%    \frametitle{Sommaire}
%{\scriptsize\tableofcontents[currentsection]
%}
%  \end{frame}
%}

\addtobeamertemplate{footline}{\hfill\insertframenumber/\inserttotalframenumber}

%\newcommand\vect[3]{ {}^{#1} \textbf{#2}_{#3} }
%\newcommand\vectn[2]{ {}^{#1} \textbf{n}^{#2} }
%\newcommand\vectdot[3]{ {}^{#1} \dot{\textbf{#2}}_{#3} }
%\newcommand\I{\textbf{I}}
%\newcommand\Lm[1]{\textbf{L}_{\textbf{#1}} }
%\newcommand\sk[1]{[#1]_{\times} }

  \begin{frame}
  \titlepage
  \end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

\begin{frame}{Bridge}
\end{frame}

\begin{frame}{Damage and SHM}
\end{frame}

\begin{frame}{Why we do that}
\end{frame}

\begin{frame}{4 levels}
\end{frame}

\begin{frame}{transition/plan}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{State of the art}

\begin{frame}{intro}
\end{frame}

\begin{frame}{Model based methods}
\end{frame}

\begin{frame}{Data driven methods}
\end{frame}

\begin{frame}{Combined methods}
\end{frame}

\begin{frame}{transition}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Physical Models}

\begin{frame}{Finite Elements model}
\end{frame}

\begin{frame}{Continu model}
\end{frame}

\begin{frame}{Discret model}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{FRF Interpolation Method}

\begin{frame}{Intro}
\end{frame}

\begin{frame}{Interpolation}
\end{frame}

\begin{frame}{Error}
\end{frame}

\begin{frame}{Proba}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Simulation}

\begin{frame}{System masses-springs}
\end{frame}

\begin{frame}{Discret model + sample freq}
\end{frame}

\begin{frame}{Interpolation}
\end{frame}

\begin{frame}{Results}
\end{frame}

\begin{frame}{Results}
\end{frame}

\begin{frame}{Results}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion}

\begin{frame}{Conclusion}
\end{frame}

  \end{document}

### 2016-11-30 slides/slides.tex
slides

@@
 \begin{frame}{Bridge}
+\includegraphics[width=5cm]{images/crack.jpg}
 \end{frame}
@@
 \begin{frame}{Damage and SHM}
+\begin{exampleblock}{Damages}
+Changes in a system that negatively affect its performance.
+\end{exampleblock}
+
+\begin{exampleblock}{Structure Health Monitoring}
+A damage identification strategy for aerospace, civil and mechanical structures.
+\end{exampleblock}
+
 \end{frame}
@@
 \begin{frame}{Finite Elements model}
+
+\begin{center}
+$M \ddot{q}(t) + C \dot{q}(t) + K q(t) = f(t)$
+\end{center}
+
 \end{frame}
 
-\begin{frame}{Continu model}
+\begin{frame}{Continous-time state-space model}
+
+\begin{center}
+$\left\{
+\begin{array}{ll}
+\dot{x}(t) = A_cx(t) + B_cf(t) \\
+y(t) = C_cx(t) + D_cf(t)
+\end{array}
+\right.$
+\end{center}
+
+$x =
+\begin{pmatrix}
+\dot{q} \\
+q
+\end{pmatrix}$
+
 \end{frame}
 
-\begin{frame}{Discret model}
+\begin{frame}{Discret-time state-space model}
+
+\begin{center}
+$\left\{
+\begin{array}{ll}
+x_{k+1} & = A_dx_k + B_df_k \\
+y_k & = C_dx_k + B_df_k
+\end{array}
+\right.$
+
+\vspace{5mm}
+
+where
+
+\vspace{5mm}
+
+$\begin{array}{ll}
+A_d = exp(A_c \Delta t) \\
+B_d= (A_d - I) A^{-1}_c B_c \\
+C_d = C_c \\
+D_d = D_c
+\end{array}$
+
+\end{center}
+
 \end{frame}
@@
 \begin{frame}{Intro}
+
+\begin{itemize}
+\item FRF calcul
+\item Interpolation on the FRF
+\item Error calcul
+\end{itemize}
+
 \end{frame}
@@
 \begin{frame}{Interpolation}
+\begin{center}
+\includegraphics[width=5cm]{images/interpolation.png}
+\end{center}
+
 \end{frame}
@@
 \begin{frame}{Error}
+
+\begin{center}
+$E(z_l,f_i) = | H_R(z_l,f_i) - H_S(z_l,f_i) |$
+
+\vspace{5mm}
+
+$E(z_l) = \sqrt{  \sum\limits_{i=1}^N  E^2(z_l,f_i) }$
+
+\vspace{5mm}
+
+$\Delta E(z_l) = E_d(z_l) - E_0(z_l)$
+
+\end{center}
+
 \end{frame}
@@
 \begin{frame}{Proba}
+\begin{center}
+\includegraphics[width=5cm]{images/gaussiennes.png}
+\end{center}
 \end{frame}
@@
 \begin{frame}{System masses-springs}
+\begin{center}
+\includegraphics[width=5cm]{images/ressorts.png}
+
+$M \ddot{q}(t) + C \dot{q}(t) + K q(t) = f(t)$
+\end{center}
+
 \end{frame}
 
-\begin{frame}{Discret model + sample freq}
+\begin{frame}{Sample frequency and Discret-time state-space model}
+
+We find the sample frequency with the eigenvalues of the matrix $A_c$ of the continous-time state-space model.
+
+\vspace{5mm}
+
+Thus, we have the matrices of the discrete-time state-space model
+\begin{center}
+$\left\{
+\begin{array}{ll}
+x_{k+1} & = A_dx_k + B_df_k \\
+y_k & = C_dx_k + B_df_k
+\end{array}
+\right.$
+\end{center}
+
 \end{frame}
 
-\begin{frame}{Interpolation}
+\begin{frame}{FRF and Interpolation}
 \end{frame}
@@
 \begin{frame}{Results}
+\begin{center}
+\includegraphics[width=5cm]{images/FRF_freq.png}
+
+FRF for one sensor in function of frequencies
+\end{center}
 \end{frame}
@@
 \begin{frame}{Results}
+\begin{center}
+\includegraphics[width=5cm]{images/curve_damage.png}
+
+For a fixed frequency, the FRF value for each sensor
+\end{center}
+
 \end{frame}

### 2016-11-30 exp.py

@@ -87,7 +87,7 @@ def experience():
 	
 	ref, inf, sup = interpolation.create_ref( frf_list_ref )
 	
-	printRef(ref,inf,sup)
+	#printRef(ref,inf,sup)
 	
 	error_ref = interpolation.global_error(ref)
 	error_undamaged = interpolation.global_error(frf_undamaged)
@@ -108,7 +108,7 @@ def experience():
 	print("Damaged state: ")
 	print(damaged)
 	
-	#printAll(ref,inf,sup, frf_undamaged, frf_damaged)
+	printAll(ref,inf,sup, frf_undamaged, frf_damaged)
 
 
 

### 2016-11-30 interpolation.py

@@ -46,13 +46,13 @@ def interpolation_error(complex_list):
 def global_error(frf_list):
 	nb_sensor = len(frf_list[0])
 	error = [0 for i in range(nb_sensor) ]
-	i = 0
+	#k = 0
 	for frf in frf_list:
-		i += 1
-		if (i>350):
-			interpol = interpolation_error(frf)
-			for i in range(nb_sensor):
-				error[i] += interpol[i]**2
+		#k += 1
+		#if (k>350):
+		interpol = interpolation_error(frf)
+		for i in range(nb_sensor):
+			error[i] += interpol[i]**2
 	for i in range(nb_sensor):
 		error[i] = math.sqrt(error[i])
 	return error

### 2016-11-30 exp.py
small correction

@@ -9,13 +9,16 @@ import parser
 ###########################     Print functions    ########################################
 ###########################################################################################
 
+indices = [399, 386, 364, 334, 296, 252, 202, 147, 90, 30]
+
+
 
 def printRef(ref,inf,sup):
     n = len(ref)
     delta = 3
     plt.ion()
     for i in range(n):
-    	if (i%50 == 0):
+    	if (i%10 == 0):
         	plt.plot(numpy.absolute(ref[i]))
         	plt.plot(sup[i])
         	plt.plot(inf[i])
@@ -25,9 +28,9 @@ def printRef(ref,inf,sup):
 def printAll(ref,inf,sup,undamaged, damaged):
     n = len(ref)
     delta = 3
-    plt.ion()
+    #plt.ion()
     for i in range(n):
-    	if ((i%20 == 0) and (i>300)):
+    	if (i % 10 == 0):
         	plt.plot(numpy.absolute(ref[i]), label = "Reference")
         	plt.plot(numpy.absolute(sup[i]))
         	plt.plot(numpy.absolute(inf[i]))
@@ -35,9 +38,11 @@ def printAll(ref,inf,sup,undamaged, damaged):
         	plt.plot(numpy.absolute(damaged[i]), label = "Damaged")
         	plt.xlabel('Sensors')
         	plt.ylabel('FRF')
+        	plt.title('freq: ' + str(i))
         	plt.legend()
-        	plt.pause(delta)
-        	plt.clf()
+        	#plt.pause(delta)
+        	#plt.clf()
+        	plt.show()
 
 
 
@@ -77,12 +82,12 @@ def experience():
 	print("Nombre de frequences:" + str(nb_freq))
 	
 	
-	#f_sampl_ref = freq_sampl("f_sampl_ref.txt")
-	#f_sampl_undamaged = freq_sampl("f_sampl_undamaged.txt")
-	#f_sampl_damaged = freq_sampl("f_sampl_damaged.txt")
-	#print("Frequence d'echantillonage reference: " + str( f_sampl_ref ) )
-	#print("Frequence d'echantillonage (undamaged): " + str( f_sampl_undamaged ) )
-	#print("Frequence d'echantillonage (damaged): " + str( f_sampl_damaged ) )
+	f_sampl_ref = freq_sampl("f_sampl_ref.txt")
+	f_sampl_undamaged = freq_sampl("f_sampl_undamaged.txt")
[…]

### 2016-11-30 main.py

@@ -19,7 +19,7 @@ import simu
 CAPTVALUE = 10
 SAMPLVALUE = 100000
 MAKEREF = 10
-DAMAGE = 5
+DAMAGE = 9
 
 
 
@@ -81,7 +81,7 @@ def frf_multiple_capter_simu_damaged(inFile=None, fichier_sampl = "f_sampl_damag
     pos = [ k for k in range(CAPTVALUE) ]
     mass = [ 100 for k in range(CAPTVALUE) ]
     stiffness = [ 100 for k in range(CAPTVALUE) ]
-    stiffness[DAMAGE] = 10
+    stiffness[DAMAGE] = 80
     N = CAPTVALUE
     #simu: a activer seulement si on veut de nouvelles donnees
     forces = simu.white_noise(SAMPLVALUE,CAPTVALUE)
@@ -152,11 +152,12 @@ def frf_multiple_capter_simu_ref(inFile=None, fichier_sampl = "f_sampl_ref.txt")
 def printPerCapter(res,time):
     n = len(res)
     delta = time/n
-    plt.ion()
+    #plt.ion()
     for i in range(n):
         plt.plot(numpy.absolute(res[i]))
-        plt.pause(delta)
-        plt.clf()
+        #plt.pause(delta)
+        #plt.clf()
+        plt.show()
 
 def printPerCapter2(res1,res2,time):
     n = len(res1)
@@ -171,15 +172,15 @@ def printPerCapter2(res1,res2,time):
 def printPerFreq(res,time):
     n = len(res[0])
     delta = time/n/10
-    plt.ion()
+    #plt.ion()
     for i in range(n):
         plt.plot(numpy.absolute(tool.get_lines(res,i)))
-        plt.pause(delta)
-        plt.clf()
-       
+        #plt.pause(delta)
+        #plt.clf()
+        plt.show()
         
         
 #frf_multiple_capter_simu_ref("FRF_ref_")        
 #frf_multiple_capter_simu("FRF_damage.txt")
-#printPerCapter(frf_multiple_capter_simu(),10)
+#printPerCapter(frf_multiple_capter_simu_undamaged(),10)
 #printPerCapter2(frf_multiple_capter_simu_damaged(),frf_multiple_capter_simu_undamaged(),10)

### 2016-11-30 simu.py

@@ -163,6 +163,8 @@ def simulation(pos,mass,stiffness,f, fichier_forces, fichier_acc, fichier_sampl,
 	
 	max_frq = max(frq)
 	
+	#print( frq )
+	
 	omega_max = max_frq*(2*math.pi)
 	
 	if (damaged == ""):

### 2016-11-30 exp.py
added interpolation affichage

@@ -44,6 +44,26 @@ def printAll(ref,inf,sup,undamaged, damaged):
         	#plt.clf()
         	plt.show()
 
+def printInterpolationError(ref,inf,sup,undamaged,damaged):
+    n = len(ref)
+    delta = 3
+    #plt.ion()
+    undamaged = interpolation.interpolation_error(undamaged)
+    damaged = interpolation.interpolation_error(damaged)
+    for i in range(n):
+    	if (i % 10 == 0):
+            undam = interpolation.interpolation_error(undamaged[i])
+            dam = interpolation.interpolation_error(damaged[i])
+        	plt.plot(numpy.absolute(undam), label = "Undamaged",'ro')
+        	plt.plot(numpy.absolute(dam), label = "Damaged",'ro')
+        	plt.xlabel('Sensors')
+        	plt.ylabel('FRF')
+        	plt.title('freq: ' + str(i))
+        	plt.legend()
+        	#plt.pause(delta)
+        	#plt.clf()
+        	plt.show()
+
 
 
 
@@ -62,12 +82,12 @@ def freq_sampl(fichier_sampl):
 def experience():
 	#frf_list_ref = main.frf_multiple_capter_simu_ref()
 	frf_list_ref = [ parser.get2("FRF_ref" + str(i) + ".txt") for i in range(main.MAKEREF) ]
-	
-	
+
+
 	#frf_undamaged = numpy.transpose(main.frf_multiple_capter_simu_undamaged("FRF_undamaged.txt"))
 	frf_undamaged = numpy.transpose(parser.get2("FRF_undamaged.txt"))
-	
-	
+
+
 	#frf_damaged = numpy.transpose(main.frf_multiple_capter_simu_damaged("FRF_damaged.txt"))
 	frf_damaged = numpy.transpose(parser.get2("FRF_damaged.txt"))
 
@@ -80,31 +100,31 @@ def experience():
 	print("Nombre de frf par capteur et par frequence:" + str(nb_frf))
 	print("Nombre de capteur:" + str(nb_sensor))
 	print("Nombre de frequences:" + str(nb_freq))
-	
-	
+
+
 	f_sampl_ref = freq_sampl("f_sampl_ref.txt")
 	f_sampl_undamaged = freq_sampl("f_sampl_undamaged.txt")
 	f_sampl_damaged = freq_sampl("f_sampl_damaged.txt")
 	print("Frequence d'echantillonage reference: " + str( f_sampl_ref ) )
[…]

### 2016-11-30 exp.py
bug encore

@@ -3,6 +3,20 @@ import interpolation
 import matplotlib.pyplot as plt
 import numpy
 import parser
+import simu
+
+###########################################################################################
+###########################     Variables    ##############################################
+###########################################################################################
+
+
+CAPTVALUE = simu.CAPTVALUE
+SAMPLVALUE = simu.SAMPLVALUE
+MAKEREF = simu.MAKEREF
+DAMAGED_SENSOR = simu.DAMAGED_SENSOR
+DAMAGE = simu.DAMAGE
+
+
 
 
 ###########################################################################################
@@ -48,21 +62,19 @@ def printInterpolationError(ref,inf,sup,undamaged,damaged):
     n = len(ref)
     delta = 3
     #plt.ion()
-    undamaged = interpolation.interpolation_error(undamaged)
-    damaged = interpolation.interpolation_error(damaged)
     for i in range(n):
     	if (i % 10 == 0):
-            undam = interpolation.interpolation_error(undamaged[i])
-            dam = interpolation.interpolation_error(damaged[i])
-        	plt.plot(numpy.absolute(undam), label = "Undamaged",'ro')
-        	plt.plot(numpy.absolute(dam), label = "Damaged",'ro')
-        	plt.xlabel('Sensors')
-        	plt.ylabel('FRF')
-        	plt.title('freq: ' + str(i))
-        	plt.legend()
+			undam = interpolation.interpolation_error(undamaged[i])
+			dam = interpolation.interpolation_error(damaged[i])
+			plt.plot(numpy.absolute(undam), label = "Undamaged")
+			plt.plot(numpy.absolute(dam), label = "Damaged")
+			plt.xlabel('Sensors')
+			plt.ylabel('Error')
+			plt.title('freq: ' + str(i))
+			plt.legend()
         	#plt.pause(delta)
         	#plt.clf()
-        	plt.show()
+			plt.show()
 
 
 
@@ -88,7 +100,7 @@ def experience():
 	frf_undamaged = numpy.transpose(parser.get2("FRF_undamaged.txt"))
 
 
-	#frf_damaged = numpy.transpose(main.frf_multiple_capter_simu_damaged("FRF_damaged.txt"))
+	frf_damaged = numpy.transpose(main.frf_multiple_capter_simu_damaged("FRF_damaged.txt"))
[…]

### 2016-11-30 interpolation.py

@@ -8,6 +8,20 @@ import math
 import parser
 import sys
 import json
+import simu
+
+###########################################################################################
+###########################     Variables    ##############################################
+###########################################################################################
+
+
+CAPTVALUE = simu.CAPTVALUE
+SAMPLVALUE = simu.SAMPLVALUE
+MAKEREF = simu.MAKEREF
+DAMAGED_SENSOR = simu.DAMAGED_SENSOR
+DAMAGE = simu.DAMAGE
+
+
 
 
 ###########################################################################################

### 2016-11-30 main.py

@@ -16,11 +16,11 @@ import simu
 ###########################################################################################
 
 
-CAPTVALUE = 10
-SAMPLVALUE = 100000
-MAKEREF = 10
-DAMAGE = 9
-
+CAPTVALUE = simu.CAPTVALUE
+SAMPLVALUE = simu.SAMPLVALUE
+MAKEREF = simu.MAKEREF
+DAMAGED_SENSOR = simu.DAMAGED_SENSOR
+DAMAGE = simu.DAMAGE
 
 
 ###########################################################################################
@@ -33,10 +33,6 @@ def fibo(n):
     return(fibo(n-1) + fibo(n-2))
 
 def frf_multiple_capter_file(inFile=None):
-    pos = [ k for k in range(CAPTVALUE) ]
-    mass = [ 100 for k in range(CAPTVALUE) ]
-    stiffness = [ 100 for k in range(CAPTVALUE) ]
-    N = CAPTVALUE
     #donnes du prof
     forces = parser.get("donnees/F.txt")[:]
     measures = parser.get("donnees/Y.txt")[:]
@@ -54,13 +50,9 @@ def frf_multiple_capter_file(inFile=None):
 
 def frf_multiple_capter_simu_undamaged(inFile=None, fichier_sampl = "f_sampl_undamaged.txt"):
     print("*************************\n Simulation for undamaged state \n *************************")
-    pos = [ k for k in range(CAPTVALUE) ]
-    mass = [ 100 for k in range(CAPTVALUE) ]
-    stiffness = [ 100 for k in range(CAPTVALUE) ]
-    N = CAPTVALUE
     #simu: a activer seulement si on veut de nouvelles donnees
     forces = simu.white_noise(SAMPLVALUE,CAPTVALUE)
-    acc, measures, f_sampl = simu.simulation(pos,mass,stiffness,forces,"F_undamaged.txt","Y_undamaged.txt", fichier_sampl)
+    acc, measures, f_sampl = simu.simulation(forces,"F_undamaged.txt","Y_undamaged.txt", fichier_sampl)
     #donnes de la simu
     forces = parser.get("F_undamaged.txt")[:]
     measures = parser.get("Y_undamaged.txt")[:]
@@ -78,14 +70,9 @@ def frf_multiple_capter_simu_undamaged(inFile=None, fichier_sampl = "f_sampl_und
 
 def frf_multiple_capter_simu_damaged(inFile=None, fichier_sampl = "f_sampl_damaged.txt"):
[…]

### 2016-11-30 simu.py

@@ -12,6 +12,26 @@ from scipy.stats import norm
 
 
 ################################################
+############# variables ########################
+################################################
+
+
+
+CAPTVALUE = 10
+SAMPLVALUE = 100000
+MAKEREF = 10
+DAMAGED_SENSOR = 5
+DAMAGE = 100
+
+
+pos = [ k for k in range(CAPTVALUE) ]
+mass = [ 100 for k in range(CAPTVALUE) ]
+stiffness = [ 100 for k in range(CAPTVALUE) ]
+
+
+
+
+################################################
 ############# functions ########################
 ################################################
 
@@ -88,7 +108,14 @@ def write_Y(fichier, measures):
 
 
 
-def simulation(pos,mass,stiffness,f, fichier_forces, fichier_acc, fichier_sampl, damaged = ""):
+################################################
+############# Simulation #######################
+################################################
+
+
+
+
+def simulation(f, fichier_forces, fichier_acc, fichier_sampl, damaged = ""):
 #pos: list of the positions of masses
 #mass: list of mass
 #stiffness: list of stiffness
@@ -181,6 +208,7 @@ def simulation(pos,mass,stiffness,f, fichier_forces, fichier_acc, fichier_sampl,
 		f_write_sampl = open(fichier_sampl,'w')
 		f_write_sampl.write(str(f_sampl))
 		f_write_sampl.close()
+		stiffness[DAMAGED_SENSOR] = DAMAGE
 		
 	
 	lambda_max = eigenvalues[ frq.index( max(frq) ) ]
@@ -249,183 +277,5 @@ def white_noise(n,nb_sensor):
 	for i in range(n):
 		noise += [ norm.rvs(size=nb_sensor, loc = mean, scale = standard_deviation) ]
 	return noise
-
-
-#print( norm.rvs(loc = mean, scale = standard_deviation, size = 5) )
-
-
-
-################################################
-############# simulation #######################
[…]

### 2016-12-02 slides/slides.tex
bridge
slides physical models

@@
 \begin{frame}{Bridge}
-\includegraphics[width=5cm]{images/crack.jpg}
+\begin{center}
+\includegraphics[width=4cm]{images/crack.jpg}
+
+\pause
+
+\includegraphics[width=5cm]{images/bridge.png}
+\end{center}
 \end{frame}
@@
 \begin{frame}{4 levels}
+\begin{center}
+\begin{itemize}
+\item Detection: Is the structure damaged or not?
+\item Localization: Where is the damaged area located?
+\item Quantification: What is the extent of damage?
+\item Prediction: What is the remaining service life of the structure?
+\end{itemize}
+\end{center}
 \end{frame}
@@
 \begin{center}
+\includegraphics[height=4cm]{images/finite_element.png}
+
 $M \ddot{q}(t) + C \dot{q}(t) + K q(t) = f(t)$
@@
 \begin{frame}{Continous-time state-space model}
+With the variable change $x =
+\begin{pmatrix}
+\dot{q} \\
+q
+\end{pmatrix}$, we have:
 
@@
 
-$x =
-\begin{pmatrix}
-\dot{q} \\
-q
-\end{pmatrix}$
+where $A_c, B_c, C_c$ and $D_c$ rely on $M, C$ and $K$.
 
@@
 
+We need to convert the system to discret time:
+
 \begin{center}
+
 $\left\{
@@
 
-\vspace{5mm}
+\end{center}
 
@@
 
-\vspace{5mm}
+\begin{center}
 
@@
 
-\begin{frame}{Intro}
+\begin{frame}{FRF Interpolation Method}
 
+\begin{alertblock}{Main hypothesis}
+A concentrated damage reflects
+in a loss of spatial regularity of the vibrational profile of a
+structure, compared with the undamaged state.
+\end{alertblock}
+
+\underline{Main steps}:
 \begin{itemize}
-\item FRF calcul
+\item Frequency Response Function (FRF) calcul
 \item Interpolation on the FRF
@@
 \begin{frame}{Interpolation}
+Cubic polynomial spline interpolation:
+
 \begin{center}
@@
 
-\begin{frame}{Error}
+\begin{frame}{Error calcul}
 
+For each sensor $z_l$ at the frequency $f_i$:
 \begin{center}
 $E(z_l,f_i) = | H_R(z_l,f_i) - H_S(z_l,f_i) |$
+\end{center}
 
-\vspace{5mm}
+For each sensor:
+\begin{center}
+$E(z_l) = \sqrt{  \sum\limits_{i=1}^N  E^2(z_l,f_i) }$
+\end{center}
 
-$E(z_l) = \sqrt{  \sum\limits_{i=1}^N  E^2(z_l,f_i) }$
-
-\vspace{5mm}
-
+Difference with the reference state:
+\begin{center}
 $\Delta E(z_l) = E_d(z_l) - E_0(z_l)$
-
 \end{center}
@@
 
-\begin{frame}{Proba}
+\begin{frame}{Probability of identification of a damage}
 \begin{center}
-\includegraphics[width=5cm]{images/gaussiennes.png}
+\includegraphics[height=4cm]{images/gaussiennes.png}
 \end{center}
@@
 
-Thus, we have the matrices of the discrete-time state-space model
+Thus, we have the matrices of the discrete-time state-space model:
 \begin{center}

### 2016-12-02 simu.py

@@ -127,6 +127,8 @@ def simulation(f, fichier_forces, fichier_acc, fichier_sampl, damaged = ""):
 
 
 #first, we make all matrixes
+	if (damaged == ""):
+		stiffness[DAMAGED_SENSOR] = DAMAGE
 
 	N = len(f)
 	n = len(mass)
@@ -208,7 +210,7 @@ def simulation(f, fichier_forces, fichier_acc, fichier_sampl, damaged = ""):
 		f_write_sampl = open(fichier_sampl,'w')
 		f_write_sampl.write(str(f_sampl))
 		f_write_sampl.close()
-		stiffness[DAMAGED_SENSOR] = DAMAGE
+		
 		
 	
 	lambda_max = eigenvalues[ frq.index( max(frq) ) ]

### 2016-12-04 exp.py
physical models

@@ -96,7 +96,7 @@ def experience():
 	frf_list_ref = [ parser.get2("FRF_ref" + str(i) + ".txt") for i in range(main.MAKEREF) ]
 
 
-	#frf_undamaged = numpy.transpose(main.frf_multiple_capter_simu_undamaged("FRF_undamaged.txt"))
+	frf_undamaged = numpy.transpose(main.frf_multiple_capter_simu_undamaged("FRF_undamaged.txt"))
 	frf_undamaged = numpy.transpose(parser.get2("FRF_undamaged.txt"))
 
 

### 2016-12-04 rapport/paper.tex
paper correction
correction damage

@@
 These techniques may be costly, taking a long time to be performed and impractical to detect damage in large urban areas.
- Furthermore, they may fail if damage is not visibly evident. This is why other global methods were developed that are automated
- and based on sensor measurements.
+ Furthermore, they may fail if damage is not visibly evident. This is why other global methods automated
+ and based on sensor measurements were developed.
 
@@
 
-The dynamic behaviour of a mechanical system consisting of $n$ degrees of freedom is described by following matrix differential equation:
+The dynamic behaviour of a mechanical system consisting of $n$ degrees of freedom (see Figure (\ref{finite_el}) is described by following matrix differential equation:
 \begin{equation}
@@
 properties of the elements.
+
+\begin{figure}
+  \centering
+  \includegraphics[height=0.3\textwidth]{images/finite_element.png}
+  \caption{Finite element model, from \cite{peeters2000system}}
+  \label{finite_el}
+\end{figure}
 
@@
 
+We have to calculate for each sensor $z_l$ and for each considered frequency $f_i$ the cubic polynomial spline interpolation of the transfer function $H_R(z_k,f_i)$.
+The cubic spline interpolation is a piecewise continuous curve, passing through each of the values.
+There is a separate cubic polynomial interpolation for each interval, each with its own coefficients.
+Cubic polynomial spline interpolations produce an interpolated function that is continuous through to the second derivative.
+
+With this interpolation, we can calculate the error as it is described in the section IV.
+
 \subsection{Result}
 
-Figure (\ref{frf_freq}) present results of the FRF on the simulation datas: here is the curve of the FRF (absolute value) for one sensor, in function of frequencies.
+For the simulation, we put a sensor on each mass.
+
+Figure (\ref{frf_freq}) presents results of the FRF on the simulation datas: here is the curve of the FRF (absolute value) of one sensor (4 in total), in function of frequencies.
+We can see three peaks which are at the natural frequencies of the system, but there is one of these frequencies which not present a peak.
+Seeing this curve for each sensor, we observed that certain sensors have one peak for each natural frequencies, and others sensors have one peak for each except one, relied on the position of the sensor in the system.
+It is problematic because it is around the natural frequencies of the system that we have better datas, but if certain sensors haven't response with certain frequencies, we could miss out on a damage.
 
@@
   \includegraphics[width=0.3\textwidth]{images/FRF_freq.png}
-  \caption{FRF for one sensor, in function of frequencies}
+  \caption{FRF of one sensor (4 in total), in function of frequencies}
   \label{frf_freq}
+\end{figure}
+
+Figure (\ref{damage}) is the FRF values for ten sensors (at a fixed frequency). Here, we easily can see that there is a damage between the sensors 4 and 5 (as we noticed it in the simulation).
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.3\textwidth]{images/curve_damage.png}
+  \caption{FRF values for 10 sensors, at a fixed frequency}
+  \label{damage}
 \end{figure}

### 2016-12-04 exp.py

@@ -46,8 +46,8 @@ def printAll(ref,inf,sup,undamaged, damaged):
     for i in range(n):
     	if (i % 10 == 0):
         	plt.plot(numpy.absolute(ref[i]), label = "Reference")
-        	plt.plot(numpy.absolute(sup[i]))
-        	plt.plot(numpy.absolute(inf[i]))
+        	#plt.plot(numpy.absolute(sup[i]))
+        	#plt.plot(numpy.absolute(inf[i]))
         	plt.plot(numpy.absolute(undamaged[i]), label = "Undamaged")
         	plt.plot(numpy.absolute(damaged[i]), label = "Damaged")
         	plt.xlabel('Sensors')
@@ -96,7 +96,7 @@ def experience():
 	frf_list_ref = [ parser.get2("FRF_ref" + str(i) + ".txt") for i in range(main.MAKEREF) ]
 
 
-	frf_undamaged = numpy.transpose(main.frf_multiple_capter_simu_undamaged("FRF_undamaged.txt"))
+	#frf_undamaged = numpy.transpose(main.frf_multiple_capter_simu_undamaged("FRF_undamaged.txt"))
 	frf_undamaged = numpy.transpose(parser.get2("FRF_undamaged.txt"))
 
 
@@ -114,10 +114,8 @@ def experience():
 	print("Nombre de frequences:" + str(nb_freq))
 
 
-	f_sampl_ref = freq_sampl("f_sampl_ref.txt")
 	f_sampl_undamaged = freq_sampl("f_sampl_undamaged.txt")
 	f_sampl_damaged = freq_sampl("f_sampl_damaged.txt")
-	print("Frequence d'echantillonage reference: " + str( f_sampl_ref ) )
 	print("Frequence d'echantillonage (undamaged): " + str( f_sampl_undamaged ) )
 	print("Frequence d'echantillonage (damaged): " + str( f_sampl_damaged ) )
 
@@ -138,8 +136,8 @@ def experience():
 		damaged[i] = error_damaged[i] - error_ref[i]
 
 	print("*************************\n Errors \n *************************")
-	print("Error ref: ")
-	print(error_ref)
+	#print("Error ref: ")
+	#print(error_ref)
 	print("Undamaged state: ")
 	print(undamaged)
 	print("Damaged state: ")
@@ -148,8 +146,12 @@ def experience():
 	plt.plot(error_undamaged)
[…]

### 2016-12-04 main.py

@@ -72,7 +72,7 @@ def frf_multiple_capter_simu_damaged(inFile=None, fichier_sampl = "f_sampl_damag
     print("*************************\n Simulation for damaged state \n *************************")
     #simu: a activer seulement si on veut de nouvelles donnees
     forces = simu.white_noise(SAMPLVALUE,CAPTVALUE)
-    acc, measures, f_sampl = simu.simulation(forces,"F_damaged.txt","Y_damaged.txt", fichier_sampl, damaged = "f_sampl_ref.txt")
+    acc, measures, f_sampl = simu.simulation(forces,"F_damaged.txt","Y_damaged.txt", fichier_sampl, damaged = "f_sampl_undamaged.txt")
     #donnes de la simu
     forces = parser.get("F_damaged.txt")[:]
     measures = parser.get("Y_damaged.txt")[:]

### 2016-12-04 simu.py

@@ -21,7 +21,7 @@ CAPTVALUE = 10
 SAMPLVALUE = 100000
 MAKEREF = 10
 DAMAGED_SENSOR = 5
-DAMAGE = 100
+DAMAGE = 10
 
 
 pos = [ k for k in range(CAPTVALUE) ]
@@ -115,7 +115,7 @@ def write_Y(fichier, measures):
 
 
 
-def simulation(f, fichier_forces, fichier_acc, fichier_sampl, damaged = ""):
+def simulation(f, fichier_forces, fichier_acc, fichier_sampl, damaged = None):
 #pos: list of the positions of masses
 #mass: list of mass
 #stiffness: list of stiffness
@@ -127,7 +127,7 @@ def simulation(f, fichier_forces, fichier_acc, fichier_sampl, damaged = ""):
 
 
 #first, we make all matrixes
-	if (damaged == ""):
+	if (damaged != None):
 		stiffness[DAMAGED_SENSOR] = DAMAGE
 
 	N = len(f)
@@ -196,7 +196,7 @@ def simulation(f, fichier_forces, fichier_acc, fichier_sampl, damaged = ""):
 	
 	omega_max = max_frq*(2*math.pi)
 	
-	if (damaged == ""):
+	if (damaged == None):
 		f_sampl = (2.5)*max_frq  #Shannon
 	
 		f_write_sampl = open(fichier_sampl,'w')

### 2016-12-04 slides/slides.tex
Skide update intro
physical models
Ajout slides : state of the art : :+1:

@@
   \institute{École Normale Supérieure de Rennes, département Informatique et Télécommunications}
+
+  \setbeamertemplate{navigation symbols}{}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction}
+\subsection{Purpose}
+\begin{frame}{Purpose}
 
-\section{Introduction}
+\begin{columns}
+		\begin{column}{0.5\textwidth} 
+		\begin{center}
+			\includegraphics[width=5cm]{images/crack.jpg}
+		\end{center}
+		\end{column}
+		\begin{column}{0.7\textwidth}
+		\begin{center}
+			\pause
+			\includegraphics[width=6cm]{images/minneapolis.jpg}
+		\end{center}
+		\end{column}
+	\end{columns}
 
-\begin{frame}{Bridge}
-\begin{center}
-\includegraphics[width=4cm]{images/crack.jpg}
-
-\pause
-
-\includegraphics[width=5cm]{images/bridge.png}
-\end{center}
+\vspace{1\baselineskip}
+\begin{itemize}
+\item ``Better safe than sorry."
+\vspace{1\baselineskip}
+\item Example: accelerate inspection of post-earthquake damage.
+\end{itemize}
 \end{frame}
 
-\begin{frame}{Damage and SHM}
+\subsection{Definitions}
+
+\begin{frame}{Definitions}
 \begin{exampleblock}{Damages}
@@
 \end{exampleblock}
-
+\begin{center}
+	\includegraphics[width=4.5cm]{images/crack.jpg}
+\end{center}
 \begin{exampleblock}{Structure Health Monitoring}
@@
 
-\begin{frame}{Why we do that}
-\end{frame}
+\subsection{4 levels in damage identification}
+\begin{frame}{4 levels in damage identification}
 
-\begin{frame}{4 levels}
 \begin{center}
-\begin{itemize}
+\begin{itemize}[<+->]
 \item Detection: Is the structure damaged or not?
+\vspace{1\baselineskip}
 \item Localization: Where is the damaged area located?
+\vspace{1\baselineskip}
 \item Quantification: What is the extent of damage?
+\vspace{1\baselineskip}
 \item Prediction: What is the remaining service life of the structure?
@@
 
-\begin{frame}{transition/plan}
+\subsection{Tools}
+\begin{frame}{Tools}
+\begin{block}{Traditional methods}
+Visual inspections or experimental techniques (such as radiography or ultrasound)
+\end{block}
+
+\setbeamertemplate{itemize item}{\color{green}$\checkmark$}
+\begin{columns}
+		\begin{column}{0.5\textwidth} 
+		\begin{center}
+			\begin{itemize}
+				\item Detailed information about a local damage state
+			\end{itemize}
+		\end{center}
+		\end{column}
+		\begin{column}{0.5\textwidth}
+		\begin{center}
+		\setbeamertemplate{itemize item}{\color{red}$\times$}
+			\begin{itemize}
+				\item Requires to know area where it is located
+				\item May be costly
+				\item Taking a long time to be performed
+				\item Hope for easy access
+			\end{itemize}
+		\end{center}
+		\end{column}
+	\end{columns}
+	\pause
+	\begin{center}
+	\textcolor{red}{{\large 
+$\Rightarrow$ Global methods automated and based on sensor measurements were developed.}}
+
+	\end{center}
+
 \end{frame}
@@
 
-\begin{frame}{intro}
+\subsection{Vibration-based damage identification}
+\begin{frame}{Vibration-based damage identification}
+\begin{block}{General idea}
+	Damage affects the physical properties (mass, damping, and stiffness) of the structure.\newline
+
+	$\Rightarrow$ This will cause detectable changes in modal properties (natural frequencies, modal damping, and mode shapes).
+\end{block}
+\begin{itemize}
+\item Example: Cracks cause reductions in stiffness.
+\end{itemize}
+\vspace{0.5\baselineskip}
+\begin{center}
+\textcolor{red}{{\large Two differents methods : model-based or data-driven.}}
+\end{center}
 \end{frame}
 
+\subsection{Model based methods}
 \begin{frame}{Model based methods}
+\begin{center}
+\begin{itemize}
+\item Damage is identified through the updating of a finite element (FE) model.
+
+\vspace{1\baselineskip}
+\item Modal characteristics is the experimental data used for damage
+assessment through FE model updating.
+\vspace{1\baselineskip}
+\item Different types of modal data can be used (natural frequencies, eigenvalues, etc).
+\end{itemize}
+\end{center}
 \end{frame}
 
+\subsection{Data driven methods}
 \begin{frame}{Data driven methods}
-\end{frame}
+\begin{center}
+\begin{itemize}
+\item Methods that use models based on experimental response data recorded on the structure.
 
-\begin{frame}{Combined methods}
+\vspace{1\baselineskip}
+\item Damage parameter $D$ is the variation of the damage feature $d$ between
+the inspection $I$ and the reference $R$ configurations:
+
+\begin{equation}
+D=d_{I} - d_{R}
+\end{equation}
+\item Data-driven methods may be applied with a limited number of available signals (both
+responses and excitations).
+\end{itemize}
+\end{center}
+
 \end{frame}
@@
 
+\subsection{Finite Elements model}
 \begin{frame}{Finite Elements model}
@@
 
+\subsection{Continous-time state-space model}
 \begin{frame}{Continous-time state-space model}
@@
 
+\subsection{Discret-time state-space model}
 \begin{frame}{Discret-time state-space model}
@@
 
+\subsection{FRF Interpolation Method}
 \begin{frame}{FRF Interpolation Method}
@@
 
+\subsection{FRF calcul}
+\begin{frame}{FRF calcul}
+\end{frame}
+
+\subsection{Interpolation}
 \begin{frame}{Interpolation}
 Cubic polynomial spline interpolation:
+
+\end{frame}
+
+\subsection{Error calcul}
+\begin{frame}{Error calcul}
 
@@
 \end{center}
-
-\end{frame}
-
-\begin{frame}{Error calcul}
 
@@
 For each sensor:
-\begin{center}
 $E(z_l) = \sqrt{  \sum\limits_{i=1}^N  E^2(z_l,f_i) }$
-\end{center}
 
 Difference with the reference state:
-\begin{center}
 $\Delta E(z_l) = E_d(z_l) - E_0(z_l)$
-\end{center}
 
@@
 
+\subsection{Probability of identification of a damage}
 \begin{frame}{Probability of identification of a damage}
@@
 
+\subsection{System masses-springs}
 \begin{frame}{System masses-springs}
@@
 
+\begin{exampleblock}{Masses}
+\begin{center}
+$
+M = 
+\begin{pmatrix} 
+m_1\\ 
+&\ddots\\ 
+&&m_n
+\end{pmatrix}
+$
+\end{center}
+\end{exampleblock}
+
 \end{frame}
 
+\subsection{Sample frequency and Discret-time state-space model}
 \begin{frame}{Sample frequency and Discret-time state-space model}
@@
 
+\subsection{FRF and Interpolation}
 \begin{frame}{FRF and Interpolation}
@@
 
-\begin{frame}{Results}
+\subsection{Results}
+\begin{frame}{Results 1/3}
 \begin{center}
@@
 
-\begin{frame}{Results}
+\begin{frame}{Results 2/3}
 \begin{center}
@@
 
-\begin{frame}{Results}
+\begin{frame}{Results 3/3}
 \end{frame}

### 2016-12-06 rapport/paper.tex
slides

@@
 
-Figure (\ref{frf_freq}) presents results of the FRF on the simulation datas: here is the curve of the FRF (absolute value) of one sensor (4 in total), in function of frequencies.
+Figure (\ref{frf_freq}) presents results of the FRF on the simulation datas: here is the curve of the FRF (absolute value) of one sensor (ten in total), against frequencies.
 We can see three peaks which are at the natural frequencies of the system, but there is one of these frequencies which not present a peak.
@@
   \centering
-  \includegraphics[width=0.3\textwidth]{images/FRF_freq.png}
-  \caption{FRF of one sensor (4 in total), in function of frequencies}
+  \includegraphics[width=0.3\textwidth]{images/persensor1.png}
+  \caption{FRF of one sensor (ten in total), against frequencies}
   \label{frf_freq}
@@
   \centering
-  \includegraphics[width=0.3\textwidth]{images/curve_damage.png}
+  \includegraphics[width=0.3\textwidth]{images/damaged4.png}
   \caption{FRF values for 10 sensors, at a fixed frequency}

### 2016-12-06 slides/slides.tex
slides

@@
   \usepackage{url}
+  \usepackage{color}
   \usetheme{Warsaw}
@@
 \begin{center}
-\begin{itemize}[<+->]
-\item Detection: Is the structure damaged or not?
+\begin{itemize}
+\item<1-> Detection: Is the structure damaged or not?
 \vspace{1\baselineskip}
-\item Localization: Where is the damaged area located?
+\item<2-|alert@5> Localization: Where is the damaged area located?
 \vspace{1\baselineskip}
-\item Quantification: What is the extent of damage?
+\item<3-> Quantification: What is the extent of damage?
 \vspace{1\baselineskip}
-\item Prediction: What is the remaining service life of the structure?
+\item<4-> Prediction: What is the remaining service life of the structure?
 \end{itemize}
@@
 
-\begin{frame}{transition}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{FRF Interpolation Method}
+
+\subsection{FRF Interpolation Method}
+\begin{frame}{FRF Interpolation Method}
+
+\begin{center}
+Data driven method
+\end{center}
+
+\pause
+
+\begin{alertblock}{Main hypothesis}
+A concentrated damage reflects
+in a loss of spatial regularity of the vibrational profile of a
+structure, compared with the undamaged state.
+\end{alertblock}
+
+\pause
+
+\underline{Main steps}:
+\begin{itemize}
+\item Frequency Response Function (FRF) calcul
+\item Interpolation on the FRF
+\item Error calcul
+\end{itemize}
+
+\end{frame}
+
+\subsection{FRF calcul}
+\begin{frame}{FRF calcul}
+\begin{exampleblock}{Frequency Response Function}
+\begin{center}
+$H = \frac{Y}{F}$
+\end{center}
+$F$: input
+
+$Y$: output
+\end{exampleblock}
+
+\pause
+
+Fourier transform:
+$
+F_n = \sum\limits_{k=1}^N f_k e^{-2i\pi kn/N},
+Y_n = \sum\limits_{k=1}^N y_k e^{-2i\pi kn/N} \ \ \ \ \ n \in \{1 ... N\}
+$
+
+\begin{block}{Estimator}
+\begin{center}
+$H_1(n) = \frac{Y_n}{F_n}$
+\end{center}
+\end{block}
+
+\end{frame}
+
+\subsection{Interpolation}
+\begin{frame}{Interpolation}
+\underline{Cubic polynomial spline interpolation:}
+\begin{itemize}
+\item piecewise continuous curve, passing through each of the values
+\item continuous through to the second derivative
+\end{itemize}
+
+\begin{center}
+\includegraphics[width=5cm]{images/interpolation_spline.png}
+\end{center}
+
+\end{frame}
+
+\subsection{Error calcul}
+\begin{frame}{Error calcul}
+
+\begin{center}
+\includegraphics[width=6cm]{images/interpolation.png}
+\end{center}
+
+For each sensor $z_l$ at the frequency $f_i$:
+$E(z_l,f_i) = | H_R(z_l,f_i) - H_S(z_l,f_i) |$
+
+\pause
+
+For each sensor:
+$E(z_l) = \sqrt{  \sum\limits_{i=1}^N  E^2(z_l,f_i) }$
+
+\pause
+
+Difference with the reference state:
+$\Delta E(z_l) = E_d(z_l) - E_0(z_l)$
+
+\end{frame}
+
+\subsection{Probability of identification of a damage}
+\begin{frame}{Probability of identification of a damage}
+\begin{center}
+\includegraphics[height=4cm]{images/gaussiennes.png}
+\end{center}
 \end{frame}
@@
 \end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{FRF Interpolation Method}
-
-\subsection{FRF Interpolation Method}
-\begin{frame}{FRF Interpolation Method}
-
-\begin{alertblock}{Main hypothesis}
-A concentrated damage reflects
-in a loss of spatial regularity of the vibrational profile of a
-structure, compared with the undamaged state.
-\end{alertblock}
-
-\underline{Main steps}:
-\begin{itemize}
-\item Frequency Response Function (FRF) calcul
-\item Interpolation on the FRF
-\item Error calcul
-\end{itemize}
-
-\end{frame}
-
-\subsection{FRF calcul}
-\begin{frame}{FRF calcul}
-\end{frame}
-
-\subsection{Interpolation}
-\begin{frame}{Interpolation}
-Cubic polynomial spline interpolation:
-
-\end{frame}
-
-\subsection{Error calcul}
-\begin{frame}{Error calcul}
-
-\begin{center}
-\includegraphics[width=5cm]{images/interpolation.png}
-\end{center}
-
-For each sensor $z_l$ at the frequency $f_i$:
-\begin{center}
-$E(z_l,f_i) = | H_R(z_l,f_i) - H_S(z_l,f_i) |$
-\end{center}
-
-For each sensor:
-$E(z_l) = \sqrt{  \sum\limits_{i=1}^N  E^2(z_l,f_i) }$
-
-Difference with the reference state:
-$\Delta E(z_l) = E_d(z_l) - E_0(z_l)$
-
-\end{frame}
-
-\subsection{Probability of identification of a damage}
-\begin{frame}{Probability of identification of a damage}
-\begin{center}
-\includegraphics[height=4cm]{images/gaussiennes.png}
-\end{center}
-\end{frame}
 
@@
 \end{center}
+
+\pause
 
@@
 
-\subsection{FRF and Interpolation}
-\begin{frame}{FRF and Interpolation}
-\end{frame}
+\subsection{Results}
+\begin{frame}{Results 1/4}
+\begin{center}
+\includegraphics[height=4cm]{images/persensor1.png}
+\hfill
+\includegraphics[height=4cm]{images/persensor2.png}
 
-\subsection{Results}
-\begin{frame}{Results 1/3}
-\begin{center}
-\includegraphics[width=5cm]{images/FRF_freq.png}
-
-FRF for one sensor in function of frequencies
+FRF for one sensor against frequencies
 \end{center}
@@
 
-\begin{frame}{Results 2/3}
+\begin{frame}{Results 2/4}
 \begin{center}
-\includegraphics[width=5cm]{images/curve_damage.png}
+\includegraphics[height=4cm]{images/damaged4.png}
+\hfill
+\includegraphics[height=4cm]{images/damaged_curve.png}
 
 For a fixed frequency, the FRF value for each sensor
+
+\vspace{5mm}
+
+Damage between sensors 4 and 5
 \end{center}
@@
 
-\begin{frame}{Results 3/3}
+\begin{frame}{Results 3/4}
+\begin{center}
+\includegraphics[height=4cm]{images/damaged2.png}
+\hfill
+\includegraphics[height=4cm]{images/damaged3.png}
+
+For a fixed frequency, the FRF value for each sensor
+
+\vspace{5mm}
+
+Damage between sensors 4 and 5
+\end{center}
+\end{frame}
+
+\begin{frame}{Results 4/4}
+\begin{center}
+\includegraphics[height=4cm]{images/globalerror.png}
+
+Global error
+
+\vspace{5mm}
+
+Damage between sensors 4 and 5
+\end{center}
+
 \end{frame}
@@
 \begin{frame}{Conclusion}
+\underline{What we did:}
+\begin{itemize}
+\item State of the art
+\item Implementation of the FRF interpolation method with a simulation
+\end{itemize}
+
+\underline{What we will do:}
+\begin{itemize}
+\item Development of a statistical extension of this method
+\end{itemize}
+
 \end{frame}

### 2016-12-06 exp.py

@@ -77,7 +77,27 @@ def printInterpolationError(ref,inf,sup,undamaged,damaged):
 			plt.show()
 
 
-
+def printAllMoustache(refs,undamaged, damaged):
+    n = len(undamaged)
+    delta = 3
+    #plt.ion()
+    for i in range(n):
+        if (i % 10 == 0):
+            l = [[] for j in range(len(refs[0]))]
+            for exp in range(len(refs)):
+                for captor in range(len(refs[exp])):
+                    l[captor] += [refs[exp][captor][i]]
+            l = [numpy.absolute(d) for d in l]
+            plt.boxplot(l,positions = [i for i in range(len(l))])
+            plt.plot(numpy.absolute(undamaged[i]), label = "Undamaged")
+            plt.plot(numpy.absolute(damaged[i]), label = "Damaged")
+            plt.xlabel('Sensors')
+            plt.ylabel('FRF')
+            plt.title('freq: ' + str(i))
+            plt.legend()
+            #plt.pause(delta)
+            #plt.clf()
+            plt.show()
 
 ###########################################################################################
 ###########################     Experience    #############################################
@@ -100,7 +120,7 @@ def experience():
 	frf_undamaged = numpy.transpose(parser.get2("FRF_undamaged.txt"))
 
 
-	frf_damaged = numpy.transpose(main.frf_multiple_capter_simu_damaged("FRF_damaged.txt"))
+	#frf_damaged = numpy.transpose(main.frf_multiple_capter_simu_damaged("FRF_damaged.txt"))
 	frf_damaged = numpy.transpose(parser.get2("FRF_damaged.txt"))
 
 	print("*************************\n Average frf calcul \n *************************")
@@ -147,13 +167,15 @@ def experience():
 	plt.plot(error_damaged)
 	plt.show()
 	
-	plt.plot(undamaged)
-	plt.plot(damaged)
+	plt.plot(undamaged, label = "Undamaged")
+	plt.plot(damaged, label = "Damaged")
+	plt.xlabel("Global error")
+	plt.legend()
 	plt.show()
 
-	printAll(ref,inf,sup, frf_undamaged, frf_damaged)
+	#printAll(ref,inf,sup, frf_undamaged, frf_damaged)
 	#printInterpolationError(ref,inf,sup,undamaged,damaged)
-
+	#printAllMoustache(frf_list_ref, frf_undamaged, frf_damaged)
 
 
 

### 2016-12-06 interpolation.py

@@ -163,7 +163,15 @@ plt.plot(i)
 plt.plot(r2)
 plt.plot(i2)
 plt.show()
+x =[1, 3, 4, 7, 8] #donnees
+y = [10.1, 5.2, 6, 2, 4] #donnees
+f = interp1d(x, y, kind = 'cubic')
+N = 1000
+x_affich = [ (1.0 + k*7.0/(N+1)) for k in range(N)]
+y_affich = [ f(1.0 + k*7.0/(N+1)) for k in range(N)]
+plt.plot(x,y, 'ro')
+plt.plot(x_affich, y_affich)
+plt.xlabel("Cubic spline interpolation")
+plt.legend()
+plt.show()
 """
-
-
-

### 2016-12-06 main.py

@@ -110,8 +110,11 @@ def printPerCapter(res,time):
     #plt.ion()
     for i in range(n):
         plt.plot(numpy.absolute(res[i]))
+        plt.xlabel("Fequencies")
+        plt.ylabel("FRF")
         #plt.pause(delta)
         #plt.clf()
+        plt.legend()
         plt.show()
 
 def printPerCapter2(res1,res2,time):

### 2016-12-06 rapport/paper.tex
paper

@@
 
-The dynamic behaviour of a mechanical system consisting of $n$ degrees of freedom (see Figure (\ref{finite_el}) is described by following matrix differential equation:
+The dynamic behaviour of a mechanical system consisting of $n$ degrees of freedom (see Figure (\ref{finite_el})) is described by following matrix differential equation:
 \begin{equation}
@@
 
-For civil engineering structures, Equation (\ref{fondamental}) is obtained as the finite element approximation of the system with only $n$ dregrees of freedom.
-The structure is divided in elements, and the global mass matrix $M$ and stiffness matrix $K$ are generated from the geometry and material
-properties of the elements.
-
-\begin{figure}
+\begin{figure}[h!]
   \centering
@@
 \end{figure}
+
+For civil engineering structures, Equation (\ref{fondamental}) is obtained as the finite element approximation of the system with only $n$ dregrees of freedom.
+The structure is divided in elements, and the global mass matrix $M$ and stiffness matrix $K$ are generated from the geometry and material
+properties of the elements.
 
@@
 
-\begin{figure}
+\begin{figure}[h!]
   \centering
@@
 
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.25\textwidth]{images/interpolation_spline.png}
+  \caption{Cubic spline interpolation}
+  \label{spline}
+\end{figure}
+
 With this interpolation, we can calculate the error as it is described in the section IV.
@@
 
-Figure (\ref{damage}) is the FRF values for ten sensors (at a fixed frequency). Here, we easily can see that there is a damage between the sensors 4 and 5 (as we noticed it in the simulation).
+Figure (\ref{damage}) is the FRF values for ten sensors (at a fixed frequency).
+Here, we easily can see that there is a damage between the sensors 4 and 5 (as we noticed it in the simulation).
+However,
 
-\begin{figure}
+\begin{figure}[h!]
   \centering
   \includegraphics[width=0.3\textwidth]{images/damaged4.png}
-  \caption{FRF values for 10 sensors, at a fixed frequency}
+  \caption{FRF values for 10 sensors, at a fixed frequency (damage between sensors 4 and 5}
   \label{damage}
+\end{figure}
+
+Figure (\ref{damage2}) is the FRF values for the same ten sensors that in Figure (\ref{damage}), at a different frequency.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.3\textwidth]{images/damaged3.png}
+  \caption{FRF values for 10 sensors, at a fixed frequency (damage between sensors 4 and 5}
+  \label{damage2}
+\end{figure}
+
+Finaly, we can see in Figure (\ref{globalerror}) the global error described in section IV.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.3\textwidth]{images/globalerror.png}
+  \caption{FRF values for 10 sensors, at a fixed frequency (damage between sensors 4 and 5}
+  \label{globalerror}
 \end{figure}

### 2016-12-06 rapport/paper.tex
paper ended

@@
 
-\subsection{Result}
+\subsection{Results}
 
-For the simulation, we put a sensor on each mass.
+For the following simulation results, we consider a system with 10 masses.
+We put a sensor on each mass.
+For the damaged state, we lower the stifness of the spring between sensors 4 and 5 by 90\%.
+The values of the FRF on the figures are the norm of the FRF values.
 
-Figure (\ref{frf_freq}) presents results of the FRF on the simulation datas: here is the curve of the FRF (absolute value) of one sensor (ten in total), against frequencies.
+Figure (\ref{frf_freq}) presents results of the FRF on the simulation datas: here is the curve of the FRF of one sensor, against frequencies.
 We can see three peaks which are at the natural frequencies of the system, but there is one of these frequencies which not present a peak.
@@
 
-Figure (\ref{damage}) is the FRF values for ten sensors (at a fixed frequency).
-Here, we easily can see that there is a damage between the sensors 4 and 5 (as we noticed it in the simulation).
-However,
-
 \begin{figure}[h!]
@@
 
-Figure (\ref{damage2}) is the FRF values for the same ten sensors that in Figure (\ref{damage}), at a different frequency.
+Figure (\ref{damage}) is the FRF values for the ten sensors (at a fixed frequency).
+Here, we easily can see that there is a damage between the sensors 4 and 5 (as we noticed it).
+However, as the damaged FRF is away from the reference FRF, we can see that there isn't a significant loss of regularity at sensors 4 and 5 (the interpolation error isn't high).
+
+Figure (\ref{damage2}) is the FRF values for the same ten sensors that in Figure (\ref{damage}), with the same damage, at a different frequency.
+Here, we can see a significant loss of regularity at sensors 6 and 8.
+It shows that we have to select the frequencies where we calculate the interpolation error.
+Indeed, an hypothesis is that significant values of the FRF are near to the natural frequencies of the system (that we can see in Figure (\ref{frf_freq})).
 
@@
 Finaly, we can see in Figure (\ref{globalerror}) the global error described in section IV.
+The two first and last values (i.e.
+for sensor 0,1,8 and 9) aren't useful because cubic spline interpolation requires two values on each side of the interpolate value.
+We can see that, if we consider all frequencies for the error calcul, results aren't as we want: here the damaged system has a FRF more regular than the undamaged system.
+A selection of the frequencies is necessary.
 
@@
 \section{Conclusion}
+
+In this paper, we presented the structure heatlh monitoring and a state of the art for this.
+Then we detailled one of the methods, the FRF interpolation method, and some physical models.
+Last, we presented our simulation with a sping-mass system and our results with the implementation of the FRF interpolation method.
+
+We saw that we have to do a selection of the frequencies where we calculate the interpolation error.
+
+In the second part of this project, we will do a detailled analysis of the statistical behaviour of the interpolation error.
 

### 2016-12-07 slides/slides.tex
slides xtra

@@
   \author{Benjamin Fasquelle, Nicolas Pompidor and Jimmy Rogala}
-  \institute{École Normale Supérieure de Rennes, département Informatique et Télécommunications}
+  \date{Supervised by Michael Döhler}
+  \institute{\textit{École Normale Supérieure de Rennes, département Informatique et Télécommunications}}
 
@@
 
-%\AtBeginSection[]
-%{
-%  \begin{frame}<beamer>
-%    \frametitle{Sommaire}
-%{\scriptsize\tableofcontents[currentsection]
-%}
-%  \end{frame}
-%}
+\AtBeginSection[]
+{
+  \begin{frame}<beamer>
+  \setcounter{tocdepth}{1}
+{\tableofcontents[currentsection]
+}
+  \end{frame}
+}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{frame}<beamer>
+  \setcounter{tocdepth}{1}
+{\tableofcontents
+}
+\end{frame}
+
 \section{Introduction}
+
 \subsection{Purpose}
+
 \begin{frame}{Purpose}
@@
 \begin{itemize}
-\item<1-> Detection: Is the structure damaged or not?
+\item<1-> {\only<5-6>{\color{green}}Detection: Is the structure damaged or not?}
 \vspace{1\baselineskip}
-\item<2-|alert@5> Localization: Where is the damaged area located?
+\item<2-|alert@6> Localization: Where is the damaged area located?
 \vspace{1\baselineskip}
@@
 			\begin{itemize}
-				\item Requires to know area where it is located
+				\item Require to know area where it is located
 				\item May be costly
@@
 \end{center}
+
+\begin{block}{}
+Applicable to arbitrary structural types, but a precise model is required
+\end{block}
+
 \end{frame}
@@
 
+\begin{block}{}
+Require no complicated model, allowing a simple and fast evaluation, but usually many sensors are required
+\end{block}
+
 \end{frame}
@@
 
-\section{FRF Interpolation Method}
+\section{Vibration modelling}
 
-\subsection{FRF Interpolation Method}
-\begin{frame}{FRF Interpolation Method}
-
-\begin{center}
-Data driven method
-\end{center}
-
-\pause
-
-\begin{alertblock}{Main hypothesis}
-A concentrated damage reflects
-in a loss of spatial regularity of the vibrational profile of a
-structure, compared with the undamaged state.
-\end{alertblock}
-
-\pause
-
-\underline{Main steps}:
-\begin{itemize}
-\item Frequency Response Function (FRF) calcul
-\item Interpolation on the FRF
-\item Error calcul
-\end{itemize}
-
-\end{frame}
-
-\subsection{FRF calcul}
-\begin{frame}{FRF calcul}
-\begin{exampleblock}{Frequency Response Function}
-\begin{center}
-$H = \frac{Y}{F}$
-\end{center}
-$F$: input
-
-$Y$: output
-\end{exampleblock}
-
-\pause
-
-Fourier transform:
-$
-F_n = \sum\limits_{k=1}^N f_k e^{-2i\pi kn/N},
-Y_n = \sum\limits_{k=1}^N y_k e^{-2i\pi kn/N} \ \ \ \ \ n \in \{1 ... N\}
-$
-
-\begin{block}{Estimator}
-\begin{center}
-$H_1(n) = \frac{Y_n}{F_n}$
-\end{center}
-\end{block}
-
-\end{frame}
-
-\subsection{Interpolation}
-\begin{frame}{Interpolation}
-\underline{Cubic polynomial spline interpolation:}
-\begin{itemize}
-\item piecewise continuous curve, passing through each of the values
-\item continuous through to the second derivative
-\end{itemize}
-
-\begin{center}
-\includegraphics[width=5cm]{images/interpolation_spline.png}
-\end{center}
-
-\end{frame}
-
-\subsection{Error calcul}
-\begin{frame}{Error calcul}
-
-\begin{center}
-\includegraphics[width=6cm]{images/interpolation.png}
-\end{center}
-
-For each sensor $z_l$ at the frequency $f_i$:
-$E(z_l,f_i) = | H_R(z_l,f_i) - H_S(z_l,f_i) |$
-
-\pause
-
-For each sensor:
-$E(z_l) = \sqrt{  \sum\limits_{i=1}^N  E^2(z_l,f_i) }$
-
-\pause
-
-Difference with the reference state:
-$\Delta E(z_l) = E_d(z_l) - E_0(z_l)$
-
-\end{frame}
-
-\subsection{Probability of identification of a damage}
-\begin{frame}{Probability of identification of a damage}
-\begin{center}
-\includegraphics[height=4cm]{images/gaussiennes.png}
-\end{center}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Physical Models}
-
-\subsection{Finite Elements model}
-\begin{frame}{Finite Elements model}
+\subsection{Vibration modelling}
+\begin{frame}{Vibration modelling}
 
@@
 
+\section{FRF Interpolation Method}
+
+\subsection{FRF Interpolation Method}
+\begin{frame}{FRF Interpolation Method}
+
+\begin{center}
+\textbf{Data driven method}
+
+\textit{Damage localization in bridges via the FRF interpolation method}, by M. Dilena, M.P. Limongelli, A. Morassi
+\end{center}
+
+\pause
+
+\begin{alertblock}{Main hypothesis}
+A concentrated damage reflects
+in a loss of spatial regularity of the vibrational profile of a
+structure, compared with the undamaged state.
+\end{alertblock}
+
+\pause
+
+\underline{Main steps}:
+\begin{itemize}
+\item Frequency Response Function (FRF) computation
+\item Interpolation on the FRF
+\item Error computation
+\end{itemize}
+
+\end{frame}
+
+\subsection{FRF computation}
+\begin{frame}{FRF computation}
+\begin{exampleblock}{Frequency Response Function}
+\begin{center}
+$H = \frac{Y}{F}$
+\end{center}
+$F$: input
+
+$Y$: output
+\end{exampleblock}
+
+\pause
+
+Fourier transform:
+$
+F_n = \sum\limits_{k=1}^N f_k e^{-2i\pi kn/N},
+Y_n = \sum\limits_{k=1}^N y_k e^{-2i\pi kn/N} \ \ \ \ \ n \in \{1 ... N\}
+$
+
+\begin{block}{Estimator}
+\begin{center}
+$H_1(n) = \frac{Y_n}{F_n}$
+\end{center}
+\end{block}
+
+\end{frame}
+
+\subsection{Interpolation}
+\begin{frame}{Interpolation}
+\underline{Cubic polynomial spline interpolation:}
+\begin{itemize}
+\item piecewise continuous curve, passing through each of the values
+\item continuous through to the second derivative
+\end{itemize}
+
+\begin{center}
+\includegraphics[width=5cm]{images/interpolation_spline.png}
+\end{center}
+
+\end{frame}
+
+\subsection{Error computation}
+\begin{frame}{Error computation}
+
+\begin{center}
+\includegraphics[width=6cm]{images/interpolation.png}
+\end{center}
+
+For each sensor $z_l$ at the frequency $f_i$:
+$E(z_l,f_i) = | H_R(z_l,f_i) - H_S(z_l,f_i) |$
+
+\pause
+
+For each sensor:
+$E(z_l) = \sqrt{  \sum\limits_{i=1}^N  E^2(z_l,f_i) }$
+
+\pause
+
+Difference with the reference state:
+$\Delta E(z_l) = E_d(z_l) - E_0(z_l)$
+
+\end{frame}
+
+\subsection{Probability of identification of a damage}
+\begin{frame}{Probability of identification of a damage}
+\begin{center}
+\includegraphics[height=4cm]{images/gaussiennes.png}
+\end{center}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Simulation}
@@
 $
+\end{center}
+\end{exampleblock}
+
+\end{frame}
+
+\begin{frame}{System masses-springs}
+
+\begin{exampleblock}{Stiffness}
+\begin{center}
+$
+K = 
+\begin{pmatrix} 
+k_1 + k_2 & - k_1 \\ 
+- k_1 &\ddots\\ 
+& -k_i & k_i + k_{i+1} & -k_{i+1} \\
+&&&\ddots& -k_n\\
+&&& -k_n & k_n
+\end{pmatrix}
+$
+\end{center}
+\end{exampleblock}
+
+\begin{exampleblock}{Damping: Rayleigh case}
+\begin{center}
+$C = \alpha M + \beta K,\ \ \ \ \ \alpha, \beta \in \mathbb{R}_+$
 \end{center}
@@
 \end{center}
+
+Natural frequencies (Hz):
+0.04,
+0.14,
+0.23,
+0.31,
+0.39,
+0.46,
+0.52,
+0.57,
+0.60,
+0.62
+
 \end{frame}
@@
 \begin{itemize}
+\item More detailed evaluation
 \item Development of a statistical extension of this method

### 2016-12-07 exp.py

@@ -120,7 +120,7 @@ def experience():
 	frf_undamaged = numpy.transpose(parser.get2("FRF_undamaged.txt"))
 
 
-	#frf_damaged = numpy.transpose(main.frf_multiple_capter_simu_damaged("FRF_damaged.txt"))
+	frf_damaged = numpy.transpose(main.frf_multiple_capter_simu_damaged("FRF_damaged.txt"))
 	frf_damaged = numpy.transpose(parser.get2("FRF_damaged.txt"))
 
 	print("*************************\n Average frf calcul \n *************************")
@@ -173,7 +173,7 @@ def experience():
 	plt.legend()
 	plt.show()
 
-	#printAll(ref,inf,sup, frf_undamaged, frf_damaged)
+	printAll(ref,inf,sup, frf_undamaged, frf_damaged)
 	#printInterpolationError(ref,inf,sup,undamaged,damaged)
 	#printAllMoustache(frf_list_ref, frf_undamaged, frf_damaged)
 

### 2016-12-07 main.py

@@ -104,13 +104,16 @@ def frf_multiple_capter_simu_ref(inFile=None, fichier_sampl = "f_sampl_ref.txt")
 
 
 
-def printPerCapter(res,time):
+def printPerCapter(res,time,freq=[1]):
     n = len(res)
+    x = [ ((float(k)/len(res[0]))*freq[0]) for k in range(len(res[0])) ]
+    print(x)
+    print(freq)
     delta = time/n
     #plt.ion()
     for i in range(n):
-        plt.plot(numpy.absolute(res[i]))
-        plt.xlabel("Fequencies")
+        plt.plot(x,numpy.absolute(res[i]))
+        plt.xlabel("Frequencies (Hz)")
         plt.ylabel("FRF")
         #plt.pause(delta)
         #plt.clf()
@@ -140,5 +143,5 @@ def printPerFreq(res,time):
         
 #frf_multiple_capter_simu_ref("FRF_ref_")        
 #frf_multiple_capter_simu("FRF_damage.txt")
-#printPerCapter(frf_multiple_capter_simu_undamaged(),10)
+printPerCapter(frf_multiple_capter_simu_undamaged(),10, freq = parser.get("f_sampl_undamaged.txt"))
 #printPerCapter2(frf_multiple_capter_simu_damaged(),frf_multiple_capter_simu_undamaged(),10)

### 2016-12-07 simu.py

@@ -20,7 +20,7 @@ from scipy.stats import norm
 CAPTVALUE = 10
 SAMPLVALUE = 100000
 MAKEREF = 10
-DAMAGED_SENSOR = 5
+DAMAGED_SENSOR = [5,6]#must be a list
 DAMAGE = 10
 
 
@@ -128,7 +128,8 @@ def simulation(f, fichier_forces, fichier_acc, fichier_sampl, damaged = None):
 
 #first, we make all matrixes
 	if (damaged != None):
-		stiffness[DAMAGED_SENSOR] = DAMAGE
+		for d in DAMAGED_SENSOR:
+			stiffness[d] = DAMAGE
 
 	N = len(f)
 	n = len(mass)

### 2017-01-12 vecteurs_propres.py
vecteurs_propres

@@ -1,0 +1,124 @@
+import numpy as np
+import math
+import cmath
+import scipy.linalg
+from scipy.stats import norm
+import matplotlib.pyplot as plt
+from simu import *
+from scipy.interpolate import interp1d
+
+
+
+def transpo(m):
+	n = len(m)
+	t = []
+	for i in range(n):
+		c = []
+		for j in range(n):
+			c += [ m[j][i] ]
+		t += [c]
+	return t
+
+#m = [ [1, 2, 3], [4, 5, 6], [7, 8, 9] ]
+#print(m)
+#print(transpo(m))
+
+
+
+
+CAPTVALUE = 8
+SAMPLVALUE = 1000
+MAKEREF = 10
+DAMAGED_SENSOR = [5]#must be a list
+DAMAGE = 70
+
+
+pos = [ k for k in range(CAPTVALUE) ]
+mass = [ 100 for k in range(CAPTVALUE) ]
+stiffness = [ 100 for k in range(CAPTVALUE) ]
+
+
+N = SAMPLVALUE
+n = len(mass)
+M = matrix_M(mass)
+K = matrix_K(stiffness)
+
+print( M )
+print( K )
+
+Minv = np.linalg.inv(M)
+MinvK = np.dot(Minv,K)
+
+eigenvalues, ev = np.linalg.eig(MinvK)
+
+
+frq = []
+for i in eigenvalues:
+		frq += [math.sqrt(abs(i))/(2*math.pi)]
+
+frq = frq[::-1]
+print(frq)
+
+ev = ev[::-1]
+ev = transpo(ev)
+
+
+for x in DAMAGED_SENSOR:
+	stiffness[x] = DAMAGE
+
+N = SAMPLVALUE
+n = len(mass)
+M = matrix_M(mass)
+K = matrix_K(stiffness)
+C = matrix_C(M,K,0.005,0.005)
+
+
+Minv = np.linalg.inv(M)
+MinvK = np.dot(Minv,K)
+
+eigenvalues, ev_damaged = np.linalg.eig(MinvK)
+
+ev_damaged = ev_damaged[::-1]
+ev_damaged = transpo(ev_damaged)
+
+for k in range(len(ev)):
+	plt.plot(pos,ev[k])
+	plt.plot(pos,ev_damaged[k])
+	plt.title("Vecteur " + str(k))
+	plt.show()
+
+
+"""
+for k in range(len(ev)):
[…]

### 2017-01-12 rapport/paper.tex
vecteurs

@@
 \begin{abstract}
-%The surveillance of a structure, as a bridge, with a human presence is something we want automate.
-%A damage identification strategy  is referred as a structural health monitoring (SHM).
-%The SHM can be divided into four levels: detection, localization, quantification and prediction.
-%We present the existing methods for the detection and the localization of damage, then we detail one of them, namely the Frequency Response Function interpolating method.
-%We also analyse this method with a simulation of a spring–mass system.
+For aerospace, civil and mechanical engineering infrastructure, implementing a damage identification strategy is referred as a structural health monitoring.
+With the help of accelerometers, a frequency point of view allows monitoring without the needs of human presence.
+The damage identification can be divided into four levels: detection, localization, quantification and prediction.
+We present the existing methods for the detection and the localization of damage, then we detail one of them, namely the Frequency Response Function interpolating method.
+We also analyse this method with a simulation of a spring–mass system, and discuss the results.
+
 \end{abstract}
@@
 In general, a damage can be observed by comparing two different states of the system,
- one of which is supposed to represent the initial often undamaged state.
+ one of which is supposed to represent the initial, and often undamaged, state.
 
@@
  Most of the time, modal characteristics is the experimental data used for damage assessment through FE model updating.% which are extracted from measured response time histories using modal analysis techniques.
- Different types of modal data can be used.
-For changes in structural stiffness, model updating can be performed based only on natural frequencies or eigenvalues which are known to change in this case.
- Detailed informations about model-based methods can be found in references  %rajouter celles en-dessous
-% C.-P. Fritzen, D. Jennewein, T. Kiefer, (1998). Damage detection based on model updating methods, Mechanical Systems and Signal Processing, 12(1): 163–186.
+Different types of modal data can be used. For changes in structural stiffness, model updating can be performed based only on natural frequencies or eigenvalues which are known to change in this case.
+ Detailed informations about model-based methods can be found in references 
 \cite{fritzen1998damage},
-% Teughels A. and G. De Roeck. (2005). Damage detection and parameter identification by finite element model updating. Archives of Computational Methods in Engineering, 12(2):123-164.
-\cite{teughels2005damage} and
-% Simoen E., De Roeck G., and Lombaert G. (2015). Dealing with uncertainty in model updating for damage assessment: a review. Mechanical Systems and Signal Processing, 56-57:123-149.
-\cite{simoen2015dealing}.
+\cite{simoen2015dealing} and
+\cite{teughels2005damage}.
 
@@
 
-A detailled analysis of the statistical behaviour of the interpolation error is envisaged in the second part of this project.
+A detailed analysis of the statistical behaviour of the interpolation error is envisaged in the second part of this project.
 
@@
 In this paper, we presented the structure heatlh monitoring and a state of the art for this.
-Then we detailled one of the methods, the FRF interpolation method, and some physical models.
+Then we detailed one of the methods, the FRF interpolation method, and some physical models.
 Last, we presented our simulation with a sping-mass system and our results with the implementation of the FRF interpolation method.
@@
 
-In the second part of this project, we will do a detailled analysis of the statistical behaviour of the interpolation error.
+In the second part of this project, we will do a detailed analysis of the statistical behaviour of the interpolation error.
 

### 2017-01-12 exp.py

@@ -23,7 +23,7 @@ DAMAGE = simu.DAMAGE
 ###########################     Print functions    ########################################
 ###########################################################################################
 
-indices = [399, 386, 364, 334, 296, 252, 202, 147, 90, 30]
+#indices = [399, 386, 364, 334, 296, 252, 202, 147, 90, 30] for 10
 
 
 
@@ -144,16 +144,16 @@ def experience():
 
 	#printRef(ref,inf,sup)
 
-	error_ref = interpolation.global_error([ref[i] for i in indices])
-	error_undamaged = interpolation.global_error([frf_undamaged[i] for i in indices])
-	error_damaged = interpolation.global_error([frf_damaged[i] for i in indices])
+	error_ref = interpolation.global_error(ref)
+	error_undamaged = interpolation.global_error(frf_undamaged)
+	error_damaged = interpolation.global_error(frf_damaged)
 
 
-	undamaged = [0 for i in range(nb_sensor) ]
-	damaged = [0 for i in range(nb_sensor) ]
-	for i in range(nb_sensor):
-		undamaged[i] = error_undamaged[i] - error_ref[i]
-		damaged[i] = error_damaged[i] - error_ref[i]
+	undamaged = [0 for i in range(nb_sensor-4) ]
+	damaged = [0 for i in range(nb_sensor-4) ]
+	for i in range(2,nb_sensor-2):
+		undamaged[i-2] = error_undamaged[i] - error_ref[i]
+		damaged[i-2] = error_damaged[i] - error_ref[i]
 
 	print("*************************\n Errors \n *************************")
 	#print("Error ref: ")
@@ -172,8 +172,15 @@ def experience():
 	plt.xlabel("Global error")
 	plt.legend()
 	plt.show()
+	
+	
+	erreur_brut = interpolation.diff_with_ref(frf_damaged, ref)
+	plt.plot(erreur_brut)
+	plt.xlabel("Erreur brute")
+	plt.legend()
+	plt.show()
 
-	printAll(ref,inf,sup, frf_undamaged, frf_damaged)
+	#printAll(ref,inf,sup, frf_undamaged, frf_damaged)
 	#printInterpolationError(ref,inf,sup,undamaged,damaged)
 	#printAllMoustache(frf_list_ref, frf_undamaged, frf_damaged)
 

### 2017-01-12 interpolation.py

@@ -34,7 +34,7 @@ DAMAGE = simu.DAMAGE
 #sortie: liste des erreurs au carre (une erreur par capteur)
 def interpolation_error(complex_list):
 	n = len(complex_list)
-	x_list = [k for k in range(n)]
+	x_list = [k for k in range(n)]# attention: la liste des positions, ne fonctionne ici que s'il y a equidistance
 	error_list = []
 	exc = 0
 	for i in range(n):
@@ -53,6 +53,31 @@ def interpolation_error(complex_list):
 	#print(exc)
 	return error_list
 
+
+
+def interpolation_error_by_2(complex_list):
+	n = len(complex_list)
+	x_list = [k for k in range(n)]# attention: la liste des positions, ne fonctionne ici que s'il y a equidistance
+	error_list = [ 0 for k in range(n) ]
+	exc = 0
+	for i in range(n-1):
+		x = []
+		y = []
+		for j in range(n):
+			if (j != i and j != i+1):
+				x += [x_list[j]]
+				y += [complex_list[j]]
+		try:
+			f = interp1d(x, y, kind = 'cubic')
+			error_list[i] +=  np.absolute(complex_list[i] - f(i))
+			error_list[i+1] +=  np.absolute(complex_list[i+1] - f(i+1))
+		except:
+			#exc += 1
+			error_list += [ 0 ]
+	#print(exc)
+	return error_list
+
+
 #entree: liste de N listes de m elements ou
 # N = nb de frequences
 # m = nb de capteurs
@@ -69,6 +94,18 @@ def global_error(frf_list):
 			error[i] += interpol[i]**2
 	for i in range(nb_sensor):
 		error[i] = math.sqrt(error[i])
+	return error
+	
+
+
+def diff_with_ref(test,ref):
+	n = len(test[0])#nb de sensor
+	error = [ 0 for k in range(n) ]
+	nb_freq = len(test)
+	for f in range(nb_freq):
+		if f > -1:
+			for i in range(n):
+				error[i] += np.absolute( test[f][i] - ref[f][i] )
 	return error
 
 

### 2017-01-12 main.py

@@ -143,5 +143,5 @@ def printPerFreq(res,time):
         
 #frf_multiple_capter_simu_ref("FRF_ref_")        
 #frf_multiple_capter_simu("FRF_damage.txt")
-printPerCapter(frf_multiple_capter_simu_undamaged(),10, freq = parser.get("f_sampl_undamaged.txt"))
+#printPerCapter(frf_multiple_capter_simu_undamaged(),10, freq = parser.get("f_sampl_undamaged.txt"))
 #printPerCapter2(frf_multiple_capter_simu_damaged(),frf_multiple_capter_simu_undamaged(),10)

### 2017-01-12 simu.py

@@ -17,11 +17,11 @@ from scipy.stats import norm
 
 
 
-CAPTVALUE = 10
+CAPTVALUE = 20
 SAMPLVALUE = 100000
 MAKEREF = 10
-DAMAGED_SENSOR = [5,6]#must be a list
-DAMAGE = 10
+DAMAGED_SENSOR = []#must be a list
+DAMAGE = 90
 
 
 pos = [ k for k in range(CAPTVALUE) ]
@@ -45,8 +45,8 @@ def matrix_K(stiffness):#make the stiffness matrix
 	K = np.diag(stiffness)
 	for i in range(n-1):
 		K[i][i] += stiffness[i+1]
-		K[i+1][i] = stiffness[i+1]
-		K[i][i+1] = stiffness[i+1]
+		K[i+1][i] = - stiffness[i+1]
+		K[i][i+1] = - stiffness[i+1]
 	return K
 
 def matrix_C(M,K,a,b):#make the C matrix

### 2017-01-12 vecteurs_propres.py

@@ -43,8 +43,8 @@ n = len(mass)
 M = matrix_M(mass)
 K = matrix_K(stiffness)
 
-print( M )
-print( K )
+#print( M )
+#print( K )
 
 Minv = np.linalg.inv(M)
 MinvK = np.dot(Minv,K)
@@ -57,7 +57,7 @@ for i in eigenvalues:
 		frq += [math.sqrt(abs(i))/(2*math.pi)]
 
 frq = frq[::-1]
-print(frq)
+#print(frq)
 
 ev = ev[::-1]
 ev = transpo(ev)
@@ -80,15 +80,17 @@ eigenvalues, ev_damaged = np.linalg.eig(MinvK)
 
 ev_damaged = ev_damaged[::-1]
 ev_damaged = transpo(ev_damaged)
-
+"""
 for k in range(len(ev)):
 	plt.plot(pos,ev[k])
 	plt.plot(pos,ev_damaged[k])
 	plt.title("Vecteur " + str(k))
 	plt.show()
-
-
 """
+
+error = [ 0 for k in range(len(ev)) ]
+error_damaged = [ 0 for k in range(len(ev)) ]
+
 for k in range(len(ev)):
 	for i in range(len(ev[k]))[1:-1]:
 		x = []
@@ -99,7 +101,7 @@ for k in range(len(ev)):
 				x += [pos[j]]
 				y += [ev[k][j]]
 				yd += [ev_damaged[k][j]]
-		print(y)
+		#print(y)
 		f = interp1d(x, y, kind = 'cubic')
 		g = interp1d(x, yd, kind = 'cubic')
 		v_int = f( pos[i] )
@@ -113,12 +115,25 @@ for k in range(len(ev)):
 			else:
 				y += [v_int]
 				yd += [v_int_damaged]
-		plt.subplot(121)
-		plt.plot(pos,ev[k])
-		plt.plot(pos,y)
-		plt.subplot(122)
-		plt.plot(pos,ev_damaged[k])
-		plt.plot(pos,yd)
-		plt.show()
-"""
+		error[i] += abs(v_int - ev[k][i])
+		error_damaged[i] += abs(v_int_damaged - ev[k][i])
+		#plt.subplot(121)
+		#plt.plot(pos,ev[k])
+		#plt.plot(pos,y)
+		#plt.subplot(122)
+		#plt.plot(pos,ev_damaged[k])
+		#plt.plot(pos,yd)
+		#plt.show()
+
+diff = error_damaged
[…]

### 2017-03-09 rapport/paper.tex
code solo

@@
 
-A detailed analysis of the statistical behaviour of the interpolation error is envisaged in the second part of this project.
+\subsection{A variant of the method}
+
+We propose here a variant of the FRF interpolation method.
+While we have worked on the implementation of the original method, we have observed the eigenvectors of the matrix $M^{-1}K$ (see part III), which have similar properties than the FRF.
+We noticed that the following method is better than the interpolation method (compute the interpolation error, then compute a difference) to detect damaged on the eigenvectors:
+\begin{itemize}
+\item first, compute the difference between the eigenvectors
+\item second, compute the interpolation error on this difference
+\end{itemize}
+
+Thus, we also study in this paper a variant of the FRF interpolation method . The only difference with the original method is the order of the steps:
+\begin{itemize}
+\item Compute the FRF
+\item Compute the difference between the FRF of reference and the FRF of the studied state, for each frequency
+\item Compute the interpolation error of these differencies
+\item Compute the sum of the interpolation errors at each frequency
+\end{itemize}
+
+From now on, to tell the difference between the two methods, we shall call our variant the FRF difference method.
 
@@
 
-\subsection{Results}
+\section{Results}
 
@@
 We put a sensor on each mass.
-For the damaged state, we lower the stifness of the spring between sensors 4 and 5 by 90\%.
+For the damaged state, we lower the stifness of the spring between sensors 6 and 7.
 The values of the FRF on the figures are the norm of the FRF values.
 
+\subsection{FRF results}
+
 Figure (\ref{frf_freq}) presents results of the FRF on the simulation datas: here is the curve of the FRF of one sensor, against frequencies.
-We can see three peaks which are at the natural frequencies of the system, but there is one of these frequencies which not present a peak.
-Seeing this curve for each sensor, we observed that certain sensors have one peak for each natural frequencies, and others sensors have one peak for each except one, relied on the position of the sensor in the system.
-It is problematic because it is around the natural frequencies of the system that we have better datas, but if certain sensors haven't response with certain frequencies, we could miss out on a damage.
+We can see peaks which are at the natural frequencies of the system, but there is one of these frequencies which not present a peak.
+
+Remake figure.
 
@@
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.3\textwidth]{images/damaged4.png}
-  \caption{FRF values for 10 sensors, at a fixed frequency (damage between sensors 4 and 5}
-  \label{damage}
-\end{figure}
+To test the localization, we have to make a thresold for each sensor.
+We want that a computed error taller than the threshold on one sensor is equivalent to have a damage on this sensor.
+With the FRF interpolation method, we have compute two thresholds from 100 experiments with the undameged state.
+The first is the maximum of the 100 errors computed.
+The second is computed from the statistics of the 100 errors computed: we suppose that the probability of the error follow a normal distribution, and we choose the threshold at 95\% of this distribution.
 
-Figure (\ref{damage}) is the FRF values for the ten sensors (at a fixed frequency).
-Here, we easily can see that there is a damage between the sensors 4 and 5 (as we noticed it).
-However, as the damaged FRF is away from the reference FRF, we can see that there isn't a significant loss of regularity at sensors 4 and 5 (the interpolation error isn't high).
+\subsection{Without noise}
 
-Figure (\ref{damage2}) is the FRF values for the same ten sensors that in Figure (\ref{damage}), with the same damage, at a different frequency.
-Here, we can see a significant loss of regularity at sensors 6 and 8.
-It shows that we have to select the frequencies where we calculate the interpolation error.
-Indeed, an hypothesis is that significant values of the FRF are near to the natural frequencies of the system (that we can see in Figure (\ref{frf_freq})).
+Figure() presents the results of the localization of a damage on sensor 7, without noise.
 
@@
   \centering
-  \includegraphics[width=0.3\textwidth]{images/damaged3.png}
-  \caption{FRF values for 10 sensors, at a fixed frequency (damage between sensors 4 and 5}
-  \label{damage2}
+  \includegraphics[width=0.4\textwidth]{images/detect_curve_without_noise.png}
+  \caption{Damage detection rate against damage (without noise)}
+  \label{detect}
 \end{figure}
-
-Finaly, we can see in Figure (\ref{globalerror}) the global error described in section IV.
-The two first and last values (i.e.
-for sensor 0,1,8 and 9) aren't useful because cubic spline interpolation requires two values on each side of the interpolate value.
-We can see that, if we consider all frequencies for the error calcul, results aren't as we want: here the damaged system has a FRF more regular than the undamaged system.
-A selection of the frequencies is necessary.
 
@@
   \centering
-  \includegraphics[width=0.3\textwidth]{images/globalerror.png}
-  \caption{FRF values for 10 sensors, at a fixed frequency (damage between sensors 4 and 5}
-  \label{globalerror}
+  \includegraphics[width=0.4\textwidth]{images/fp.png}
+  \caption{False positives rate against damage (without noise)}
+  \label{fp}
+\end{figure}
+
+\subsection{With noise}
+
+Figure (\ref{itp_error_noise}) presents the results of the localization of a damage on sensor 7, where noise (5\%) has been add at the measurement.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.4\textwidth]{images/damage_noise_10percent.png}
+  \caption{Error computed for a damage of 10\% on sensor 7}
+  \label{itp_error_noise}
+\end{figure}
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.4\textwidth]{images/detect_curve_with_005noise.png}
+  \caption{}
+  \label{detect_5noise}
+\end{figure}
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.4\textwidth]{images/detect_curve_with_01noise.png}
+  \caption{}
+  \label{detect_10noise}
+\end{figure}
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.4\textwidth]{images/fp_noise005.png}
+  \caption{}
+  \label{fp_5noise}
+\end{figure}
+
+\subsection{Eliminate the false positives}
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.4\textwidth]{images/detect_max_10percent.png}
+  \caption{}
+  \label{detect_max}
 \end{figure}
@@
 Last, we presented our simulation with a sping-mass system and our results with the implementation of the FRF interpolation method.
-
-We saw that we have to do a selection of the frequencies where we calculate the interpolation error.
-
-In the second part of this project, we will do a detailed analysis of the statistical behaviour of the interpolation error.
 

### 2017-03-09 code_solo/all.py

@@ -13,7 +13,7 @@ import print_functions as pr
 import interpolation as itp
 import matplotlib.pyplot as plt
 import parser
-
+import random
 
 ################################################
 ############# variables ########################
@@ -25,16 +25,24 @@ CAPTVALUE = 20
 SAMPLVALUE = 10000
 MAKEREF = 10
 DAMAGED_SENSOR = [13]#must be a list
-EXCITED_SENSOR = 5
-DAMAGE = 30# % of damage
+EXCITED_SENSOR = 0
+DAMAGE = 10# % of damage
 
 pos = [ k for k in range(CAPTVALUE) ]
+z = [ 0 for k in range(CAPTVALUE) ]
 mass = [ 100 for k in range(CAPTVALUE) ]
 
 
 indic = ""
 stiffness_undamaged = [ 100 for k in range(CAPTVALUE) ]
 stiffness_damaged = [ 100 for k in range(CAPTVALUE) ]
+
+
+stiffness_undamaged = [ 50+10*random.randint(1,10) for k in range(CAPTVALUE) ]
+stiffness_damaged = [ stiffness_undamaged[k] for k in range(CAPTVALUE) ]
+
+
+
 
 #for noise
 mean = 0
@@ -145,6 +153,8 @@ def simulation(remake,damage):
 	for x in damage:
 		stiffness_damaged[x] = int(float(stiffness_damaged[x])*float(100-DAMAGE)/100)
 	
+	print(stiffness_damaged)
+	
 	A_damaged, B_damaged, C_useless, D_useless, freq_useless = make_matrices(mass, stiffness_damaged)
 
 	acc = [ [0 for k in range(2*n) ] ]
@@ -173,7 +183,7 @@ def simulation(remake,damage):
 	for i in range(SAMPLVALUE):
 		acc += [ np.dot(A_damaged,acc[-1]) + np.dot(B_damaged,f_damaged[i]) ]
 		measurement_damaged += [ np.dot(C,acc[-2]) + np.dot(D,f_damaged[i]) ]
-	
+	"""
 	f_damaged = []
 	for k in range(MAKEREF):
 		m = []
@@ -183,6 +193,7 @@ def simulation(remake,damage):
 			m += [ np.dot(C,acc[-2]) + np.dot(D,fd[i]) ]
 		measurement_damaged += [m]
 		f_damaged += [fd]
+	"""
 	return measurement_ref, measurement_damaged, f, f_damaged, freq
 	
 ################################################
[…]

### 2017-03-09 code_solo/average.py

@@ -1,0 +1,371 @@
+################################################
+############# import ###########################
+################################################
+
+import numpy as np
+import math
+import cmath
+import scipy.linalg
+from scipy.stats import norm
+import scipy.signal
+import tool
+import print_functions as pr
+import interpolation as itp
+import matplotlib.pyplot as plt
+import parser
+import random
+
+################################################
+############# variables ########################
+################################################
+
+
+
+NB_EXP = 20
+CAPTVALUE = 20
+SAMPLVALUE = 10000
+MAKEREF = 10
+DAMAGED_SENSOR = [13]#must be a list
+EXCITED_SENSOR = 0
+DAMAGE = 5# % of damage
+
+pos = [ k for k in range(CAPTVALUE) ]
+z = [ 0 for k in range(CAPTVALUE) ]
+mass = [ 100 for k in range(CAPTVALUE) ]
+
+
+indic = ""
+stiffness_undamaged = [ 100 for k in range(CAPTVALUE) ]
+stiffness_damaged = [ 100 for k in range(CAPTVALUE) ]
+
+
+#stiffness_undamaged = [ 50+10*random.randint(1,10) for k in range(CAPTVALUE) ]
+#stiffness_damaged = [ stiffness_undamaged[k] for k in range(CAPTVALUE) ]
+
+
+
+
+#for noise
+mean = 0
+standard_deviation = 10
+
+################################################
+############# functions ########################
+################################################
+
+
+def av_std(l):# l = [ [ a1, a2, a3], [a4, a5, a6] ... ]
+	n = len(l)
+	k = len(l[0])
+	av = [ 0 for i in range(k) ]
+	std = [ 0 for i in range(k) ]
+	for i in range(n):
+		for j in range(k):
+			av[j] = av[j] + l[i][j]
+	for i in range(k):
+		av[i] = av[i]/float(n)
+	for i in range(n):
+		for j in range(k):
+			std[j] = std[j] + (l[i][j] - av[j])**2
+	for i in range(k):
+		std[i] = math.sqrt(std[i]/float(n))
+	return av, std
+
+def gauss(av,std,start,end,nb_pts):
+	x = [ start + float((end-start)*k)/nb_pts for k in range(nb_pts)]
[…]

### 2017-03-09 code_solo/average2.py

@@ -1,0 +1,411 @@
+################################################
+############# import ###########################
+################################################
+
+import numpy as np
+import math
+import cmath
+import scipy.linalg
+from scipy.stats import norm
+import scipy.signal
+import tool
+import print_functions as pr
+import interpolation as itp
+import matplotlib.pyplot as plt
+import parser
+import random
+
+################################################
+############# variables ########################
+################################################
+
+
+
+NB_EXP = 20
+CAPTVALUE = 20
+SAMPLVALUE = 10000
+MAKEREF = 10
+DAMAGED_SENSOR = [5]#must be a list
+EXCITED_SENSOR = 0
+DAMAGE = 5# % of damage
+
+pos = [ k for k in range(CAPTVALUE) ]
+z = [ 0 for k in range(CAPTVALUE) ]
+mass = [ 100 for k in range(CAPTVALUE) ]
+
+
+indic = ""
+stiffness_undamaged = [ 100 for k in range(CAPTVALUE) ]
+stiffness_damaged = [ 100 for k in range(CAPTVALUE) ]
+
+
+#stiffness_undamaged = [ 50+10*random.randint(1,10) for k in range(CAPTVALUE) ]
+#stiffness_damaged = [ stiffness_undamaged[k] for k in range(CAPTVALUE) ]
+
+
+
+
+#for noise
+mean = 0
+standard_deviation = 10
+
+################################################
+############# functions ########################
+################################################
+
+
+def av_std(l):# l = [ [ a1, a2, a3], [a4, a5, a6] ... ]
+	n = len(l)
+	k = len(l[0])
+	av = [ 0 for i in range(k) ]
+	std = [ 0 for i in range(k) ]
+	for i in range(n):
+		for j in range(k):
+			av[j] = av[j] + l[i][j]
+	for i in range(k):
+		av[i] = av[i]/float(n)
+	for i in range(n):
+		for j in range(k):
+			std[j] = std[j] + (l[i][j] - av[j])**2
+	for i in range(k):
+		std[i] = math.sqrt(std[i]/float(n))
+	return av, std
+
+def gauss(av,std,start,end,nb_pts):
[…]

### 2017-03-09 code_solo/damage.py

@@ -1,0 +1,305 @@
+################################################
+############# import ###########################
+################################################
+
+import numpy as np
+import math
+import cmath
+import scipy.linalg
+from scipy.stats import norm
+import scipy.signal
+import tool
+import print_functions as pr
+import interpolation as itp
+import matplotlib.pyplot as plt
+import parser
+import random
+
+################################################
+############# variables ########################
+################################################
+
+
+CAPTVALUE = 20
+SAMPLVALUE = 10000
+MAKEREF = 100
+DAMAGED_SENSOR = [7]#must be a list
+EXCITED_SENSOR = 0
+DAMAGE = 10# % of damage
+
+pos = [ k for k in range(CAPTVALUE) ]
+z = [ 0 for k in range(CAPTVALUE) ]
+mass = [ 100 for k in range(CAPTVALUE) ]
+
+
+stiffness_undamaged = [ 100 for k in range(CAPTVALUE) ]
+stiffness_damaged = [ 100 for k in range(CAPTVALUE) ]
+
+
+
+
+#for noise
+mean = 0
+standard_deviation = 10
+
+################################################
+############# functions ########################
+################################################
+
+
+def av_std(l):# l = [ [ a1, a2, a3], [a4, a5, a6] ... ]
+	n = len(l)
+	k = len(l[0])
+	av = [ 0 for i in range(k) ]
+	std = [ 0 for i in range(k) ]
+	for i in range(n):
+		for j in range(k):
+			av[j] = av[j] + l[i][j]
+	for i in range(k):
+		av[i] = av[i]/float(n)
+	for i in range(n):
+		for j in range(k):
+			std[j] = std[j] + (l[i][j] - av[j])**2
+	for i in range(k):
+		std[i] = math.sqrt(std[i]/float(n))
+	return av, std
+
+def gauss(av,std,start,end,nb_pts):
+	x = [ start + float((end-start)*k)/nb_pts for k in range(nb_pts)]
+	g = [ (1/(std*math.sqrt(2*math.pi)))*math.exp(-(x[k] - av)**2/(2*std**2)) for k in range(nb_pts) ]
+	return x, g
+
+def matrix_M(mass):#make the mass matrix
+	return np.diag(mass)
+
[…]

### 2017-03-09 code_solo/damage_inv.py

@@ -1,0 +1,294 @@
+################################################
+############# import ###########################
+################################################
+
+import numpy as np
+import math
+import cmath
+import scipy.linalg
+from scipy.stats import norm
+import scipy.signal
+import tool
+import print_functions as pr
+import interpolation as itp
+import matplotlib.pyplot as plt
+import parser
+import random
+
+################################################
+############# variables ########################
+################################################
+
+
+CAPTVALUE = 20
+SAMPLVALUE = 10000
+MAKEREF = 100
+DAMAGED_SENSOR = [7]#must be a list
+EXCITED_SENSOR = 0
+DAMAGE = 20# % of damage
+
+pos = [ k for k in range(CAPTVALUE) ]
+z = [ 0 for k in range(CAPTVALUE) ]
+mass = [ 100 for k in range(CAPTVALUE) ]
+
+
+indic = ""
+stiffness_undamaged = [ 100 for k in range(CAPTVALUE) ]
+stiffness_damaged = [ 100 for k in range(CAPTVALUE) ]
+
+
+#stiffness_undamaged = [ 80+random.randint(1,40) for k in range(CAPTVALUE) ]
+#stiffness_damaged = [ stiffness_undamaged[k] for k in range(CAPTVALUE) ]
+
+
+
+
+#for noise
+mean = 0
+standard_deviation = 10
+
+################################################
+############# functions ########################
+################################################
+
+
+def av_std(l):# l = [ [ a1, a2, a3], [a4, a5, a6] ... ]
+	n = len(l)
+	k = len(l[0])
+	av = [ 0 for i in range(k) ]
+	std = [ 0 for i in range(k) ]
+	for i in range(n):
+		for j in range(k):
+			av[j] = av[j] + l[i][j]
+	for i in range(k):
+		av[i] = av[i]/float(n)
+	for i in range(n):
+		for j in range(k):
+			std[j] = std[j] + (l[i][j] - av[j])**2
+	for i in range(k):
+		std[i] = math.sqrt(std[i]/float(n))
+	return av, std
+
+def gauss(av,std,start,end,nb_pts):
+	x = [ start + float((end-start)*k)/nb_pts for k in range(nb_pts)]
[…]

### 2017-03-09 code_solo/damage_max.py

@@ -1,0 +1,388 @@
+################################################
+############# import ###########################
+################################################
+
+import numpy as np
+import math
+import cmath
+import scipy.linalg
+from scipy.stats import norm
+import scipy.signal
+import tool
+import print_functions as pr
+import interpolation as itp
+import matplotlib.pyplot as plt
+import parser
+import random
+
+################################################
+############# variables ########################
+################################################
+
+
+CAPTVALUE = 20
+SAMPLVALUE = 10000
+MAKEREF = 100
+DAMAGED_SENSOR = [7]#must be a list
+EXCITED_SENSOR = 0
+DAMAGE = 100# % of damage
+
+pos = [ k for k in range(CAPTVALUE) ]
+z = [ 0 for k in range(CAPTVALUE) ]
+mass = [ 100 for k in range(CAPTVALUE) ]
+
+stiffness_undamaged = [ 100 for k in range(CAPTVALUE) ]
+stiffness_damaged = [ 100 for k in range(CAPTVALUE) ]
+
+#for noise
+mean = 0
+standard_deviation = 10
+
+################################################
+############# functions ########################
+################################################
+
+
+def two_max_ind(tab):
+	if tab[0] > tab[1]:
+		a = 0
+		va = tab[0]
+		b = 1
+		vb = tab[1]
+	else:
+		a = 1
+		va = tab[1]
+		b = 0
+		vb = tab[0]
+	for i in range(2,len(tab)):
+		if tab[i] > vb:
+			if tab[i] > va:
+				b = a
+				a = i
+				vb = va
+				va = tab[i]
+			else:
+				b = i
+				vb = tab[i]
+	return a, b, va, vb
+
+
+
+def av_std(l):# l = [ [ a1, a2, a3], [a4, a5, a6] ... ]
+	n = len(l)
+	k = len(l[0])
+	av = [ 0 for i in range(k) ]
+	std = [ 0 for i in range(k) ]
+	for i in range(n):
+		for j in range(k):
+			av[j] = av[j] + l[i][j]
+	for i in range(k):
+		av[i] = av[i]/float(n)
+	for i in range(n):
+		for j in range(k):
[…]

### 2017-03-09 code_solo/damage_noise.py

@@ -1,0 +1,325 @@
+################################################
+############# import ###########################
+################################################
+
+import numpy as np
+import math
+import cmath
+import scipy.linalg
+from scipy.stats import norm
+import scipy.signal
+import tool
+import print_functions as pr
+import interpolation as itp
+import matplotlib.pyplot as plt
+import parser
+import random
+
+################################################
+############# variables ########################
+################################################
+
+NOISE = 0.1
+CAPTVALUE = 20
+SAMPLVALUE = 10000
+MAKEREF = 100
+DAMAGED_SENSOR = [7]#must be a list
+DAMAGE = 14# % of damage
+
+pos = [ k for k in range(CAPTVALUE) ]
+z = [ 0 for k in range(CAPTVALUE) ]
+mass = [ 100 for k in range(CAPTVALUE) ]
+
+
+stiffness_undamaged = [ 100 for k in range(CAPTVALUE) ]
+stiffness_damaged = [ 100 for k in range(CAPTVALUE) ]
+
+#for noise
+mean = 0
+standard_deviation = 10
+
+################################################
+############# functions ########################
+################################################
+
+
+def av_std(l):# l = [ [ a1, a2, a3], [a4, a5, a6] ... ]
+	n = len(l)
+	k = len(l[0])
+	av = [ 0 for i in range(k) ]
+	std = [ 0 for i in range(k) ]
+	for i in range(n):
+		for j in range(k):
+			av[j] = av[j] + l[i][j]
+	for i in range(k):
+		av[i] = av[i]/float(n)
+	for i in range(n):
+		for j in range(k):
+			std[j] = std[j] + (l[i][j] - av[j])**2
+	for i in range(k):
+		std[i] = math.sqrt(std[i]/float(n))
+	return av, std
+
+def av_std_for_noise(l):# for add noise on measurement, l = [ [ a1, a2, a3], [a4, a5, a6] ... ]
+	n = len(l)
+	k = len(l[0])
+	av = 0
+	std = 0
+	for i in range(n):
+		for j in range(k):
+			av += l[i][j]
+	av = av/float(n)
+	for i in range(n):
+		for j in range(k):
+			std += (l[i][j] - av)**2
[…]

### 2017-03-09 code_solo/damage_noise_max.py

@@ -1,0 +1,366 @@
+################################################
+############# import ###########################
+################################################
+
+import numpy as np
+import math
+import cmath
+import scipy.linalg
+from scipy.stats import norm
+import scipy.signal
+import tool
+import print_functions as pr
+import interpolation as itp
+import matplotlib.pyplot as plt
+import parser
+import random
+
+################################################
+############# variables ########################
+################################################
+
+NOISE = 0.05
+CAPTVALUE = 20
+SAMPLVALUE = 10000
+MAKEREF = 100
+DAMAGED_SENSOR = [7]#must be a list
+DAMAGE = 30# % of damage
+
+pos = [ k for k in range(CAPTVALUE) ]
+z = [ 0 for k in range(CAPTVALUE) ]
+mass = [ 100 for k in range(CAPTVALUE) ]
+
+
+stiffness_undamaged = [ 100 for k in range(CAPTVALUE) ]
+stiffness_damaged = [ 100 for k in range(CAPTVALUE) ]
+
+#for noise
+mean = 0
+standard_deviation = 10
+
+################################################
+############# functions ########################
+################################################
+
+
+def two_max_ind(tab):
+	if tab[0] > tab[1]:
+		a = 0
+		va = tab[0]
+		b = 1
+		vb = tab[1]
+	else:
+		a = 1
+		va = tab[1]
+		b = 0
+		vb = tab[0]
+	for i in range(2,len(tab)):
+		if tab[i] > vb:
+			if tab[i] > va:
+				b = a
+				a = i
+				vb = va
+				va = tab[i]
+			else:
+				b = i
+				vb = tab[i]
+	return a, b
+
+
+
+
+def av_std(l):# l = [ [ a1, a2, a3], [a4, a5, a6] ... ]
+	n = len(l)
+	k = len(l[0])
+	av = [ 0 for i in range(k) ]
+	std = [ 0 for i in range(k) ]
+	for i in range(n):
+		for j in range(k):
+			av[j] = av[j] + l[i][j]
+	for i in range(k):
+		av[i] = av[i]/float(n)
+	for i in range(n):
+		for j in range(k):
+			std[j] = std[j] + (l[i][j] - av[j])**2
+	for i in range(k):
[…]

### 2017-03-09 code_solo/data/detect.py

@@ -1,0 +1,31 @@
+import parser as pa
+import matplotlib.pyplot as plt
+
+error = [1, 2, 3, 4, 5, 10, 20, 30]
+
+DAMAGED_SENSOR = 7
+
+maxi, gauss, maxi_inv, gauss_inv = [], [], [], []
+
+for e in error:
+	t_maxi = pa.get3("detect_damage_1_" + str(e) + "percent.txt")
+	t_gauss = pa.get3("detect_damage_2_" + str(e) + "percent.txt")
+	t_maxi_inv = pa.get3("detect_damage_1_inv_" + str(e) + "percent.txt")
+	t_gauss_inv = pa.get3("detect_damage_2_inv_" + str(e) + "percent.txt")
+
+	maxi += [ t_maxi[DAMAGED_SENSOR] ]
+	gauss += [ t_gauss[DAMAGED_SENSOR] ]
+	maxi_inv += [ t_maxi_inv[DAMAGED_SENSOR] ]
+	gauss_inv += [ t_gauss_inv[DAMAGED_SENSOR] ]
+
+
+plt.plot(error, maxi, label = 'Maxi')
+plt.plot(error, gauss, label = 'Gauss')
+plt.plot(error, maxi_inv, label = 'Maxi inv')
+plt.plot(error, gauss_inv, label = 'Gauss inv')
+plt.xlabel("Percent of damage")
+plt.ylabel("Percent of localization")
+plt.legend()
+plt.show()
+
+

### 2017-03-09 code_solo/data/detect_noise.py

@@ -1,0 +1,42 @@
+import parser as pa
+import matplotlib.pyplot as plt
+
+
+DAMAGED_SENSOR = 7
+
+#NOISE = 0.05
+#error = [0,2,3,4,5,6,8,10,20]
+
+NOISE = 0.1
+error = [2,3,4,5,7,8,9,10,12,14,15,20]
+
+
+def tp(t):
+	return max(t[DAMAGED_SENSOR-1], t[DAMAGED_SENSOR])
+
+
+maxi, gauss, maxi_inv, gauss_inv = [], [], [], []
+
+for e in error:
+	t_maxi = pa.get3("detect_damage_1_" + str(e) + "percent_noise"+str(NOISE)+".txt")
+	t_gauss = pa.get3("detect_damage_2_" + str(e) + "percent_noise"+str(NOISE)+".txt")
+	t_maxi_inv = pa.get3("detect_damage_1_inv_" + str(e) + "percent_noise"+str(NOISE)+".txt")
+	t_gauss_inv = pa.get3("detect_damage_2_inv_" + str(e) + "percent_noise"+str(NOISE)+".txt")
+
+	maxi += [ tp(t_maxi) ]
+	gauss += [ tp(t_gauss) ]
+	maxi_inv += [ tp(t_maxi_inv) ]
+	gauss_inv += [ tp(t_gauss_inv) ]
+
+
+plt.plot(error, maxi, label = 'Maxi')
+plt.plot(error, gauss, label = 'Gauss')
+plt.plot(error, maxi_inv, label = 'Maxi inv')
+plt.plot(error, gauss_inv, label = 'Gauss inv')
+plt.xlabel("Percent of damage")
+plt.ylabel("Percent of localization")
+plt.title("Noise: " + str(NOISE))
+plt.legend()
+plt.show()
+
+

### 2017-03-09 code_solo/data/detect_noise2.py

@@ -1,0 +1,38 @@
+import parser as pa
+import matplotlib.pyplot as plt
+
+noise = [0.05,0.1,0.2]
+
+DAMAGED_SENSOR = 7
+#NOISE = 0.05
+DAMAGE = 10#percent of damage
+
+def tp(t):
+	return max(t[DAMAGED_SENSOR-1], t[DAMAGED_SENSOR])
+
+
+maxi, gauss, maxi_inv, gauss_inv = [], [], [], []
+
+for n in noise:
+	t_maxi = pa.get3("detect_damage_1_" + str(DAMAGE) + "percent_noise"+str(n)+".txt")
+	t_gauss = pa.get3("detect_damage_2_" + str(DAMAGE) + "percent_noise"+str(n)+".txt")
+	t_maxi_inv = pa.get3("detect_damage_1_inv_" + str(DAMAGE) + "percent_noise"+str(n)+".txt")
+	t_gauss_inv = pa.get3("detect_damage_2_inv_" + str(DAMAGE) + "percent_noise"+str(n)+".txt")
+
+	maxi += [ tp(t_maxi) ]
+	gauss += [ tp(t_gauss) ]
+	maxi_inv += [ tp(t_maxi_inv) ]
+	gauss_inv += [ tp(t_gauss_inv) ]
+
+
+plt.plot(noise, maxi, label = 'Maxi')
+plt.plot(noise, gauss, label = 'Gauss')
+plt.plot(noise, maxi_inv, label = 'Maxi inv')
+plt.plot(noise, gauss_inv, label = 'Gauss inv')
+plt.xlabel("Percent of noise")
+plt.ylabel("Percent of localization")
+plt.title("Damage: " + str(DAMAGE) + "%")
+plt.legend()
+plt.show()
+
+

### 2017-03-09 code_solo/data/faux_pos_old.py

@@ -1,0 +1,14 @@
+import parser as pa
+
+t = pa.get3("detect_damage_1_10percent_noise.txt")
+
+s = 0
+for x in t:
+	s += x
+
+if 0:
+	print(float(s)/1800)
+else:
+	print(float( s - 200 ) / 1600)
+
+

### 2017-03-09 code_solo/data/fp.py

@@ -1,0 +1,43 @@
+import parser as pa
+import matplotlib.pyplot as plt
+
+error = [1, 2, 3, 4, 5, 10, 20, 30]
+
+DAMAGED_SENSOR = 7
+
+
+
+def fp(t):
+	n = 0
+	fp = 0
+	for i in range(len(t)):
+		if (i < DAMAGED_SENSOR - 2 or i > DAMAGED_SENSOR + 2):
+			n += 1
+			fp += t[i]
+	return float(fp)/n
+
+
+maxi, gauss, maxi_inv, gauss_inv = [], [], [], []
+
+for e in error:
+	t_maxi = pa.get3("detect_damage_1_" + str(e) + "percent.txt")
+	t_gauss = pa.get3("detect_damage_2_" + str(e) + "percent.txt")
+	t_maxi_inv = pa.get3("detect_damage_1_inv_" + str(e) + "percent.txt")
+	t_gauss_inv = pa.get3("detect_damage_2_inv_" + str(e) + "percent.txt")
+
+	maxi += [ fp(t_maxi) ]
+	gauss += [ fp(t_gauss) ]
+	maxi_inv += [ fp(t_maxi_inv) ]
+	gauss_inv += [ fp(t_gauss_inv) ]
+
+
+plt.plot(error, maxi, label = 'Maxi')
+plt.plot(error, gauss, label = 'Gauss')
+plt.plot(error, maxi_inv, label = 'Maxi inv')
+plt.plot(error, gauss_inv, label = 'Gauss inv')
+plt.xlabel("Percent of damage")
+plt.ylabel("Percent of false positif")
+plt.legend()
+plt.show()
+
+

### 2017-03-09 code_solo/data/fp_noise.py

@@ -1,0 +1,44 @@
+import parser as pa
+import matplotlib.pyplot as plt
+
+
+error = [0,2,3,4,5,10,20]
+
+DAMAGED_SENSOR = 7
+NOISE = 0.05
+
+
+def fp(t):
+	n = 0
+	fp = 0
+	for i in range(len(t)):
+		if (i < DAMAGED_SENSOR - 2 or i > DAMAGED_SENSOR + 2):
+			n += 1
+			fp += t[i]
+	return float(fp)/n
+
+
+maxi, gauss, maxi_inv, gauss_inv = [], [], [], []
+
+for e in error:
+	t_maxi = pa.get3("detect_damage_1_" + str(e) + "percent_noise"+str(NOISE)+".txt")
+	t_gauss = pa.get3("detect_damage_2_" + str(e) + "percent_noise"+str(NOISE)+".txt")
+	t_maxi_inv = pa.get3("detect_damage_1_inv_" + str(e) + "percent_noise"+str(NOISE)+".txt")
+	t_gauss_inv = pa.get3("detect_damage_2_inv_" + str(e) + "percent_noise"+str(NOISE)+".txt")
+
+	maxi += [ fp(t_maxi) ]
+	gauss += [ fp(t_gauss) ]
+	maxi_inv += [ fp(t_maxi_inv) ]
+	gauss_inv += [ fp(t_gauss_inv) ]
+
+
+plt.plot(error, maxi, label = 'Maxi')
+plt.plot(error, gauss, label = 'Gauss')
+plt.plot(error, maxi_inv, label = 'Maxi inv')
+plt.plot(error, gauss_inv, label = 'Gauss inv')
+plt.xlabel("Percent of damage")
+plt.ylabel("Percent of false positif")
+plt.legend()
+plt.show()
+
+

### 2017-03-09 code_solo/data/quantification.py

@@ -1,0 +1,36 @@
+import parser
+import matplotlib.pyplot as plt
+
+
+DAMAGED_SENSOR = 7
+
+#NOISE = 0.05
+#error = [0,2,3,4,5,6,8,10,20]
+
+NOISE = 0.1
+damage = [0,5,10,20,30,40,50,60,70,80,90,100]
+
+NOISE = 0
+
+q1, q2, q1_inv, q2_inv = [], [], [], []
+
+
+for DAMAGE in damage:
+	d1 = parser.get3("quantification1_"+str(DAMAGE)+"damage_"+str(NOISE)+"noise.txt")
+	d2 = parser.get3("quantification2_"+str(DAMAGE)+"damage_"+str(NOISE)+"noise.txt")
+	d1_inv = parser.get3("quantification1_inv_"+str(DAMAGE)+"damage_"+str(NOISE)+"noise.txt")
+	d2_inv = parser.get3("quantification2_inv_"+str(DAMAGE)+"damage_"+str(NOISE)+"noise.txt")
+	q1 += [max(d1[DAMAGED_SENSOR],d1[DAMAGED_SENSOR-1])]
+	q2 += [max(d2[DAMAGED_SENSOR],d2[DAMAGED_SENSOR-1])]
+	q1_inv += [max(d1_inv[DAMAGED_SENSOR],d1_inv[DAMAGED_SENSOR-1])]
+	q2_inv += [max(d2_inv[DAMAGED_SENSOR],d2_inv[DAMAGED_SENSOR-1])]
+
+plt.plot(damage, q1, label = 'Maxi')
+plt.plot(damage, q2, label = 'Gauss')
+plt.plot(damage, q1_inv, label = 'Maxi inv')
+plt.plot(damage, q2_inv, label = 'Gauss inv')
+plt.xlabel("Percent of damage")
+plt.ylabel("difference")
+plt.title("Quantification")
+plt.legend()
+plt.show()

### 2017-03-09 code_solo/display_frf.py

@@ -1,0 +1,273 @@
+################################################
+############# import ###########################
+################################################
+
+import numpy as np
+import math
+import cmath
+import scipy.linalg
+from scipy.stats import norm
+import scipy.signal
+import tool
+import print_functions as pr
+import interpolation as itp
+import matplotlib.pyplot as plt
+import parser
+import random
+
+################################################
+############# variables ########################
+################################################
+
+
+CAPTVALUE = 5
+SAMPLVALUE = 10000
+DAMAGED_SENSOR = []#must be a list
+DAMAGE = 0# % of damage
+
+pos = [ k for k in range(CAPTVALUE) ]
+z = [ 0 for k in range(CAPTVALUE) ]
+mass = [ 100 for k in range(CAPTVALUE) ]
+
+
+stiffness_undamaged = [ 100 for k in range(CAPTVALUE) ]
+stiffness_damaged = [ 100 for k in range(CAPTVALUE) ]
+
+#for noise
+mean = 0
+standard_deviation = 10
+
+################################################
+############# functions ########################
+################################################
+
+
+def av_std(l):# l = [ [ a1, a2, a3], [a4, a5, a6] ... ]
+	n = len(l)
+	k = len(l[0])
+	av = [ 0 for i in range(k) ]
+	std = [ 0 for i in range(k) ]
+	for i in range(n):
+		for j in range(k):
+			av[j] = av[j] + l[i][j]
+	for i in range(k):
+		av[i] = av[i]/float(n)
+	for i in range(n):
+		for j in range(k):
+			std[j] = std[j] + (l[i][j] - av[j])**2
+	for i in range(k):
+		std[i] = math.sqrt(std[i]/float(n))
+	return av, std
+
+def gauss(av,std,start,end,nb_pts):
+	x = [ start + float((end-start)*k)/nb_pts for k in range(nb_pts)]
+	g = [ (1/(std*math.sqrt(2*math.pi)))*math.exp(-(x[k] - av)**2/(2*std**2)) for k in range(nb_pts) ]
+	return x, g
+
+def matrix_M(mass):#make the mass matrix
+	return np.diag(mass)
+
+def matrix_K(stiffness):#make the stiffness matrix
+	n = len(stiffness)
+	K = np.zeros((n,n))
+	for i in range(n-1):
+		K[i][i] += stiffness[i+1]
+		K[i+1][i+1] += stiffness[i+1]
[…]

### 2017-03-09 code_solo/localization.py

@@ -1,0 +1,297 @@
+################################################
+############# import ###########################
+################################################
+
+import numpy as np
+import math
+import cmath
+import scipy.linalg
+from scipy.stats import norm
+import scipy.signal
+import tool
+import print_functions as pr
+import interpolation as itp
+import matplotlib.pyplot as plt
+import parser
+import random
+
+################################################
+############# variables ########################
+################################################
+
+
+
+NB_EXP = 20
+CAPTVALUE = 40
+SAMPLVALUE = 10000
+MAKEREF = 10
+DAMAGED_SENSOR = [13]#must be a list
+EXCITED_SENSOR = 0
+DAMAGE = 2# % of damage
+
+pos = [ k for k in range(CAPTVALUE) ]
+z = [ 0 for k in range(CAPTVALUE) ]
+mass = [ 100 for k in range(CAPTVALUE) ]
+
+
+indic = ""
+stiffness_undamaged = [ 100 for k in range(CAPTVALUE) ]
+stiffness_damaged = [ 100 for k in range(CAPTVALUE) ]
+
+
+#stiffness_undamaged = [ 80+random.randint(1,40) for k in range(CAPTVALUE) ]
+#stiffness_damaged = [ stiffness_undamaged[k] for k in range(CAPTVALUE) ]
+
+
+
+
+#for noise
+mean = 0
+standard_deviation = 10
+
+################################################
+############# functions ########################
+################################################
+
+
+def av_std(l):# l = [ [ a1, a2, a3], [a4, a5, a6] ... ]
+	n = len(l)
+	k = len(l[0])
+	av = [ 0 for i in range(k) ]
+	std = [ 0 for i in range(k) ]
+	for i in range(n):
+		for j in range(k):
+			av[j] = av[j] + l[i][j]
+	for i in range(k):
+		av[i] = av[i]/float(n)
+	for i in range(n):
+		for j in range(k):
+			std[j] = std[j] + (l[i][j] - av[j])**2
+	for i in range(k):
+		std[i] = math.sqrt(std[i]/float(n))
+	return av, std
+
+def gauss(av,std,start,end,nb_pts):
+	x = [ start + float((end-start)*k)/nb_pts for k in range(nb_pts)]
[…]

### 2017-03-09 code_solo/threshold1.py

@@ -1,0 +1,288 @@
+################################################
+############# import ###########################
+################################################
+
+import numpy as np
+import math
+import cmath
+import scipy.linalg
+from scipy.stats import norm
+import scipy.signal
+import tool
+import print_functions as pr
+import interpolation as itp
+import matplotlib.pyplot as plt
+import parser
+import random
+
+################################################
+############# variables ########################
+################################################
+
+
+CAPTVALUE = 20
+SAMPLVALUE = 10000
+MAKEREF = 100
+DAMAGED_SENSOR = [7]#must be a list
+EXCITED_SENSOR = 0
+DAMAGE = 0# % of damage
+
+pos = [ k for k in range(CAPTVALUE) ]
+z = [ 0 for k in range(CAPTVALUE) ]
+mass = [ 100 for k in range(CAPTVALUE) ]
+
+
+indic = ""
+stiffness_undamaged = [ 100 for k in range(CAPTVALUE) ]
+stiffness_damaged = [ 100 for k in range(CAPTVALUE) ]
+
+
+#stiffness_undamaged = [ 80+random.randint(1,40) for k in range(CAPTVALUE) ]
+#stiffness_damaged = [ stiffness_undamaged[k] for k in range(CAPTVALUE) ]
+
+
+
+
+#for noise
+mean = 0
+standard_deviation = 10
+
+################################################
+############# functions ########################
+################################################
+
+
+def av_std(l):# l = [ [ a1, a2, a3], [a4, a5, a6] ... ]
+	n = len(l)
+	k = len(l[0])
+	av = [ 0 for i in range(k) ]
+	std = [ 0 for i in range(k) ]
+	for i in range(n):
+		for j in range(k):
+			av[j] = av[j] + l[i][j]
+	for i in range(k):
+		av[i] = av[i]/float(n)
+	for i in range(n):
+		for j in range(k):
+			std[j] = std[j] + (l[i][j] - av[j])**2
+	for i in range(k):
+		std[i] = math.sqrt(std[i]/float(n))
+	return av, std
+
+def gauss(av,std,start,end,nb_pts):
+	x = [ start + float((end-start)*k)/nb_pts for k in range(nb_pts)]
[…]

### 2017-03-09 code_solo/threshold1_inv.py

@@ -1,0 +1,288 @@
+################################################
+############# import ###########################
+################################################
+
+import numpy as np
+import math
+import cmath
+import scipy.linalg
+from scipy.stats import norm
+import scipy.signal
+import tool
+import print_functions as pr
+import interpolation as itp
+import matplotlib.pyplot as plt
+import parser
+import random
+
+################################################
+############# variables ########################
+################################################
+
+
+CAPTVALUE = 20
+SAMPLVALUE = 10000
+MAKEREF = 100
+DAMAGED_SENSOR = [7]#must be a list
+EXCITED_SENSOR = 0
+DAMAGE = 0# % of damage
+
+pos = [ k for k in range(CAPTVALUE) ]
+z = [ 0 for k in range(CAPTVALUE) ]
+mass = [ 100 for k in range(CAPTVALUE) ]
+
+
+indic = ""
+stiffness_undamaged = [ 100 for k in range(CAPTVALUE) ]
+stiffness_damaged = [ 100 for k in range(CAPTVALUE) ]
+
+
+#stiffness_undamaged = [ 80+random.randint(1,40) for k in range(CAPTVALUE) ]
+#stiffness_damaged = [ stiffness_undamaged[k] for k in range(CAPTVALUE) ]
+
+
+
+
+#for noise
+mean = 0
+standard_deviation = 10
+
+################################################
+############# functions ########################
+################################################
+
+
+def av_std(l):# l = [ [ a1, a2, a3], [a4, a5, a6] ... ]
+	n = len(l)
+	k = len(l[0])
+	av = [ 0 for i in range(k) ]
+	std = [ 0 for i in range(k) ]
+	for i in range(n):
+		for j in range(k):
+			av[j] = av[j] + l[i][j]
+	for i in range(k):
+		av[i] = av[i]/float(n)
+	for i in range(n):
+		for j in range(k):
+			std[j] = std[j] + (l[i][j] - av[j])**2
+	for i in range(k):
+		std[i] = math.sqrt(std[i]/float(n))
+	return av, std
+
+def gauss(av,std,start,end,nb_pts):
+	x = [ start + float((end-start)*k)/nb_pts for k in range(nb_pts)]
[…]

### 2017-03-09 code_solo/threshold1_noise.py

@@ -1,0 +1,303 @@
+################################################
+############# import ###########################
+################################################
+
+import numpy as np
+import math
+import cmath
+import scipy.linalg
+from scipy.stats import norm
+import scipy.signal
+import tool
+import print_functions as pr
+import interpolation as itp
+import matplotlib.pyplot as plt
+import parser
+import random
+
+################################################
+############# variables ########################
+################################################
+
+
+CAPTVALUE = 20
+SAMPLVALUE = 10000
+MAKEREF = 100
+DAMAGED_SENSOR = [7]#must be a list
+EXCITED_SENSOR = 0
+DAMAGE = 0# % of damage
+
+pos = [ k for k in range(CAPTVALUE) ]
+z = [ 0 for k in range(CAPTVALUE) ]
+mass = [ 100 for k in range(CAPTVALUE) ]
+
+
+indic = ""
+stiffness_undamaged = [ 100 for k in range(CAPTVALUE) ]
+stiffness_damaged = [ 100 for k in range(CAPTVALUE) ]
+
+
+#for noise (entry)
+mean = 0
+standard_deviation = 10
+
+################################################
+############# functions ########################
+################################################
+
+
+def av_std(l):# l = [ [ a1, a2, a3], [a4, a5, a6] ... ]
+	n = len(l)
+	k = len(l[0])
+	av = [ 0 for i in range(k) ]
+	std = [ 0 for i in range(k) ]
+	for i in range(n):
+		for j in range(k):
+			av[j] = av[j] + l[i][j]
+	for i in range(k):
+		av[i] = av[i]/float(n)
+	for i in range(n):
+		for j in range(k):
+			std[j] = std[j] + (l[i][j] - av[j])**2
+	for i in range(k):
+		std[i] = math.sqrt(std[i]/float(n))
+	return av, std
+
+
+def av_std_for_noise(l):# for add noise on measurement, l = [ [ a1, a2, a3], [a4, a5, a6] ... ]
+	n = len(l)
+	k = len(l[0])
+	av = 0
+	std = 0
+	for i in range(n):
+		for j in range(k):
+			av += l[i][j]
+	av = av/float(n)
+	for i in range(n):
+		for j in range(k):
+			std += (l[i][j] - av)**2
[…]

### 2017-03-09 code_solo/threshold2.py

@@ -1,0 +1,281 @@
+################################################
+############# import ###########################
+################################################
+
+import numpy as np
+import math
+import cmath
+import scipy.linalg
+from scipy.stats import norm
+import scipy.signal
+import tool
+import print_functions as pr
+import interpolation as itp
+import matplotlib.pyplot as plt
+import parser
+import random
+
+################################################
+############# variables ########################
+################################################
+
+
+
+CAPTVALUE = 20
+SAMPLVALUE = 10000
+MAKEREF = 100
+DAMAGED_SENSOR = [13]#must be a list
+EXCITED_SENSOR = 0
+DAMAGE = 0# % of damage
+
+pos = [ k for k in range(CAPTVALUE) ]
+z = [ 0 for k in range(CAPTVALUE) ]
+mass = [ 100 for k in range(CAPTVALUE) ]
+
+
+indic = ""
+stiffness_undamaged = [ 100 for k in range(CAPTVALUE) ]
+stiffness_damaged = [ 100 for k in range(CAPTVALUE) ]
+
+
+#stiffness_undamaged = [ 80+random.randint(1,40) for k in range(CAPTVALUE) ]
+#stiffness_damaged = [ stiffness_undamaged[k] for k in range(CAPTVALUE) ]
+
+
+
+
+#for noise
+mean = 0
+standard_deviation = 10
+
+################################################
+############# functions ########################
+################################################
+
+
+def av_std(l):# l = [ [ a1, a2, a3], [a4, a5, a6] ... ]
+	n = len(l)
+	k = len(l[0])
+	av = [ 0 for i in range(k) ]
+	std = [ 0 for i in range(k) ]
+	for i in range(n):
+		for j in range(k):
+			av[j] = av[j] + l[i][j]
+	for i in range(k):
+		av[i] = av[i]/float(n)
+	for i in range(n):
+		for j in range(k):
+			std[j] = std[j] + (l[i][j] - av[j])**2
+	for i in range(k):
+		std[i] = math.sqrt(std[i]/float(n))
+	return av, std
+
+def gauss(av,std,start,end,nb_pts):
+	x = [ start + float((end-start)*k)/nb_pts for k in range(nb_pts)]
[…]

### 2017-03-09 code_solo/threshold2_inv.py

@@ -1,0 +1,281 @@
+################################################
+############# import ###########################
+################################################
+
+import numpy as np
+import math
+import cmath
+import scipy.linalg
+from scipy.stats import norm
+import scipy.signal
+import tool
+import print_functions as pr
+import interpolation as itp
+import matplotlib.pyplot as plt
+import parser
+import random
+
+################################################
+############# variables ########################
+################################################
+
+
+
+CAPTVALUE = 20
+SAMPLVALUE = 10000
+MAKEREF = 100
+DAMAGED_SENSOR = [13]#must be a list
+EXCITED_SENSOR = 0
+DAMAGE = 0# % of damage
+
+pos = [ k for k in range(CAPTVALUE) ]
+z = [ 0 for k in range(CAPTVALUE) ]
+mass = [ 100 for k in range(CAPTVALUE) ]
+
+
+indic = ""
+stiffness_undamaged = [ 100 for k in range(CAPTVALUE) ]
+stiffness_damaged = [ 100 for k in range(CAPTVALUE) ]
+
+
+#stiffness_undamaged = [ 80+random.randint(1,40) for k in range(CAPTVALUE) ]
+#stiffness_damaged = [ stiffness_undamaged[k] for k in range(CAPTVALUE) ]
+
+
+
+
+#for noise
+mean = 0
+standard_deviation = 10
+
+################################################
+############# functions ########################
+################################################
+
+
+def av_std(l):# l = [ [ a1, a2, a3], [a4, a5, a6] ... ]
+	n = len(l)
+	k = len(l[0])
+	av = [ 0 for i in range(k) ]
+	std = [ 0 for i in range(k) ]
+	for i in range(n):
+		for j in range(k):
+			av[j] = av[j] + l[i][j]
+	for i in range(k):
+		av[i] = av[i]/float(n)
+	for i in range(n):
+		for j in range(k):
+			std[j] = std[j] + (l[i][j] - av[j])**2
+	for i in range(k):
+		std[i] = math.sqrt(std[i]/float(n))
+	return av, std
+
+def gauss(av,std,start,end,nb_pts):
+	x = [ start + float((end-start)*k)/nb_pts for k in range(nb_pts)]
[…]

### 2017-03-09 code_solo/threshold2_noise.py

@@ -1,0 +1,305 @@
+################################################
+############# import ###########################
+################################################
+
+import numpy as np
+import math
+import cmath
+import scipy.linalg
+from scipy.stats import norm
+import scipy.signal
+import tool
+import print_functions as pr
+import interpolation as itp
+import matplotlib.pyplot as plt
+import parser
+import random
+
+################################################
+############# variables ########################
+################################################
+
+
+
+CAPTVALUE = 20
+SAMPLVALUE = 10000
+MAKEREF = 100
+DAMAGED_SENSOR = [13]#must be a list
+EXCITED_SENSOR = 0
+DAMAGE = 0# % of damage
+
+pos = [ k for k in range(CAPTVALUE) ]
+z = [ 0 for k in range(CAPTVALUE) ]
+mass = [ 100 for k in range(CAPTVALUE) ]
+
+
+indic = ""
+stiffness_undamaged = [ 100 for k in range(CAPTVALUE) ]
+stiffness_damaged = [ 100 for k in range(CAPTVALUE) ]
+
+
+#stiffness_undamaged = [ 80+random.randint(1,40) for k in range(CAPTVALUE) ]
+#stiffness_damaged = [ stiffness_undamaged[k] for k in range(CAPTVALUE) ]
+
+
+
+
+#for noise
+mean = 0
+standard_deviation = 10
+
+################################################
+############# functions ########################
+################################################
+
+
+def av_std(l):# l = [ [ a1, a2, a3], [a4, a5, a6] ... ]
+	n = len(l)
+	k = len(l[0])
+	av = [ 0 for i in range(k) ]
+	std = [ 0 for i in range(k) ]
+	for i in range(n):
+		for j in range(k):
+			av[j] = av[j] + l[i][j]
+	for i in range(k):
+		av[i] = av[i]/float(n)
+	for i in range(n):
+		for j in range(k):
+			std[j] = std[j] + (l[i][j] - av[j])**2
+	for i in range(k):
+		std[i] = math.sqrt(std[i]/float(n))
+	return av, std
+
+
+def av_std_for_noise(l):# for add noise on measurement, l = [ [ a1, a2, a3], [a4, a5, a6] ... ]
+	n = len(l)
+	k = len(l[0])
+	av = 0
+	std = 0
[…]

### 2017-03-09 code_solo/threshold_noise.py

@@ -1,0 +1,325 @@
+################################################
+############# import ###########################
+################################################
+
+import numpy as np
+import math
+import cmath
+import scipy.linalg
+from scipy.stats import norm
+import scipy.signal
+import tool
+import print_functions as pr
+import interpolation as itp
+import matplotlib.pyplot as plt
+import parser
+import random
+
+################################################
+############# variables ########################
+################################################
+
+NOISE = 0.15
+CAPTVALUE = 20
+SAMPLVALUE = 10000
+MAKEREF = 100
+DAMAGED_SENSOR = [7]#must be a list
+EXCITED_SENSOR = 0
+DAMAGE = 0# % of damage
+
+pos = [ k for k in range(CAPTVALUE) ]
+z = [ 0 for k in range(CAPTVALUE) ]
+mass = [ 100 for k in range(CAPTVALUE) ]
+
+
+indic = ""
+stiffness_undamaged = [ 100 for k in range(CAPTVALUE) ]
+stiffness_damaged = [ 100 for k in range(CAPTVALUE) ]
+
+
+#stiffness_undamaged = [ 80+random.randint(1,40) for k in range(CAPTVALUE) ]
+#stiffness_damaged = [ stiffness_undamaged[k] for k in range(CAPTVALUE) ]
+
+
+
+
+#for noise
+mean = 0
+standard_deviation = 10
+
+################################################
+############# functions ########################
+################################################
+
+
+def av_std(l):# l = [ [ a1, a2, a3], [a4, a5, a6] ... ]
+	n = len(l)
+	k = len(l[0])
+	av = [ 0 for i in range(k) ]
+	std = [ 0 for i in range(k) ]
+	for i in range(n):
+		for j in range(k):
+			av[j] = av[j] + l[i][j]
+	for i in range(k):
+		av[i] = av[i]/float(n)
+	for i in range(n):
+		for j in range(k):
+			std[j] = std[j] + (l[i][j] - av[j])**2
+	for i in range(k):
+		std[i] = math.sqrt(std[i]/float(n))
+	return av, std
+
+
+def av_std_for_noise(l):# for add noise on measurement, l = [ [ a1, a2, a3], [a4, a5, a6] ... ]
+	n = len(l)
+	k = len(l[0])
[…]

### 2017-03-09 exp.py

@@ -120,7 +120,7 @@ def experience():
 	frf_undamaged = numpy.transpose(parser.get2("FRF_undamaged.txt"))
 
 
-	frf_damaged = numpy.transpose(main.frf_multiple_capter_simu_damaged("FRF_damaged.txt"))
+	#frf_damaged = numpy.transpose(main.frf_multiple_capter_simu_damaged("FRF_damaged.txt"))
 	frf_damaged = numpy.transpose(parser.get2("FRF_damaged.txt"))
 
 	print("*************************\n Average frf calcul \n *************************")
@@ -155,6 +155,7 @@ def experience():
 		undamaged[i-2] = error_undamaged[i] - error_ref[i]
 		damaged[i-2] = error_damaged[i] - error_ref[i]
 
+	"""
 	print("*************************\n Errors \n *************************")
 	#print("Error ref: ")
 	#print(error_ref)
@@ -166,21 +167,23 @@ def experience():
 	plt.plot(error_undamaged)
 	plt.plot(error_damaged)
 	plt.show()
+	"""
 	
+	"""
 	plt.plot(undamaged, label = "Undamaged")
 	plt.plot(damaged, label = "Damaged")
 	plt.xlabel("Global error")
 	plt.legend()
 	plt.show()
 	
-	
 	erreur_brut = interpolation.diff_with_ref(frf_damaged, ref)
 	plt.plot(erreur_brut)
 	plt.xlabel("Erreur brute")
 	plt.legend()
 	plt.show()
+	"""
 
-	#printAll(ref,inf,sup, frf_undamaged, frf_damaged)
+	printAll(ref,inf,sup, frf_undamaged, frf_damaged)
 	#printInterpolationError(ref,inf,sup,undamaged,damaged)
 	#printAllMoustache(frf_list_ref, frf_undamaged, frf_damaged)
 

### 2017-03-09 interpolation.py

@@ -85,11 +85,8 @@ def interpolation_error_by_2(complex_list):
 def global_error(frf_list):
 	nb_sensor = len(frf_list[0])
 	error = [0 for i in range(nb_sensor) ]
-	#k = 0
-	for frf in frf_list:
-		#k += 1
-		#if (k>350):
-		interpol = interpolation_error(frf)
+	for k in range(len(frf_list)):
+		interpol = interpolation_error(frf_list[k])
 		for i in range(nb_sensor):
 			error[i] += interpol[i]**2
 	for i in range(nb_sensor):

### 2017-03-09 simu.py

@@ -20,8 +20,12 @@ from scipy.stats import norm
 CAPTVALUE = 20
 SAMPLVALUE = 100000
 MAKEREF = 10
-DAMAGED_SENSOR = []#must be a list
+DAMAGED_SENSOR = [7]#must be a list
 DAMAGE = 90
+
+#for noise
+mean = 0
+standard_deviation = 10
 
 
 pos = [ k for k in range(CAPTVALUE) ]
@@ -272,8 +276,6 @@ def simulation(f, fichier_forces, fichier_acc, fichier_sampl, damaged = None):
 
 ##### white noise ######
 
-mean = 0
-standard_deviation = 1
 
 def white_noise(n,nb_sensor):
 	noise = []

### 2017-03-09 simulation/damage.py

@@ -262,27 +262,12 @@ def experience():
 	detect_damage1_inv = [ 0 for k in range(CAPTVALUE) ]
 	detect_damage2_inv = [ 0 for k in range(CAPTVALUE) ]
 	
-	
-	"""
-	detect_damage3 = [ 0 for k in range(CAPTVALUE) ]
-	detect_damage4 = [ 0 for k in range(CAPTVALUE) ]
-	detect_damage5 = [ 0 for k in range(CAPTVALUE) ]
-	detect_damage6 = [ 0 for k in range(CAPTVALUE) ]
-	detect_damage7 = [ 0 for k in range(CAPTVALUE) ]
-	"""
-	
 	threshold1 = parser.get3("data/threshold1.txt")
 	threshold2 = parser.get3("data/threshold2.txt")
 	
 	threshold1_inv = parser.get3("data/threshold1_inv.txt")
 	threshold2_inv = parser.get3("data/threshold2_inv.txt")
-	"""
-	threshold3 = [ 1.1*threshold1[k] for k in range(CAPTVALUE) ]
-	threshold4 = [ 1.2*threshold1[k] for k in range(CAPTVALUE) ]
-	threshold5 = [ 1.3*threshold1[k] for k in range(CAPTVALUE) ]
-	threshold6 = [ 1.5*threshold1[k] for k in range(CAPTVALUE) ]
-	threshold7 = [ 2*threshold1[k] for k in range(CAPTVALUE) ]
-	"""
+
 	for k in range(MAKEREF):
 		print(k)
 		frf_damaged, acc = frf_multiple_sensors(2, acc)
@@ -298,34 +283,13 @@ def experience():
 				detect_damage1_inv[x] = detect_damage1_inv[x] + 1
 			if error_damaged_inv[x] > threshold2_inv[x]:
 				detect_damage2_inv[x] = detect_damage2_inv[x] + 1
-			"""
-			if diff[x] > threshold3[x]:
-				detect_damage3[x] = detect_damage3[x] + 1
-			if diff[x] > threshold4[x]:
-				detect_damage4[x] = detect_damage4[x] + 1
-			if diff[x] > threshold5[x]:
-				detect_damage5[x] = detect_damage5[x] + 1
-			if diff[x] > threshold6[x]:
-				detect_damage6[x] = detect_damage6[x] + 1
-			if diff[x] > threshold7[x]:
-				detect_damage7[x] = detect_damage7[x] + 1
-			"""
+
 	
[…]

### 2017-03-09 vecteurs_propres.py

@@ -6,8 +6,41 @@ from scipy.stats import norm
 import matplotlib.pyplot as plt
 from simu import *
 from scipy.interpolate import interp1d
+import random
+import curve_study as cs
+
+####################################################################################################################
+############################################## Parameters ##########################################################
+####################################################################################################################
+
+CAPTVALUE = 20
+DAMAGED_SENSOR = [2]#must be a list
+DAMAGE = 0.20
 
 
+pos = [ k for k in range(CAPTVALUE) ]
+mass = [ 100 for k in range(CAPTVALUE) ]
+stiffness = [ 100 for k in range(CAPTVALUE) ]
+#mass = [ 100*random.randint(1,5) for k in range(CAPTVALUE) ]
+#stiffness = [ 100*random.randint(1,5) for k in range(CAPTVALUE) ]
+
+
+####################################################################################################################
+############################################## Functions ###########################################################
+####################################################################################################################
+
+
+def matrix_K(stiffness):#make the stiffness matrix
+	n = len(stiffness)
+	K = np.zeros((n,n))
+	for i in range(n-1):
+		K[i][i] += stiffness[i+1]
+		K[i+1][i+1] += stiffness[i+1]
+		K[i+1][i] = - stiffness[i+1]
+		K[i][i+1] = - stiffness[i+1]
+	K[0][0] += stiffness[0]
+	K[n-1][n-1] += stiffness[n-1]
+	return K
 
 def transpo(m):
 	n = len(m)
@@ -19,78 +52,107 @@ def transpo(m):
 		t += [c]
 	return t
 
-#m = [ [1, 2, 3], [4, 5, 6], [7, 8, 9] ]
-#print(m)
-#print(transpo(m))
+def minus_list(l,m):
+	n = len(l)
+	r = [ (l[k] - m[k]) for k in range(n)]
+	return r		
 
+####################################################################################################################
+############################################## Undamaged state #####################################################
[…]

### 2017-03-20 rapport/paper.tex
intro paper

@@
 The purpose of this work is the analysis of a particular data-driven damage localization method,
- namely the FRF interpolation method \cite{dilena2015damage}, and the development of a statistical extension of this method.
+ namely the FRF interpolation method \cite{dilena2015damage}.
+Our contribution is the development of a simulation to obtain acceleration measurement (which can run on several structures), a proposition of a variant of the FRF interpolation method, and the statistical analysis of the two methods.
 This paper is organized as follows. In section II we  present the existing methods (model-based and data driven methods), 
-then in section III we detail the different models of vibrating structures and finally, in section IV we talk about the localization using FRF interpolation method and, finally,  its results in section V.
+then in section III we talk about the localization using FRF interpolation method, in section IV we detail the different models of vibrating structures used to obtain data and, finally, the experiences and its results in section V.
 
@@
 
-\section{Models of vibrating structures}% or Physical models
+\section{Localization using FRF interpolation method}
 
-\subsection{Finite element model}
-
-The dynamic behaviour of a mechanical system consisting of $n$ degrees of freedom (see Figure (\ref{finite_el})) is described by following matrix differential equation:
-\begin{equation}
-M \ddot{q}(t) + C \dot{q}(t) + K q(t) = f(t)
-\label{fondamental}
-\end{equation}
-where $q(t)$ is the displacement vector at a continous time $t$, and $M, C, K \in \mathbb{R}^{n \times n}$, are the mass, damping and stiffness matrices.
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=0.3\textwidth]{images/finite_element.png}
-  \caption{Finite element model, from \cite{peeters2000system}}
-  \label{finite_el}
-\end{figure}
-
-For civil engineering structures, Equation (\ref{fondamental}) is obtained as the finite element approximation of the system with only $n$ dregrees of freedom.
-The structure is divided in elements, and the global mass matrix $M$ and stiffness matrix $K$ are generated from the geometry and material
-properties of the elements.
-
-\subsection{Continous-time state-space model} %(model parameters and reduction):
-
-From the Equation (\ref{fondamental}) and with the variable change $x =
-\begin{pmatrix}
-\dot{q} \\
-q
-\end{pmatrix}$, we obtain the state equation:
-\begin{equation}
-\dot{x}(t) = A_cx(t) + B_cf(t)
-\end{equation}
- where
-$A_c =
-\begin{pmatrix}
-0 & I \\
-M^{-1}K & M^{-1}C
-\end{pmatrix}$
-and
-$B_c=
-\begin{pmatrix}
-0 \\
-M^{-1}
-\end{pmatrix}$
-
-In a practical vibration experiment, not all $n$ degrees of freedom of the structure are measured, but only
-a subset. The observation equation is:
-\begin{equation}
-y(t) = C_cx(t) + D_cf(t)
-\end{equation}
-
-If it is assumed that all $n$ degrees of freedom are measured and that the sensors are accelerometers transducers, we have
-$C_c =
-\begin{pmatrix}
-M^{-1}K & M^{-1}C
-\end{pmatrix}$
-and
-$D_c=
-\begin{pmatrix}
-M^{-1}
-\end{pmatrix}$
-
-Thus, the classical continuous-time state-space model is:
-\begin{equation}
-\left\{
-\begin{array}{ll}
-\dot{x}(t) = A_cx(t) + B_cf(t) \\
-y(t) = C_cx(t) + D_cf(t)
-\end{array}
-\right.
-\end{equation}
-
-\subsection{Discrete-time state-space model} %(impulses response)
-
-Up to now all equations were expressed in continuous time, whereas in reality
-measurements are taken at discrete time instants.
-So this model need to be converted to discrete time.
-Another reason is that it is needed for performing simulations.
-
-Thus, we choose a certain fixed sampling period $\Delta t$, and the continuous-time equations are discretized and solved at all
-discrete time instants $k$ with $t = k \Delta t, k \in \mathbb{N}$.
-
-The discrete-time state-space model is:
-\begin{equation}
-\left\{
-\begin{array}{ll}
-x_{k+1} & = A_dx_k + B_df_k \\
-y_k & = C_dx_k + B_df_k
-\end{array}
-\right.
-\label{discrete}
-\end{equation}
-where
-\begin{equation}
-\begin{array}{ll}
-A_d = exp(A_c \Delta t) \\
-B_d= (A_d - I) A^{-1}_c B_c \\
-C_d = C_c \\
-D_d = D_c
-\end{array}
-\end{equation}
-
-%Stockastic state-space models
-%ARMA models
-%Continuous time frequency-domain models
-%Discrete time frequency-domain models
-
-\section{Localization using FRF interpolation method}
+\subsection{The FRF interpolation method}
 
@@
 
+\subsection{Frequency Response Function}
+
+The FRF correspond to the transfer function of the system. In frequency domain, if $F$ is the force that is apply on the system and $S$ is the response of this force, the FRF is given by:
+\begin{equation}
+H = \frac{S}{F}
+\end{equation}
+
+We want to calculate the FRF of the system, for each sensor localization.
+Here, we calculate an estimation of the FRF, called $H_1$ estimator \cite{cauberghe2004applied}.
+We suppose we have a vector of the forces $\{ f_k\}_{k=1}^N$ and a vector of the accelerations $\{ y_k\}_{k=1}^N$ for each sensor (the two vectors are size $N$).
+We need to be in frequency domain, so we calculate the discrete Fourier transform:
+\begin{equation}
+\begin{array}{ll}
+F_n = \sum\limits_{k=1}^N f_k e^{-2i\pi kn/N} \ \ \ \ \ n \in \{1 ... N\} \\
+Y_n = \sum\limits_{k=1}^N y_k e^{-2i\pi kn/N} \ \ \ \ \ n \in \{1 ... N\}
+\end{array}
+\end{equation}
+
+Then we calculate the power spectra, i.e. the Auto Power spectra of the inputs and the outputs
+and the Cross Power spectra between the inputs and outputs respectively given by:
+
+\begin{equation}
+\begin{array}{ll}
+S_{ff}(n) = F_n F_n^H \ \ \ \ \ n \in \{1 ... N\} \\
+S_{yf}(n) = Y_n F_n^H \ \ \ \ \ n \in \{1 ... N\}
+\end{array}
+\end{equation}
+where $M^H$ is the Hermitian of the matrix $M$. Thus, the FRF is given by:
+\begin{equation}
+H_1(n) = S_{yf}(n) S_{ff}(n)^{-1}
+\end{equation}
+
+\begin{remark}
+If we consider each sensor separately, $F_n$ and $Y_n$ are scalars, so we have:
+\begin{equation}
+\begin{array}{lll}
+H_1(n) & = & S_{yf}(n) S_{ff}(n)^{-1} \\
+& = & Y_n F_n^H (F_n F_n^H)^{-1} \\
+& = & Y_n / F_n
+\end{array}
+\end{equation}
+\end{remark}
+
+\subsection{Interpolation}
+
+We have to calculate for each sensor $z_l$ and for each considered frequency $f_i$ the cubic polynomial spline interpolation of the transfer function $H_R(z_k,f_i)$.
+The cubic spline interpolation is a piecewise continuous curve, passing through each of the values.
+There is a separate cubic polynomial interpolation for each interval, each with its own coefficients.
+Cubic polynomial spline interpolations produce an interpolated function that is continuous through to the second derivative.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.25\textwidth]{images/interpolation_spline.png}
+  \caption{Cubic spline interpolation}
+  \label{spline}
+\end{figure}
+
+With this interpolation, we can calculate the error as it is described in the section IV.
+
 \subsection{A variant of the method}
@@
 \section{Simulation}
+
+\subsection{Models of vibrating structures}% or Physical models
+
+\subsubsection{Finite element model}
+
+The dynamic behaviour of a mechanical system consisting of $n$ degrees of freedom (see Figure (\ref{finite_el})) is described by following matrix differential equation:
+\begin{equation}
+M \ddot{q}(t) + C \dot{q}(t) + K q(t) = f(t)
+\label{fondamental}
+\end{equation}
+where $q(t)$ is the displacement vector at a continous time $t$, and $M, C, K \in \mathbb{R}^{n \times n}$, are the mass, damping and stiffness matrices.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[height=0.3\textwidth]{images/finite_element.png}
+  \caption{Finite element model, from \cite{peeters2000system}}
+  \label{finite_el}
+\end{figure}
+
+For civil engineering structures, Equation (\ref{fondamental}) is obtained as the finite element approximation of the system with only $n$ dregrees of freedom.
+The structure is divided in elements, and the global mass matrix $M$ and stiffness matrix $K$ are generated from the geometry and material
+properties of the elements.
+
+\subsubsection{Continous-time state-space model} %(model parameters and reduction):
+
+From the Equation (\ref{fondamental}) and with the variable change $x =
+\begin{pmatrix}
+\dot{q} \\
+q
+\end{pmatrix}$, we obtain the state equation:
+\begin{equation}
+\dot{x}(t) = A_cx(t) + B_cf(t)
+\end{equation}
+ where
+$A_c =
+\begin{pmatrix}
+0 & I \\
+M^{-1}K & M^{-1}C
+\end{pmatrix}$
+and
+$B_c=
+\begin{pmatrix}
+0 \\
+M^{-1}
+\end{pmatrix}$
+
+In a practical vibration experiment, not all $n$ degrees of freedom of the structure are measured, but only
+a subset. The observation equation is:
+\begin{equation}
+y(t) = C_cx(t) + D_cf(t)
+\end{equation}
+
+If it is assumed that all $n$ degrees of freedom are measured and that the sensors are accelerometers transducers, we have
+$C_c =
+\begin{pmatrix}
+M^{-1}K & M^{-1}C
+\end{pmatrix}$
+and
+$D_c=
+\begin{pmatrix}
+M^{-1}
+\end{pmatrix}$
+
+Thus, the classical continuous-time state-space model is:
+\begin{equation}
+\left\{
+\begin{array}{ll}
+\dot{x}(t) = A_cx(t) + B_cf(t) \\
+y(t) = C_cx(t) + D_cf(t)
+\end{array}
+\right.
+\end{equation}
+
+\subsubsection{Discrete-time state-space model} %(impulses response)
+
+Up to now all equations were expressed in continuous time, whereas in reality
+measurements are taken at discrete time instants.
+So this model need to be converted to discrete time.
+Another reason is that it is needed for performing simulations.
+
+Thus, we choose a certain fixed sampling period $\Delta t$, and the continuous-time equations are discretized and solved at all
+discrete time instants $k$ with $t = k \Delta t, k \in \mathbb{N}$.
+
+The discrete-time state-space model is:
+\begin{equation}
+\left\{
+\begin{array}{ll}
+x_{k+1} & = A_dx_k + B_df_k \\
+y_k & = C_dx_k + B_df_k
+\end{array}
+\right.
+\label{discrete}
+\end{equation}
+where
+\begin{equation}
+\begin{array}{ll}
+A_d = exp(A_c \Delta t) \\
+B_d= (A_d - I) A^{-1}_c B_c \\
+C_d = C_c \\
+D_d = D_c
+\end{array}
+\end{equation}
 
@@
 So we can calculate the matrices $A, B$ and make the simulation with the discrete-time state-space model (Equation (\ref{discrete})). To simulate the forces $f_k$, we use a white noise.
-
-\subsection{Frequency Response Function}
-
-The FRF correspond to the transfer function of the system. In frequency domain, if $F$ is the force that is apply on the system and $S$ is the response of this force, the FRF is given by:
-\begin{equation}
-H = \frac{S}{F}
-\end{equation}
-
-We want to calculate the FRF of the system, for each sensor localization.
-Here, we calculate an estimation of the FRF, called $H_1$ estimator \cite{cauberghe2004applied}.
-We suppose we have a vector of the forces $\{ f_k\}_{k=1}^N$ and a vector of the accelerations $\{ y_k\}_{k=1}^N$ for each sensor (the two vectors are size $N$).
-We need to be in frequency domain, so we calculate the discrete Fourier transform:
-\begin{equation}
-\begin{array}{ll}
-F_n = \sum\limits_{k=1}^N f_k e^{-2i\pi kn/N} \ \ \ \ \ n \in \{1 ... N\} \\
-Y_n = \sum\limits_{k=1}^N y_k e^{-2i\pi kn/N} \ \ \ \ \ n \in \{1 ... N\}
-\end{array}
-\end{equation}
-
-Then we calculate the power spectra, i.e. the Auto Power spectra of the inputs and the outputs
-and the Cross Power spectra between the inputs and outputs respectively given by:
-
-\begin{equation}
-\begin{array}{ll}
-S_{ff}(n) = F_n F_n^H \ \ \ \ \ n \in \{1 ... N\} \\
-S_{yf}(n) = Y_n F_n^H \ \ \ \ \ n \in \{1 ... N\}
-\end{array}
-\end{equation}
-where $M^H$ is the Hermitian of the matrix $M$. Thus, the FRF is given by:
-\begin{equation}
-H_1(n) = S_{yf}(n) S_{ff}(n)^{-1}
-\end{equation}
-
-\begin{remark}
-If we consider each sensor separately, $F_n$ and $Y_n$ are scalars, so we have:
-\begin{equation}
-\begin{array}{lll}
-H_1(n) & = & S_{yf}(n) S_{ff}(n)^{-1} \\
-& = & Y_n F_n^H (F_n F_n^H)^{-1} \\
-& = & Y_n / F_n
-\end{array}
-\end{equation}
-\end{remark}
-
-\subsection{Interpolation}
-
-We have to calculate for each sensor $z_l$ and for each considered frequency $f_i$ the cubic polynomial spline interpolation of the transfer function $H_R(z_k,f_i)$.
-The cubic spline interpolation is a piecewise continuous curve, passing through each of the values.
-There is a separate cubic polynomial interpolation for each interval, each with its own coefficients.
-Cubic polynomial spline interpolations produce an interpolated function that is continuous through to the second derivative.
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.25\textwidth]{images/interpolation_spline.png}
-  \caption{Cubic spline interpolation}
-  \label{spline}
-\end{figure}
-
-With this interpolation, we can calculate the error as it is described in the section IV.
 
@@
 
+\subsection{Beam}
+
+We test our localization on another structure: a beam. We don't detail this model in this paper, we just use it to verify our methods. The damage is localized between the sensors 4 and 5.
+
+Figure (\ref{beam_curve}) shows two FRF, one for the undamaged state and the second for the damaged one, at a fixed frequency. We can easily see there is an irregularity at the sensor 4.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.4\textwidth]{images/poutre_curve2.png}
+  \caption{}
+  \label{beam_curve}
+\end{figure}
+
+Figure (\ref{beam_error}) shows the computed error. We can see that there are only two sensors with a positiv error, which are the sensors 4 and 5. Thus, the localization is good.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.4\textwidth]{images/poutre_error.png}
+  \caption{}
+  \label{beam_error}
+\end{figure}
+
+\subsection{Quantification}
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.4\textwidth]{images/quantification_without_noise_100.png}
+  \caption{}
+  \label{quant}
+\end{figure}
+
 \section{Conclusion}

### 2017-03-20 code_solo/damage_noise_max.py

@@ -24,10 +24,9 @@ CAPTVALUE = 20
 SAMPLVALUE = 10000
 MAKEREF = 100
 DAMAGED_SENSOR = [7]#must be a list
-DAMAGE = 30# % of damage
+DAMAGE = 20# % of damage
 
 pos = [ k for k in range(CAPTVALUE) ]
-z = [ 0 for k in range(CAPTVALUE) ]
 mass = [ 100 for k in range(CAPTVALUE) ]
 
 
@@ -64,7 +63,7 @@ def two_max_ind(tab):
 			else:
 				b = i
 				vb = tab[i]
-	return a, b
+	return a, b, va, vb
 
 
 
@@ -206,7 +205,7 @@ A, B, C, D, sampling_freq = make_matrices(mass, stiffness_undamaged)
 for x in DAMAGED_SENSOR:
 	stiffness_damaged[x] = int(float(stiffness_undamaged[x])*float(100-DAMAGE)/100)
 
-A_damaged, B_damaged, C_useless, D_useless, freq_useless = make_matrices(mass, stiffness_damaged)
+A_damaged, B_damaged, C_damaged, D_useless, freq_useless = make_matrices(mass, stiffness_damaged)
 
 #acc = [ [0 for k in range(2*n) ] ]
 
@@ -239,7 +238,7 @@ def simulation(typ,acc,std_noise):
 		f_damaged = white_noise(SAMPLVALUE,n)
 		for i in range(SAMPLVALUE):
 			acc += [ np.dot(A_damaged,acc[-1]) + np.dot(B_damaged,f_damaged[i]) ]
-			measurement_damaged += [ np.dot(C,acc[-2]) + np.dot(D,f_damaged[i]) ]
+			measurement_damaged += [ np.dot(C_damaged,acc[-2]) + np.dot(D,f_damaged[i]) ]
 		for i in range(SAMPLVALUE):
 			for j in range(CAPTVALUE):
 				measurement_damaged[i][j] = measurement_damaged[i][j] + NOISE*norm.rvs(size=1, loc = 0, scale = std_noise)[0]
@@ -311,6 +310,12 @@ def experience():
 	threshold1_inv = parser.get3("data/threshold1_inv_noise"+str(NOISE)+".txt")
 	threshold2_inv = parser.get3("data/threshold2_inv_noise"+str(NOISE)+".txt")
 	
+	
+	quantification1 = [ 0 for k in range(CAPTVALUE) ]
[…]

### 2017-03-20 code_solo/data/quantification.py

@@ -4,13 +4,12 @@ import matplotlib.pyplot as plt
 
 DAMAGED_SENSOR = 7
 
-#NOISE = 0.05
-#error = [0,2,3,4,5,6,8,10,20]
-
-NOISE = 0.1
-damage = [0,5,10,20,30,40,50,60,70,80,90,100]
 
 NOISE = 0
+#damage = [0,5,10,20,30,40,50,60,70,80,90,100]
+
+NOISE = 0.05
+damage = [10,20,30,40,50]
 
 q1, q2, q1_inv, q2_inv = [], [], [], []
 

### 2017-03-23 rapport/paper.tex
paper

@@
 
+Figure (\ref{theo}) shows this loss of spatial regularity on the theoretical FRF, for a damage at the position 7.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.3\textwidth]{images/theo60.png}
+  \caption{Theoretical FRF for undamaged and damage states}
+  \label{theo}
+\end{figure}
+
 In this section, we suppose that we have $n$ sensors, which are located along an axis $z$, and we denote them by
@@
 to be a symptom of a local variation of stiffness at $z_l$ associated with the occurrence of damage.
-
-The above analysis has been developed in a deterministic context. Several sources, such as temperature, nonlinear
-behavior, soil structure interaction and noise in recorded data, can induce variations of the interpolation error even if no
-damage occurs.
-
-Thus, once have to determine a threshold $E_T$, such as $ \Delta E(z_l)$ must be taller than $E_T$ to have a high probability of identification of a damage at location $z_l$.
-Indeed, as we can see in the Figure (\ref{proba}), the curves which represent the fact to have a damage or not have a share area: if the interpolation error $ \Delta E(z_l)$ is in this area, one can commit two errors:
-\begin{itemize}
-\item if it is in the area $P_f(z_l)$ under the graph of $p_{E,0}(z_l)$, once can detect a damage since there isn't one (false alarm).
-\item if it is in the area $P_m(z_l)$ under the graph of $p_{E,d}(z_l)$, once can not detect a damage since there is one (missing alarm).
-\end{itemize}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.4\textwidth]{images/gaussiennes.png}
-  \caption{Probabilities of false and missing alarm, from \cite{dilena2015damage}}
-  \label{proba}
-\end{figure}
 
@@
 
+\subsection{False and missing alarm}
+
+The above analysis has been developed in a deterministic context. Several sources, such as temperature, nonlinear
+behavior, soil structure interaction and noise in recorded data, can induce variations of the interpolation error even if no
+damage occurs.
+
+Thus, once have to determine a threshold $E_T$, such as $ \Delta E(z_l)$ must be taller than $E_T$ to have a high probability of identification of a damage at location $z_l$.
+Indeed, as we can see in the Figure (\ref{proba}), the curves which represent the fact to have a damage or not have a share area: if the interpolation error $ \Delta E(z_l)$ is in this area, one can commit two errors:
+\begin{itemize}
+\item if it is in the area $P_f(z_l)$ under the graph of $p_{E,0}(z_l)$, once can detect a damage since there isn't one (false alarm).
+\item if it is in the area $P_m(z_l)$ under the graph of $p_{E,d}(z_l)$, once can not detect a damage since there is one (missing alarm).
+\end{itemize}
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.4\textwidth]{images/gaussiennes.png}
+  \caption{Probabilities of false and missing alarm, from \cite{dilena2015damage}}
+  \label{proba}
+\end{figure}
+
 \subsection{A variant of the method}
@@
 \end{itemize}
+
+Figure(\ref{theodiff}) shows the difference betweem the two FRF, and we can see the loss of spatial regularity (damage at position 7).
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.3\textwidth]{images/theodiff60.png}
+  \caption{Difference betweem theoretical FRF of undamaged and damage states}
+  \label{theodiff}
+\end{figure}
 
@@
 
-\section{Results}
+We can also use our simulation with other structures, like a beam, if we know the matrices $M$, $K$, $C$ and the impact of a damage on these matrices.
+We will also validate the FRF interpolation method with a beam in this paper, but we don't detail the matrices $M$, $K$, $C$.
+
+\section{Analysis}
 
@@
 
-\subsection{FRF results}
+\subsection{Data presentation}
 
@@
 
+\subsection{FRF interpolation method results}
+
 To test the localization, we have to make a thresold for each sensor.
@@
 
-\subsection{Without noise}
+\subsubsection{Without noise}
 
@@
 
-\subsection{With noise}
+\subsubsection{With noise}
 
@@
 
-\subsection{Eliminate the false positives}
+\subsection{Eliminate the false positives to improve the efficiency}
+
+We have seen that there are too many false positives.
+We try to remove them with the next idea: the difference between the threshold and the computed values is larger on the damage than on other sensors.
+As the damage is localized on one spring, so between two sensors, we apply the next algorithm to determine where is the damage:
+\begin{itemize}
+\item We compute the error values
+\item We make the difference with the threshold
+\item We keep only the two highest values, and we detect a damage only if they are positives
+\end{itemize}
+
+Figure (\ref{detect_max}) shows the results of this method.
 
@@
 
-\subsection{Beam}
+\subsection{FRF interpolation method on a beam}
 
@@
 \subsection{Quantification}
+
+We think we can use the FRF method interpolation for a quantification of the damage. For that, we have compared the threshold and the difference between it and the computed error.
+
+We shows in Figure(\ref{quant}) the computed error, in percent of the threshold.
 

### 2017-03-23 code_solo/damage.py

@@ -25,7 +25,7 @@ SAMPLVALUE = 10000
 MAKEREF = 100
 DAMAGED_SENSOR = [7]#must be a list
 EXCITED_SENSOR = 0
-DAMAGE = 10# % of damage
+DAMAGE = 8# % of damage
 
 pos = [ k for k in range(CAPTVALUE) ]
 z = [ 0 for k in range(CAPTVALUE) ]
@@ -166,7 +166,7 @@ A, B, C, D, sampling_freq = make_matrices(mass, stiffness_undamaged)
 for x in DAMAGED_SENSOR:
 	stiffness_damaged[x] = int(float(stiffness_undamaged[x])*float(100-DAMAGE)/100)
 
-A_damaged, B_damaged, C_useless, D_useless, freq_useless = make_matrices(mass, stiffness_damaged)
+A_damaged, B_damaged, C_damaged, D_damaged, freq_useless = make_matrices(mass, stiffness_damaged)
 
 #acc = [ [0 for k in range(2*n) ] ]
 
@@ -193,7 +193,7 @@ def simulation(typ,acc):
 		f_damaged = white_noise(SAMPLVALUE,n)
 		for i in range(SAMPLVALUE):
 			acc += [ np.dot(A_damaged,acc[-1]) + np.dot(B_damaged,f_damaged[i]) ]
-			measurement_damaged += [ np.dot(C,acc[-2]) + np.dot(D,f_damaged[i]) ]
+			measurement_damaged += [ np.dot(C_damaged,acc[-2]) + np.dot(D_damaged,f_damaged[i]) ]
 		return measurement_damaged, f_damaged, acc
 
 	

### 2017-03-23 code_solo/damage_max.py

@@ -25,7 +25,7 @@ SAMPLVALUE = 10000
 MAKEREF = 100
 DAMAGED_SENSOR = [7]#must be a list
 EXCITED_SENSOR = 0
-DAMAGE = 100# % of damage
+DAMAGE = 15# % of damage
 
 pos = [ k for k in range(CAPTVALUE) ]
 z = [ 0 for k in range(CAPTVALUE) ]
@@ -187,7 +187,7 @@ A, B, C, D, sampling_freq = make_matrices(mass, stiffness_undamaged)
 for x in DAMAGED_SENSOR:
 	stiffness_damaged[x] = int(float(stiffness_undamaged[x])*float(100-DAMAGE)/100)
 
-A_damaged, B_damaged, C_useless, D_useless, freq_useless = make_matrices(mass, stiffness_damaged)
+A_damaged, B_damaged, C_damaged, D_damaged, freq_useless = make_matrices(mass, stiffness_damaged)
 
 #acc = [ [0 for k in range(2*n) ] ]
 
@@ -214,7 +214,7 @@ def simulation(typ,acc):
 		f_damaged = white_noise(SAMPLVALUE,n)
 		for i in range(SAMPLVALUE):
 			acc += [ np.dot(A_damaged,acc[-1]) + np.dot(B_damaged,f_damaged[i]) ]
-			measurement_damaged += [ np.dot(C,acc[-2]) + np.dot(D,f_damaged[i]) ]
+			measurement_damaged += [ np.dot(C_damaged,acc[-2]) + np.dot(D_damaged,f_damaged[i]) ]
 		return measurement_damaged, f_damaged, acc
 
 	
@@ -296,37 +296,37 @@ def experience():
 		error_damaged_inv = itp.global_error(minus_list(frf_ref,frf_damaged))
 		diff = minus_list(error_damaged, error_ref)
 		#threshold1
-		ind_max1, ind_max2, max1, max2 = two_max_ind(minus_list(diff,threshold1))
-		if ind_max1 > 0:
-			detect_damage1[ind_max1] = detect_damage1[ind_max1] + 1
-			quantification1[ind_max1] = quantification1[ind_max1] + max1
-		if ind_max2 > 0:
-			detect_damage1[ind_max2] = detect_damage1[ind_max2] + 1
-			quantification1[ind_max2] = quantification1[ind_max2] + max2
+		ind_max1, ind_max2, max1, max2 = two_max_ind(minus_list(diff,threshold1)[1:-1])
+		ind_max1 += 1;
[…]

### 2017-03-23 code_solo/damage_noise.py

@@ -19,12 +19,12 @@ import random
 ############# variables ########################
 ################################################
 
-NOISE = 0.1
+NOISE = 0.04
 CAPTVALUE = 20
 SAMPLVALUE = 10000
 MAKEREF = 100
 DAMAGED_SENSOR = [7]#must be a list
-DAMAGE = 14# % of damage
+DAMAGE = 5# % of damage
 
 pos = [ k for k in range(CAPTVALUE) ]
 z = [ 0 for k in range(CAPTVALUE) ]
@@ -180,7 +180,7 @@ A, B, C, D, sampling_freq = make_matrices(mass, stiffness_undamaged)
 for x in DAMAGED_SENSOR:
 	stiffness_damaged[x] = int(float(stiffness_undamaged[x])*float(100-DAMAGE)/100)
 
-A_damaged, B_damaged, C_useless, D_useless, freq_useless = make_matrices(mass, stiffness_damaged)
+A_damaged, B_damaged, C_damaged, D_damaged, freq_useless = make_matrices(mass, stiffness_damaged)
 
 #acc = [ [0 for k in range(2*n) ] ]
 
@@ -213,7 +213,7 @@ def simulation(typ,acc,std_noise):
 		f_damaged = white_noise(SAMPLVALUE,n)
 		for i in range(SAMPLVALUE):
 			acc += [ np.dot(A_damaged,acc[-1]) + np.dot(B_damaged,f_damaged[i]) ]
-			measurement_damaged += [ np.dot(C,acc[-2]) + np.dot(D,f_damaged[i]) ]
+			measurement_damaged += [ np.dot(C_damaged,acc[-2]) + np.dot(D_damaged,f_damaged[i]) ]
 		for i in range(SAMPLVALUE):
 			for j in range(CAPTVALUE):
 				measurement_damaged[i][j] = measurement_damaged[i][j] + NOISE*norm.rvs(size=1, loc = 0, scale = std_noise)[0]

### 2017-03-23 code_solo/damage_noise_max.py

@@ -19,12 +19,12 @@ import random
 ############# variables ########################
 ################################################
 
-NOISE = 0.05
+NOISE = 0
 CAPTVALUE = 20
 SAMPLVALUE = 10000
 MAKEREF = 100
 DAMAGED_SENSOR = [7]#must be a list
-DAMAGE = 20# % of damage
+DAMAGE = 5# % of damage
 
 pos = [ k for k in range(CAPTVALUE) ]
 mass = [ 100 for k in range(CAPTVALUE) ]

### 2017-03-23 code_solo/data/detect.py

@@ -1,7 +1,7 @@
 import parser as pa
 import matplotlib.pyplot as plt
 
-error = [1, 2, 3, 4, 5, 10, 20, 30]
+error = [0,1, 2, 3, 4, 5, 8, 10, 13, 15, 20, 30]#12
 
 DAMAGED_SENSOR = 7
 

### 2017-03-23 code_solo/data/detect_noise.py

@@ -7,9 +7,11 @@ DAMAGED_SENSOR = 7
 #NOISE = 0.05
 #error = [0,2,3,4,5,6,8,10,20]
 
-NOISE = 0.1
-error = [2,3,4,5,7,8,9,10,12,14,15,20]
+#NOISE = 0.1
+#error = [2,3,4,5,7,8,9,10,12,14,15,20]
 
+NOISE = 0.04
+error = [5,10,15,20,25,30]
 
 def tp(t):
 	return max(t[DAMAGED_SENSOR-1], t[DAMAGED_SENSOR])

### 2017-03-23 code_solo/data/fp_noise.py

@@ -1,11 +1,13 @@
 import parser as pa
 import matplotlib.pyplot as plt
 
-
-error = [0,2,3,4,5,10,20]
-
 DAMAGED_SENSOR = 7
-NOISE = 0.05
+
+#error = [0,2,3,4,5,10,20]
+#NOISE = 0.05
+
+NOISE = 0.04
+error = [5,10,15,20,25,30]
 
 
 def fp(t):

### 2017-03-23 code_solo/data/quantification.py

@@ -6,10 +6,11 @@ DAMAGED_SENSOR = 7
 
 
 NOISE = 0
-#damage = [0,5,10,20,30,40,50,60,70,80,90,100]
+damage = [0,5,10,20,30,40,50,60,70,80,90,100]
+damage = [20,30,40,50,60,70,80,90,100]
 
-NOISE = 0.05
-damage = [10,20,30,40,50]
+#NOISE = 0.05
+#damage = [10,20,30,40,50]
 
 q1, q2, q1_inv, q2_inv = [], [], [], []
 

### 2017-03-23 code_solo/threshold_noise.py

@@ -19,7 +19,7 @@ import random
 ############# variables ########################
 ################################################
 
-NOISE = 0.15
+NOISE = 0.04
 CAPTVALUE = 20
 SAMPLVALUE = 10000
 MAKEREF = 100

### 2017-03-31 rapport/paper.tex
MAJ paper

@@
 This paper is organized as follows. In section II we  present the existing methods (model-based and data driven methods), 
-then in section III we talk about the localization using FRF interpolation method, in section IV we detail the different models of vibrating structures used to obtain data and, finally, the experiences and its results in section V.
+then in section III we present different models of vibrating structures required for what happens next.
+In section IV,  we talk about the localization using FRF interpolation method, in section V we detail our simulation used to obtain data and, finally, the experiences and its results in section VI.
 
@@
 
-\section{Localization using FRF interpolation method}
+\section{Vibration modeling}
 
-\subsection{The FRF interpolation method}
+In this section, we present the physical models that we use to obtain data for our experiences, and the Frequency Response Function (FRF) which is the base of the FRF interpolation method.
 
-This method is presented in \cite{dilena2015damage}.
-The main hypothesis underlying the method is that a concentrated damage reflects in a loss of spatial regularity of the
-vibrational profile of a structure, compared with the reference (undamaged) state.
-
-Figure (\ref{theo}) shows this loss of spatial regularity on the theoretical FRF, for a damage at the position 7.
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.3\textwidth]{images/theo60.png}
-  \caption{Theoretical FRF for undamaged and damage states}
-  \label{theo}
-\end{figure}
-
-In this section, we suppose that we have $n$ sensors, which are located along an axis $z$, and we denote them by
-$\{z_l\}, l\in \{1 ... n\}$. We also suppose we have $N$ measurements for each sensor.
-
-For each sensor, we calculate the Frequency Response Function (FRF) from the acceleration's measures, at certain frequencies 
-(which are $\frac{k}{N}, k \in \{0 ... N-1\}$).
-
-Thus, for each frequency and each sensor, we have the transfer function value. Let us denote $H_R(z_l,f_i)$ the value of the transfer function for  the sensor $z_l$ at the frequency $f_i$.
-
-Then, we calculate for each sensor $z_l$ the cubic polynomial spline interpolation of the transfer functions $H_R(z_k,f_i)$ measured at all 
-the other instrumented locations $\{z_k\}, k\in \{1 ... n\}, k \neq l$: we denote it $H_S(z_l,f_i)$.
-
-For these two transfer functions, we define the interpolation error $E(z_l,f_i)$ as the absolute value of the difference between recorded and interpolated FRFs:
-\begin{equation}
-E(z_l,f_i) = | H_R(z_l,f_i) - H_S(z_l,f_i) |
-\end{equation}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.4\textwidth]{images/interpolation.png}
-  \caption{Interpolation error, from \cite{dilena2015damage}}
-  \label{interpolation_error}
-\end{figure}
-
-Since we want to characterize each location $z_l$ with a scalar-valued error index, we introduce the norm of the error on the whole range of
-frequencies:
-\begin{equation}
-E(z_l) = \sqrt{  \sum\limits_{i=1}^N  E^2(z_l,f_i) }
-\label{error}
-\end{equation}
-
-Transfer function values obviously depend on the state of the structure. Hence, if the estimation of the error function
-through Equation (\ref{error}) is repeated in the baseline (undamaged) and in the inspection (possibly damaged) configuration, then the
-difference between the two values, denoted respectively by $E_0(z_l)$ and $E_d(z_l)$, can provide an indication about the existence of
-degradation at location $z_l$:
-\begin{equation}
-\Delta E(z_l) = E_d(z_l) - E_0(z_l)
-\end{equation}
-
-An increase in the interpolation error between the reference configuration and the current configuration at a station $z_l$ , i.e.
-$ \Delta E(z_l) > 0$, highlights a localized reduction of smoothness in the vibrational amplitude profile and, therefore, it is assumed
-to be a symptom of a local variation of stiffness at $z_l$ associated with the occurrence of damage.
-
-\subsection{Frequency Response Function}
-
-The FRF correspond to the transfer function of the system. In frequency domain, if $F$ is the force that is apply on the system and $S$ is the response of this force, the FRF is given by:
-\begin{equation}
-H = \frac{S}{F}
-\end{equation}
-
-We want to calculate the FRF of the system, for each sensor localization.
-Here, we calculate an estimation of the FRF, called $H_1$ estimator \cite{cauberghe2004applied}.
-We suppose we have a vector of the forces $\{ f_k\}_{k=1}^N$ and a vector of the accelerations $\{ y_k\}_{k=1}^N$ for each sensor (the two vectors are size $N$).
-We need to be in frequency domain, so we calculate the discrete Fourier transform:
-\begin{equation}
-\begin{array}{ll}
-F_n = \sum\limits_{k=1}^N f_k e^{-2i\pi kn/N} \ \ \ \ \ n \in \{1 ... N\} \\
-Y_n = \sum\limits_{k=1}^N y_k e^{-2i\pi kn/N} \ \ \ \ \ n \in \{1 ... N\}
-\end{array}
-\end{equation}
-
-Then we calculate the power spectra, i.e. the Auto Power spectra of the inputs and the outputs
-and the Cross Power spectra between the inputs and outputs respectively given by:
-
-\begin{equation}
-\begin{array}{ll}
-S_{ff}(n) = F_n F_n^H \ \ \ \ \ n \in \{1 ... N\} \\
-S_{yf}(n) = Y_n F_n^H \ \ \ \ \ n \in \{1 ... N\}
-\end{array}
-\end{equation}
-where $M^H$ is the Hermitian of the matrix $M$. Thus, the FRF is given by:
-\begin{equation}
-H_1(n) = S_{yf}(n) S_{ff}(n)^{-1}
-\end{equation}
-
-\begin{remark}
-If we consider each sensor separately, $F_n$ and $Y_n$ are scalars, so we have:
-\begin{equation}
-\begin{array}{lll}
-H_1(n) & = & S_{yf}(n) S_{ff}(n)^{-1} \\
-& = & Y_n F_n^H (F_n F_n^H)^{-1} \\
-& = & Y_n / F_n
-\end{array}
-\end{equation}
-\end{remark}
-
-\subsection{Interpolation}
-
-We have to calculate for each sensor $z_l$ and for each considered frequency $f_i$ the cubic polynomial spline interpolation of the transfer function $H_R(z_k,f_i)$.
-The cubic spline interpolation is a piecewise continuous curve, passing through each of the values.
-There is a separate cubic polynomial interpolation for each interval, each with its own coefficients.
-Cubic polynomial spline interpolations produce an interpolated function that is continuous through to the second derivative.
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.25\textwidth]{images/interpolation_spline.png}
-  \caption{Cubic spline interpolation}
-  \label{spline}
-\end{figure}
-
-With this interpolation, we can calculate the error as it is described in the section IV.
-
-\subsection{False and missing alarm}
-
-The above analysis has been developed in a deterministic context. Several sources, such as temperature, nonlinear
-behavior, soil structure interaction and noise in recorded data, can induce variations of the interpolation error even if no
-damage occurs.
-
-Thus, once have to determine a threshold $E_T$, such as $ \Delta E(z_l)$ must be taller than $E_T$ to have a high probability of identification of a damage at location $z_l$.
-Indeed, as we can see in the Figure (\ref{proba}), the curves which represent the fact to have a damage or not have a share area: if the interpolation error $ \Delta E(z_l)$ is in this area, one can commit two errors:
-\begin{itemize}
-\item if it is in the area $P_f(z_l)$ under the graph of $p_{E,0}(z_l)$, once can detect a damage since there isn't one (false alarm).
-\item if it is in the area $P_m(z_l)$ under the graph of $p_{E,d}(z_l)$, once can not detect a damage since there is one (missing alarm).
-\end{itemize}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.4\textwidth]{images/gaussiennes.png}
-  \caption{Probabilities of false and missing alarm, from \cite{dilena2015damage}}
-  \label{proba}
-\end{figure}
-
-\subsection{A variant of the method}
-
-We propose here a variant of the FRF interpolation method.
-While we have worked on the implementation of the original method, we have observed the eigenvectors of the matrix $M^{-1}K$ (see part III), which have similar properties than the FRF.
-We noticed that the following method is better than the interpolation method (compute the interpolation error, then compute a difference) to detect damaged on the eigenvectors:
-\begin{itemize}
-\item first, compute the difference between the eigenvectors
-\item second, compute the interpolation error on this difference
-\end{itemize}
-
-Figure(\ref{theodiff}) shows the difference betweem the two FRF, and we can see the loss of spatial regularity (damage at position 7).
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.3\textwidth]{images/theodiff60.png}
-  \caption{Difference betweem theoretical FRF of undamaged and damage states}
-  \label{theodiff}
-\end{figure}
-
-Thus, we also study in this paper a variant of the FRF interpolation method . The only difference with the original method is the order of the steps:
-\begin{itemize}
-\item Compute the FRF
-\item Compute the difference between the FRF of reference and the FRF of the studied state, for each frequency
-\item Compute the interpolation error of these differencies
-\item Compute the sum of the interpolation errors at each frequency
-\end{itemize}
-
-From now on, to tell the difference between the two methods, we shall call our variant the FRF difference method.
-
-\section{Simulation}
-
-\subsection{Models of vibrating structures}% or Physical models
-
-\subsubsection{Finite element model}
+\subsection{Finite element model}
 
@@
 \end{equation}
-where $q(t)$ is the displacement vector at a continous time $t$, and $M, C, K \in \mathbb{R}^{n \times n}$, are the mass, damping and stiffness matrices.
+where $q(t)$ is the displacement vector at a continous time $t$, $f(t)$ is the excitement vector at $t$ and $M, C, K \in \mathbb{R}^{n \times n}$, are the mass, damping and stiffness matrices.
 
@@
 
-\subsubsection{Continous-time state-space model} %(model parameters and reduction):
+\subsection{Continous-time state-space model} %(model parameters and reduction):
 
@@
 
-\subsubsection{Discrete-time state-space model} %(impulses response)
+\subsection{Discrete-time state-space model} %(impulses response)
 
@@
 
-\subsection{Obtaining acceleration measures}
+\subsection{Frequency Response Function}
 
-We have implemented a simulation to check this method of localization. We made this on the following system: $n$ masses, connected
+The FRF correspond to the transfer function of the system. In frequency domain, if $F$ is the force that is apply on the system and $X$ is the response of this force, the FRF is given by:
+\begin{equation}
+H = \frac{X}{F}
+\end{equation}
+
+We can express the theoretical FRF with the matrices $M, C, K$. Indeed, in the frequency domain, we have
+\begin{equation}
+s^2 M x + s C x + K x = f
+\end{equation}
+where s is $i\omega$, with $\omega$ the pulsation.
+Thus, the FRF $H$ is:
+\begin{equation}
+H = \frac{x}{f} = (s^2 M + s C + K)^{-1}
+\end{equation}
+
+In practice, we want to calculate the FRF of the system, for each sensor localization.
+Here, we calculate an estimation of the FRF, called $H_1$ estimator \cite{cauberghe2004applied}.
+We suppose we have a vector of the forces $\{ f_k\}_{k=1}^N$ and a vector of the accelerations $\{ y_k\}_{k=1}^N$ for each sensor (the two vectors are size $N$).
+We need to be in frequency domain, so we calculate the discrete Fourier transform:
+\begin{equation}
+\begin{array}{ll}
+F_n = \sum\limits_{k=1}^N f_k e^{-2i\pi kn/N} \ \ \ \ \ n \in \{1 ... N\} \\
+Y_n = \sum\limits_{k=1}^N y_k e^{-2i\pi kn/N} \ \ \ \ \ n \in \{1 ... N\}
+\end{array}
+\end{equation}
+
+Then we calculate the power spectra, i.e. the Auto Power spectra of the inputs and the outputs
+and the Cross Power spectra between the inputs and outputs respectively given by:
+
+\begin{equation}
+\begin{array}{ll}
+S_{ff}(n) = F_n F_n^H \ \ \ \ \ n \in \{1 ... N\} \\
+S_{yf}(n) = Y_n F_n^H \ \ \ \ \ n \in \{1 ... N\}
+\end{array}
+\end{equation}
+where $M^H$ is the Hermitian of the matrix $M$. Thus, the FRF is given by:
+\begin{equation}
+H_1(n) = S_{yf}(n) S_{ff}(n)^{-1}
+\end{equation}
+
+\begin{remark}
+If we consider each sensor separately, $F_n$ and $Y_n$ are scalars, so we have:
+\begin{equation}
+\begin{array}{lll}
+H_1(n) & = & S_{yf}(n) S_{ff}(n)^{-1} \\
+& = & Y_n F_n^H (F_n F_n^H)^{-1} \\
+& = & Y_n / F_n
+\end{array}
+\end{equation}
+\end{remark}
+
+\section{Localization using FRF interpolation method}
+
+\subsection{The FRF interpolation method}
+
+This method is presented in \cite{dilena2015damage}.
+The main hypothesis underlying the method is that a concentrated damage reflects in a loss of spatial regularity of the
+vibrational profile of a structure, compared with the reference (undamaged) state.
+
+Figure (\ref{theo}) shows this loss of spatial regularity on the theoretical FRF, for a damage at the position 7.
+We can see there is a loss of regularity at the position 7 for the damaged state.
+We can also see there is an iregularity at the position 2, but here the two states have the same iregularity, so it's not a loss of regularity.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.3\textwidth]{images/theo60.png}
+  \caption{Theoretical FRF for undamaged and damage states}
+  \label{theo}
+\end{figure}
+
+In this section, we suppose that we have $n$ sensors, which are located along an axis $z$, and we denote them by
+$\{z_l\}, l\in \{1 ... n\}$ (that is their position on the axis $z$). We also suppose we have $N$ measurements for each sensor.
+
+For each sensor, we calculate the Frequency Response Function (FRF) from the acceleration's measures, at certain frequencies 
+(which are $\frac{k}{N}, k \in \{0 ... N-1\}$ with $N$ the size of the input and output vectors).
+
+Thus, for each frequency and each sensor, we have the transfer function value. Let us denote $H_R(z_l,f_i)$ the value of the transfer function for  the sensor $z_l$ at the frequency $f_i$.
+
+Then, we calculate for each sensor $z_l$ the cubic polynomial spline interpolation of the transfer functions $H_R(z_k,f_i)$ measured at all 
+the other instrumented locations $\{z_k\}, k\in \{1 ... n\}, k \neq l$: we denote it $H_S(z_l,f_i)$.
+
+For these two transfer functions, we define the interpolation error $E(z_l,f_i)$ as the absolute value of the difference between recorded and interpolated FRFs:
+\begin{equation}
+E(z_l,f_i) = | H_R(z_l,f_i) - H_S(z_l,f_i) |
+\end{equation}
+
+We can see this error on the Figure(\ref{interpolation_error}).
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.4\textwidth]{images/interpolation.png}
+  \caption{Interpolation error, from \cite{dilena2015damage}}
+  \label{interpolation_error}
+\end{figure}
+
+Since we want to characterize each location $z_l$ with a scalar-valued error index, we introduce the norm of the error on the whole range of
+frequencies:
+\begin{equation}
+E(z_l) = \sqrt{  \sum\limits_{i=1}^N  E^2(z_l,f_i) }
+\label{error}
+\end{equation}
+
+Transfer function values obviously depend on the state of the structure. Hence, if the estimation of the error function
+through Equation (\ref{error}) is repeated in the baseline (undamaged) and in the inspection (possibly damaged) configuration, then the
+difference between the two values, denoted respectively by $E_0(z_l)$ and $E_d(z_l)$, can provide an indication about the existence of
+degradation at location $z_l$:
+\begin{equation}
+\Delta E(z_l) = E_d(z_l) - E_0(z_l)
+\end{equation}
+
+An increase in the interpolation error between the reference configuration and the current configuration at a station $z_l$ , i.e.
+$ \Delta E(z_l) > 0$, highlights a localized reduction of smoothness in the vibrational amplitude profile and, therefore, it is assumed
+to be a symptom of a local variation of stiffness at $z_l$ associated with the occurrence of damage.
+
+\subsection{Interpolation}
+
+We have to calculate for each sensor $z_l$ and for each considered frequency $f_i$ the cubic polynomial spline interpolation of the transfer function $H_R(z_k,f_i)$.
+The cubic spline interpolation is a piecewise continuous curve, passing through each of the values.
+There is a separate cubic polynomial interpolation for each interval, each with its own coefficients.
+This is for this local aspect that we use this interpolation, since we want to detect local iregularities.
+Cubic polynomial spline interpolations produce an interpolated function that is continuous through to the second derivative.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.25\textwidth]{images/interpolation_spline.png}
+  \caption{Cubic spline interpolation}
+  \label{spline}
+\end{figure}
+
+With this interpolation, we can calculate the error as it is described previously.
+
+\subsection{Threshold}
+
+The above analysis has been developed in a deterministic context. Several sources, such as temperature, nonlinear
+behavior, soil structure interaction and noise in recorded data, can induce variations of the interpolation error even if no
+damage occurs.
+
+Thus, we can have different values of the error interpolation for a same state.
+Heowever, the distributions of the erros for a same state is close to a gaussian distribution.
+The problem is that the distributions for a undamaged and a damaged states can be near.
+
+So that means once have to determine a threshold $E_T$, such as $ \Delta E(z_l)$ must be taller than $E_T$ to have a high probability of identification of a damage at location $z_l$.
+Indeed, as we can see in the Figure (\ref{proba}), the curves which represent the fact to have a damage or not have a share area: if the interpolation error $ \Delta E(z_l)$ is in this area, one can commit two errors:
+\begin{itemize}
+\item if it is in the area $P_f(z_l)$ under the graph of $p_{E,0}(z_l)$, once can detect a damage since there isn't one (false alarm).
+\item if it is in the area $P_m(z_l)$ under the graph of $p_{E,d}(z_l)$, once can not detect a damage since there is one (missing alarm).
+\end{itemize}
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.4\textwidth]{images/explication_FP.png}
+  \caption{Probabilities of false and missing alarm, from \cite{dilena2015damage}}
+  \label{proba}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\begin{tabular}{|c|c|c|}
+\hline
+\ & Damaged & Undamaged \\ \hline
+Detected & TP & FP \\ \hline
+No detected & FN & TN \\ \hline
+\end{tabular}
+\end{center}
+\caption{True/False positives and negatives}
+\label{TFPN}
+\end{figure}
+
+Now, to denote corect detection (or no detection), we will use the terms true positives and negatives, to denote missing alarms we will use false negatives and for false alarms, we will use false positives.
+
+In our experiences, we measure the number of true/false positives and negatives. The figure(\ref{TFPN}) present the notations used for the number of true/false positives and negatives.
+
+To evaluate the two methods, we use the specificity predictive factors, which are 
+$\frac{TP}{TP + FP}$ and $\frac{TN}{TN + FN}$.
+The first correspond to the probability that there is a damage when we detect one, and the second correspond to the probability there isn't any damage when we detect nothing.
+A good method has the two factors near to 1.
+
+\subsection{A variant of the method}
+
+We propose here a variant of the FRF interpolation method.
+While we have worked on the implementation of the original method, we have observed the theoretical FRF to see if the FRF interpolation method worked on that.
+We noticed that the following method is better than the interpolation method (compute the interpolation error, then compute a difference) to detect damaged on the eigenvectors:
+\begin{itemize}
+\item first, compute the difference between the eigenvectors
+\item second, compute the interpolation error on this difference
+\end{itemize}
+
+Figure(\ref{theodiff}) shows the difference betweem the two FRF, and we can see the loss of spatial regularity (damage at position 7).
+In comparaison with the Figure(\ref{theo}), we can see here there is only one iregularity: the fact to compute the difference before the interpolation erase iregularity when they are in the two states.
+With the initial method, they are also erase when we compute the difference between the interpolation errors.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.3\textwidth]{images/theodiff60.png}
+  \caption{Difference betweem theoretical FRF of undamaged and damage states}
+  \label{theodiff}
+\end{figure}
+
+Thus, we also study in this paper a variant of the FRF interpolation method . The only difference with the original method is the order of the steps:
+\begin{itemize}
+\item Compute the FRF
+\item Compute the difference between the FRF of reference and the FRF of the studied state, for each frequency
+\item Compute the interpolation error of these differencies
+\item Compute the sum of the interpolation errors at each frequency
+\end{itemize}
+
+From now on, to tell the difference between the two methods, we shall call our variant the FRF difference method.
+
+\section{Simulation}
+
+We have implemented a simulation to obtain the data used to check the methods of localization. To explain it, we detil here the following system we used for our experiences: $n$ masses, connected
 through springs and dampers. We denote the masses $\{m_i\}_{i=1}^n$, the springs stifness $\{k_i\}_{i=1}^n$ and the dampers $\{c_i\}_{i=1}^n$ (see Figure (\ref{springs})).
@@
 
-For the following simulation results, we consider a system with 10 masses.
+For the following simulation results, we consider a system with 20 masses.
 We put a sensor on each mass.
 For the damaged state, we lower the stifness of the spring between sensors 6 and 7.
-The values of the FRF on the figures are the norm of the FRF values.
+The values of the FRF on the figures are the norm of the complex FRF values.
 
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{images/detect_curve_without_noise.png}
+  \includegraphics[width=0.4\textwidth]{images/detect004.png}
   \caption{Damage detection rate against damage (without noise)}
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{images/detect_curve_with_005noise.png}
+  \includegraphics[width=0.4\textwidth]{images/detect_noise004.png}
   \caption{}
@@
 
+Figure (\ref{pred_max}) shows the predicitve factor with this method.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.4\textwidth]{images/pred_max.png}
+  \caption{Predictive factor}
+  \label{pred_max}
+\end{figure}
+
 \subsection{FRF interpolation method on a beam}
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{images/quantification_without_noise_100.png}
+  \includegraphics[width=0.4\textwidth]{images/quantification.png}
   \caption{}

### 2017-03-31 code_solo/damage.py

@@ -25,7 +25,7 @@ SAMPLVALUE = 10000
 MAKEREF = 100
 DAMAGED_SENSOR = [7]#must be a list
 EXCITED_SENSOR = 0
-DAMAGE = 8# % of damage
+DAMAGE = 1# % of damage
 
 pos = [ k for k in range(CAPTVALUE) ]
 z = [ 0 for k in range(CAPTVALUE) ]

### 2017-03-31 code_solo/damage_noise.py

@@ -24,7 +24,7 @@ CAPTVALUE = 20
 SAMPLVALUE = 10000
 MAKEREF = 100
 DAMAGED_SENSOR = [7]#must be a list
-DAMAGE = 5# % of damage
+DAMAGE = 33# % of damage
 
 pos = [ k for k in range(CAPTVALUE) ]
 z = [ 0 for k in range(CAPTVALUE) ]

### 2017-03-31 code_solo/data/detect.py

@@ -1,7 +1,8 @@
 import parser as pa
 import matplotlib.pyplot as plt
 
-error = [0,1, 2, 3, 4, 5, 8, 10, 13, 15, 20, 30]#12
+error = [0,1, 2, 3, 4, 5, 8, 10, 13, 15, 20, 30,40,50,60,70]#12
+error = [1,5,10,15,20,30,40,50,60,70]#il faudrait ajouter autour de 18
 
 DAMAGED_SENSOR = 7
 

### 2017-03-31 code_solo/data/detect_noise.py

@@ -11,7 +11,7 @@ DAMAGED_SENSOR = 7
 #error = [2,3,4,5,7,8,9,10,12,14,15,20]
 
 NOISE = 0.04
-error = [5,10,15,20,25,30]
+error = [5,10,15,20,25,30,40]
 
 def tp(t):
 	return max(t[DAMAGED_SENSOR-1], t[DAMAGED_SENSOR])

### 2017-03-31 code_solo/data/fp.py

@@ -1,7 +1,8 @@
 import parser as pa
 import matplotlib.pyplot as plt
 
-error = [1, 2, 3, 4, 5, 10, 20, 30]
+error = [1, 2, 3, 4, 5, 10, 20, 30,40,50,60,70]
+error = [1,5,10,15,20,30,40,50,60,70]
 
 DAMAGED_SENSOR = 7
 

### 2017-04-04 rapport/paper.tex
rapport

@@
 
-Figure (\ref{frf_freq}) presents results of the FRF on the simulation datas: here is the curve of the FRF of one sensor, against frequencies.
+Figure (\ref{frf_freq}) presents results of the FRF on the simulation data: here is the curve of the FRF of one sensor, against frequencies.
 We can see peaks which are at the natural frequencies of the system, but there is one of these frequencies which not present a peak.
@@
 With the FRF interpolation method, we have compute two thresholds from 100 experiments with the undameged state.
-The first is the maximum of the 100 errors computed.
+The first is the error just below the maximum of the 100 errors computed.
 The second is computed from the statistics of the 100 errors computed: we suppose that the probability of the error follow a normal distribution, and we choose the threshold at 95\% of this distribution.
+
+From now on, the majority of the figures will show four curves:
+\begin{itemize}
+\item in blue (deep): results for the FRF interpolation method with a threshold at 99\% of the reference errors
+\item in green: results for the FRF interpolation method with a threshold at 95\% of the reference distribution
+\item in red: results for the FRF difference method with a threshold at 99\% of the reference errors
+\item in blue (light): results for the FRF difference method with a threshold at 95\% of the reference distribution
+\end{itemize}
+
+To disting the two methods with the two thresholds, we denote them with the color initials: the first one BD, the second one G, the third one R and the last one BL.
 
@@
 
-Figure() presents the results of the localization of a damage on sensor 7, without noise.
+Figure(\ref{damage30}) presents the results of the localization of a damage of 30\% between sensors 6 and 7, without noise.
+It shows the percent of detection of a damage against its position.
+We can see that the damage between sensors 6 and 7 are always detected, but there is also detection on other sensors (that is false positives).
 
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{images/detect004.png}
+  \includegraphics[width=0.4\textwidth]{images/damage30percent.png}
+  \caption{Damage detection rate for a damage between sensors 6 and 7 (without noise)}
+  \label{damage30}
+\end{figure}
+
+Figure(\ref{detect}) presents the percent of detection of a damage between sensors 6 and 7 against the damage percent (a single damage is always simulated on sensor 7).
+We can see here that below 5\% of damage, none of the methods detect the damage more than 50\% of the time, but we can see that BL is the best: at 10\% of damage, it reach 90\% of detection, while the others are below 30\%.
+However, at 15\% of damage, it's BD and G which are the best, with 100\% of detection.
+BL reaches 100\% of detection at 20\% of damage, and R reaches it at 30\% of damage.
+Here, R seems to be the worst.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.4\textwidth]{images/detect.png}
   \caption{Damage detection rate against damage (without noise)}
@@
 \end{figure}
+
+Figure(\ref{fp}) presents the percent of false positives against the damage percent.
+Here, R is the best: around 2\% of false positives regardless of the percent of damage, while the others are between 5\% and 25\%.
 

### 2017-04-04 code_solo/data/detect.py

@@ -3,6 +3,7 @@ import matplotlib.pyplot as plt
 
 error = [0,1, 2, 3, 4, 5, 8, 10, 13, 15, 20, 30,40,50,60,70]#12
 error = [1,5,10,15,20,30,40,50,60,70]#il faudrait ajouter autour de 18
+error = [1,5,10,15,20,30]
 
 DAMAGED_SENSOR = 7
 

### 2017-04-04 rapport/paper.tex
small collection

@@
  namely the FRF interpolation method \cite{dilena2015damage}.
-Our contribution is the development of a simulation to obtain acceleration measurement (which can run on several structures), a proposition of a variant of the FRF interpolation method, and the statistical analysis of the two methods.
-This paper is organized as follows. In section II we  present the existing methods (model-based and data driven methods), 
+Our contribution is the development of a simulator to obtain acceleration measurement of different structures, a proposition of a variant of the FRF interpolation method, and a statistical analysis of the two methods.
+
+This paper is organized as follows: In section II we  present the existing methods (model-based and data driven methods),
 then in section III we present different models of vibrating structures required for what happens next.
@@
 
-We have implemented a simulation to obtain the data used to check the methods of localization. To explain it, we detil here the following system we used for our experiences: $n$ masses, connected
+We have implemented a simulation to obtain the data used to check the methods of localization. To explain it, we detail here the following system we used for our experiences: $n$ masses, connected
 through springs and dampers. We denote the masses $\{m_i\}_{i=1}^n$, the springs stifness $\{k_i\}_{i=1}^n$ and the dampers $\{c_i\}_{i=1}^n$ (see Figure (\ref{springs})).
@@
 
-To test the localization, we have to make a thresold for each sensor.
-We want that a computed error taller than the threshold on one sensor is equivalent to have a damage on this sensor.
-With the FRF interpolation method, we have compute two thresholds from 100 experiments with the undameged state.
+To test the localization, we have to make a threshold for each sensor.
+We want that a computed error bigger than the threshold on one sensor is equivalent to have a damage on this sensor.
+With the FRF interpolation method, we have compute two thresholds from 100 experiments with the undamaged state.
 The first is the error just below the maximum of the 100 errors computed.
@@
 \begin{itemize}
-\item in blue (deep): results for the FRF interpolation method with a threshold at 99\% of the reference errors
-\item in green: results for the FRF interpolation method with a threshold at 95\% of the reference distribution
-\item in red: results for the FRF difference method with a threshold at 99\% of the reference errors
-\item in blue (light): results for the FRF difference method with a threshold at 95\% of the reference distribution
+\item in dark blue: results of the FRF interpolation method with a threshold at 99\% of the reference errors
+\item in green: results of the FRF interpolation method with a threshold at 95\% of the reference distribution
+\item in red: results of the FRF difference method with a threshold at 99\% of the reference errors
+\item in blue : results of the FRF difference method with a threshold at 95\% of the reference distribution
 \end{itemize}
 
-To disting the two methods with the two thresholds, we denote them with the color initials: the first one BD, the second one G, the third one R and the last one BL.
+To disting the two methods with the two thresholds, we denote them with the color initials: the first one DB, the second one G, the third one R and the last one B.
 
@@
 Figure(\ref{detect}) presents the percent of detection of a damage between sensors 6 and 7 against the damage percent (a single damage is always simulated on sensor 7).
-We can see here that below 5\% of damage, none of the methods detect the damage more than 50\% of the time, but we can see that BL is the best: at 10\% of damage, it reach 90\% of detection, while the others are below 30\%.
-However, at 15\% of damage, it's BD and G which are the best, with 100\% of detection.
-BL reaches 100\% of detection at 20\% of damage, and R reaches it at 30\% of damage.
+We can see here that below 5\% of damage, none of the methods detect the damage more than 50\% of the time, but we can see that B is the best: at 10\% of damage, it reach 90\% of detection, while the others are below 30\%.
+However, at 15\% of damage, it's DB and G which are the best, with 100\% of detection.
+B reaches 100\% of detection at 20\% of damage, and R reaches it at 30\% of damage.
 Here, R seems to be the worst.

### 2017-04-04 rapport/paper.tex
com

--- 2017-04-04 rapport/paper.tex
@@
 
-Figure(\ref{detect}) presents the percent of detection of a damage between sensors 6 and 7 against the damage percent (a single damage is always simulated on sensor 7).
+Figure(\ref{detect}) presents the percent of detection of a damage between sensors 6 and 7 against the damage percent (a single damage is always simulated between sensors 6 and 7).
 We can see here that below 5\% of damage, none of the methods detect the damage more than 50\% of the time, but we can see that BL is the best: at 10\% of damage, it reach 90\% of detection, while the others are below 30\%.
@@
 
-Figure (\ref{itp_error_noise}) presents the results of the localization of a damage on sensor 7, where noise (5\%) has been add at the measurement.
+Figure (\ref{damage30noise}) presents the results of the localization of a damage of 30\% between sensors 6 and 7, where noise (5\%) has been add at the measurement.
+We can see that results are similar that without noise.
 
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{images/damage_noise_10percent.png}
-  \caption{Error computed for a damage of 10\% on sensor 7}
-  \label{itp_error_noise}
+  \includegraphics[width=0.4\textwidth]{images/damage30percent004noise.png}
+  \caption{Damage detection rate for a damage between sensors 6 and 7 (with 5\% of noise)}
+  \label{damage30noise}
 \end{figure}
+
+However, we can see on Figure(\ref{detect_noise}) that the rate of true positives is impacted by the noise: the G and BD methods reach 100\% of detection at 20\% of damage and the R and BL methods reach it at 40\% of damage.
 
@@
   \includegraphics[width=0.4\textwidth]{images/detect_noise004.png}
-  \caption{}
-  \label{detect_5noise}
+  \caption{Damage detection rate against damage (with 5\% of noise)}
+  \label{detect_noise}
 \end{figure}
+
+For the false positives rate, we can notice that the R method is always the best, but the BL method is better than without noise.
 
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{images/detect_curve_with_01noise.png}
-  \caption{}
-  \label{detect_10noise}
+  \includegraphics[width=0.4\textwidth]{images/fp004.png}
+  \caption{False positives rate with 5\% of noise}
+  \label{fp_noise}
 \end{figure}
+
+With the noise, we can so do two observations: first, the FRF interpolation method has a better localization for small damages than the FRF difference method, second,  the FRF difference method has a better false positives rate than the FRF interpolation method.
+
+\subsection{Eliminate the false positives to improve the efficiency}
+
+First, we present here the the predictive factors for our methods.
+
+Figure (\ref{pred}) shows the predictive positive factor. We can see that the R method is the best.
 
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{images/fp_noise005.png}
-  \caption{}
-  \label{fp_5noise}
+  \includegraphics[width=0.4\textwidth]{images/pred.png}
+  \caption{Predictive factor}
+  \label{pred}
 \end{figure}
 
-\subsection{Eliminate the false positives to improve the efficiency}
+Figure (\ref{pred_neg}) shows the predictive negative factor with this method. We can see that all the method reach 1 at 30\% of damage, and are a factor higher than 0.9 for small damages.
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.4\textwidth]{images/pred_neg.png}
+  \caption{Predictive negative factor}
+  \label{pred_neg}
+\end{figure}
 
-We have seen that there are too many false positives.
+We can see that the predictive negative factor isn't bad, but the positive one can be better.
+To improve it, we must have less false positives.
 We try to remove them with the next idea: the difference between the threshold and the computed values is larger on the damage than on other sensors.
@@
 
-Figure (\ref{detect_max}) shows the results of this method.
-
 \begin{figure}[h!]
@@
 
-Figure (\ref{pred_max}) shows the predicitve factor with this method.
+Figure (\ref{detect_max}) shows the results of this method. We can see that all the false positives are eliminated.
+
+Figure (\ref{pred_max}) shows the predictive factor with this method. We can see that all the method reach 1 at 30\% of damage. That is what you wanted to obtain with this method.
 
@@
 \end{figure}
+
+Figure (\ref{pred_neg_max}) shows the predictive negative factor with this method.
+We can see that this factor is similar at the factor for the initial methods.
+It could be worst, but it's not the case.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.4\textwidth]{images/pred_neg_max.png}
+  \caption{Predictive negative factor}
+  \label{pred_neg_max}
+\end{figure}
+
+We have here improved the methods, because we eliminate the false positives. The only requirement is to have a detection method.
 
@@
 
-We shows in Figure(\ref{quant}) the computed error, in percent of the threshold.
+We shows in Figure(\ref{quant}) the computed error, in percent of the threshold. We can see that its evolution is linear against the damage percent.
+It could permit to quantify the damage.
 

### 2017-04-04 code_solo/data/fp_noise.py

@@ -7,7 +7,7 @@ DAMAGED_SENSOR = 7
 #NOISE = 0.05
 
 NOISE = 0.04
-error = [5,10,15,20,25,30]
+error = [5,10,15,20,30,40]
 
 
 def fp(t):

### 2017-04-14 rapport/paper.tex
MAJ rapport

@@
 For aerospace, civil and mechanical engineering infrastructure, implementing a damage identification strategy is referred as a structural health monitoring.
-With the help of accelerometers, a frequency point of view allows monitoring without the needs of human presence.
+With the help of accelerometers, a vibration analysis allows monitoring without the needs of human presence.
 The damage identification can be divided into four levels: detection, localization, quantification and prediction.
-We present the existing methods for the detection and the localization of damage, then we detail one of them, namely the Frequency Response Function interpolating method.
-We also analyse this method with a simulation of a spring–mass system, and discuss the results.
+We present existing methods for the detection and the localization of damage, and detail one of them, namely the Frequency Response Function interpolating method.
+We analyse this method in a statistical sense and illustrate it with a simulation of a spring–mass system and a beam, and discuss the results.
 
@@
 
-Almost all industries want to detect damage in their infrastructure as quickly as possible whether
+It is of interest to detect damage in infrastructure as quickly as possible whether
  for the potential life-safety or economic impact.
-Such detection requires these industries to perform some form of SHM.
+Such detection requires industries to perform some form of SHM.
 
-Clearly, such damage identification has significant life-safety implications.
 For instance, there are  no quantifiable methods to
@@
 Traditional methods of damage detection based on visual inspections or experimental techniques such as radiography
- or ultrasound allow to obtain detailed information about a local damage state but requires to know area where it is located (and hope for easy access).
+ or ultrasound allow to obtain detailed information about a local damage state but requires to know the area where it is located (and hope for easy access).
 These techniques may be costly, taking a long time to be performed and impractical to detect damage in large urban areas.
@@
 
-The use of methods based on recorded responses proved to perform as valuable alternatives.
+The use of methods based on recorded vibration responses proved to perform as valuable alternatives.
 The general idea for vibration-based damage identification is that the damage affects the physical properties (mass, damping, and stiffness) of the structure, and this will cause detectable changes in modal properties (natural frequencies, modal damping, and mode shapes).
-For instance, cracks cause reductions in stiffness. Therefore, by analyzing the physical properties of the structure a damage can be detected.
+For instance, cracks cause reductions in stiffness. Therefore, by analyzing the dynamic properties of the structure a damage can be detected.
 \\
@@
 Most of the different vibration based damage identification methods can be classified as data-driven or model-based.
- The model-based methods assume that a detailed numerical model of the structure is available for damage identification and, by vibration measurements, updates the model parameters.
- On another side, data-driven methods are based solely on the recorded response.
+% The model-based methods assume that a detailed numerical model of the structure is available for damage identification and, by vibration measurements, updates the model parameters.
+% On another side, data-driven methods are based solely on the recorded response.
 These methods are interesting for a real-time damage identification but unavailability of a numerical model often hinders the estimation of damage severity.
@@
 
-\subsection{Model-based methods}
+\subsection{Finite Element model-based methods}
 
 In model-based methods, damage is identified through the updating of a finite element (FE) model.
- Most of the time, modal characteristics is the experimental data used for damage assessment through FE model updating.% which are extracted from measured response time histories using modal analysis techniques.
-Different types of modal data can be used. For changes in structural stiffness, model updating can be performed based only on natural frequencies or eigenvalues which are known to change in this case.
+% Most of the time, modal characteristics is the experimental data used for damage assessment through FE model updating.% which are extracted from measured response time histories using modal analysis techniques.
+Different types of modal data can be used. For changes in structural stiffness, model updating can be performed based only on modal parameters which are known to change with damage.
+Note that model updating is often an ill-posed problem, requiring engineering expertise, that is difficult to automate.
  Detailed informations about model-based methods can be found in references
@@
 
-Data driven methods are inverse methods that use models based on experimental response data recorded on the structure instead of physical models
+Data driven methods are inverse methods that use models based on response data recorded on the structure instead of physical models
 \cite{limongelli2016towards}.
- In these methods, the damage parameter $D$ is the variation of the damage feature $d$ between the inspection $I$ and the reference $R$ configurations: %Damage-sensitive features are extracted from data and their changes used to identify damage in the structures so the damage parameter D in these method is the variation of the damage feature f between the inspection I and the reference R configurations.
+Here, a FE model isn't necessary, only recorded data are analyzed.
+ In these methods, the damage parameter $D$ is the variation of a damage feature $d$ between the inspection $I$ and the reference $R$ configurations: %Damage-sensitive features are extracted from data and their changes used to identify damage in the structures so the damage parameter D in these method is the variation of the damage feature f between the inspection I and the reference R configurations.
 % référence TOWARDS EXTRACTION OF VIBRATION-BASED DAMAGE INDICATORS
@@
 A third group of methods for damage localization and quantification lies between the data-driven and model-based approaches.
- "This class is based on datadriven features from measurements of the reference and damaged states, which are confronted to a FE model of the structure to define damage indicators for the elements of the FE model,
- without updating its parameters" \cite{limongelli2016towards}. %rajouter référence au papier
+Damage features are computed from both the data and the FE model, without updating the model.
+% "This class is based on datadriven features from measurements of the reference and damaged states, which are confronted to a FE model of the structure to define damage indicators for the elements of the FE model,
+% without updating its parameters" \cite{limongelli2016towards}. %rajouter référence au papier
 % référence TOWARDS EXTRACTION OF VIBRATION-BASED DAMAGE INDICATORS
@@
 
-In this section, we present the physical models that we use to obtain data for our experiences, and the Frequency Response Function (FRF) which is the base of the FRF interpolation method.
+In this section, we present the dynamic models for vibration analysis, and the Frequency Response Function (FRF) which is the base of the FRF interpolation method.
 
-\subsection{Finite element model}
+\subsection{Equation of motion}
 
-The dynamic behaviour of a mechanical system consisting of $n$ degrees of freedom (see Figure (\ref{finite_el})) is described by following matrix differential equation:
+The dynamic behaviour of a mechanical system consisting of $n$ degrees of freedom is described by following matrix differential equation:
 \begin{equation}
@@
 \end{equation}
-where $q(t)$ is the displacement vector at a continous time $t$, $f(t)$ is the excitement vector at $t$ and $M, C, K \in \mathbb{R}^{n \times n}$, are the mass, damping and stiffness matrices.
+where $q(t)$ is the displacement vector at a continous time $t$, $f(t)$ is the external force vector at $t$ and $M, C, K \in \mathbb{R}^{n \times n}$, are the mass, damping and stiffness matrices.
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[height=0.3\textwidth]{images/finite_element.png}
-  \caption{Finite element model, from \cite{peeters2000system}}
-  \label{finite_el}
-\end{figure}
-
-For civil engineering structures, Equation (\ref{fondamental}) is obtained as the finite element approximation of the system with only $n$ dregrees of freedom.
+In real applications, only measurement data (forces $f$, most of accelerations $\ddot{q}$) are available, but matrices $M, C$ and $K$ are unknown.
+For the purpose of simulating civil engineering structures, matrices $M, C$ and $K$ can be modeled through a
+finite element approximation of the system with only $n$ dregrees of freedom.
 The structure is divided in elements, and the global mass matrix $M$ and stiffness matrix $K$ are generated from the geometry and material
@@
 
-From the Equation (\ref{fondamental}) and with the variable change $x =
+For data analysis, Equation (\ref{fondamental}) is transformed. With the variable change $x =
 \begin{pmatrix}
@@
 
-If it is assumed that all $n$ degrees of freedom are measured and that the sensors are accelerometers transducers, we have
+If it is assumed that all $n$ degrees of freedom are measured and that the sensors are accelerometers, we have
 $C_c =
@@
 
-The FRF correspond to the transfer function of the system. In frequency domain, if $F$ is the force that is apply on the system and $X$ is the response of this force, the FRF is given by:
+The FRF correspond to the transfer function of the system and reflects its dynamic behavior.
+In frequency domain, if $F(s)$ is the force that is applied on the system and $X(s)$ is the response of this force, the transfer function is given by:
 \begin{equation}
-H = \frac{X}{F}
+H(s) = \frac{X(s)}{F(s)}
 \end{equation}
 
-We can express the theoretical FRF with the matrices $M, C, K$. Indeed, in the frequency domain, we have
+We can express the theoretical transfer function with the matrices $M, C, K$. Indeed, in the frequency domain, we have
 \begin{equation}
-s^2 M x + s C x + K x = f
+s^2 M X(s) + s C X(s) + K X(s) = F(s)
 \end{equation}
-where s is $i\omega$, with $\omega$ the pulsation.
-Thus, the FRF $H$ is:
+Thus, the transfer function $H$ is:
 \begin{equation}
-H = \frac{x}{f} = (s^2 M + s C + K)^{-1}
+H(s) = \frac{X(s)}{F(s)} = (s^2 M + s C + K)^{-1}
+\label{changes}
 \end{equation}
 
+The FRF is evaluated at $s = i \omega$, with $\omega$ the pulsation.
 In practice, we want to calculate the FRF of the system, for each sensor localization.
+The FRF is calculated for each sensor location and each frequency $\omega_j = \frac{2\pi}{\Delta t} \frac{j}{N}$.
 Here, we calculate an estimation of the FRF, called $H_1$ estimator \cite{cauberghe2004applied}.
@@
 \begin{array}{ll}
-F_n = \sum\limits_{k=1}^N f_k e^{-2i\pi kn/N} \ \ \ \ \ n \in \{1 ... N\} \\
-Y_n = \sum\limits_{k=1}^N y_k e^{-2i\pi kn/N} \ \ \ \ \ n \in \{1 ... N\}
+F_j = \sum\limits_{k=1}^N f_k e^{-2i\pi kj/N} \ \ \ \ \ j \in \{1 ... N\} \\
+Y_j = \sum\limits_{k=1}^N y_k e^{-2i\pi kj/N} \ \ \ \ \ j \in \{1 ... N\}
 \end{array}
@@
 \begin{array}{ll}
-S_{ff}(n) = F_n F_n^H \ \ \ \ \ n \in \{1 ... N\} \\
-S_{yf}(n) = Y_n F_n^H \ \ \ \ \ n \in \{1 ... N\}
+S_{ff}(j) = F_j F_j^H \ \ \ \ \ j \in \{1 ... N\} \\
+S_{yf}(j) = Y_j F_j^H \ \ \ \ \ j \in \{1 ... N\}
 \end{array}
@@
 \begin{equation}
-H_1(n) = S_{yf}(n) S_{ff}(n)^{-1}
+H_1(j) = S_{yf}(j) S_{ff}(j)^{-1}
 \end{equation}
@@
 \begin{array}{lll}
-H_1(n) & = & S_{yf}(n) S_{ff}(n)^{-1} \\
-& = & Y_n F_n^H (F_n F_n^H)^{-1} \\
-& = & Y_n / F_n
+H_1(j) & = & S_{yf}(j) S_{ff}(j)^{-1} \\
+& = & Y_j F_j^H (F_j F_j^H)^{-1} \\
+& = & Y_j / F_j
 \end{array}
+\label{estimate}
 \end{equation}
@@
 
+Changes due to damage induces changes in the FRF due to Equation(\ref{changes}).
+The FRF interpolation method analyses those changes based only on measurements of the system, computed from Equation(\ref{estimate}) without needing a FE model of the structure.
+
 This method is presented in \cite{dilena2015damage}.
@@
 
-Figure (\ref{theo}) shows this loss of spatial regularity on the theoretical FRF, for a damage at the position 7.
+Figure \ref{theo} shows this loss of spatial regularity on the theoretical FRF, for a damage at the position 7.
 We can see there is a loss of regularity at the position 7 for the damaged state.
-We can also see there is an iregularity at the position 2, but here the two states have the same iregularity, so it's not a loss of regularity.
+We can also see there is an iregularity at the position 2, but here the two states have the same iregularity, so it's not a loss of regularity compared to the reference state.
 
@@
 
-In this section, we suppose that we have $n$ sensors, which are located along an axis $z$, and we denote them by
-$\{z_l\}, l\in \{1 ... n\}$ (that is their position on the axis $z$). We also suppose we have $N$ measurements for each sensor.
+We suppose that we have $n_s$ sensors, which are located along an axis $z$, and we denote them by
+$\{z_l\}, l\in \{1 ... n_s\}$ (that is their position on the axis $z$). We also suppose we have $N$ measurements for each sensor.
 
@@
 
-Thus, for each frequency and each sensor, we have the transfer function value. Let us denote $H_R(z_l,f_i)$ the value of the transfer function for  the sensor $z_l$ at the frequency $f_i$.
+Thus, for each frequency and each sensor, we have the transfer function value.
+Let us denote $H_R(z_l,j) = H_1^l(j)$ ($l^{th}$ entry of $H_1$) the value of the transfer function for the sensor $z_l$ at the frequency line $j$, corresponding to $\omega_j$.
 
-Then, we calculate for each sensor $z_l$ the cubic polynomial spline interpolation of the transfer functions $H_R(z_k,f_i)$ measured at all
-the other instrumented locations $\{z_k\}, k\in \{1 ... n\}, k \neq l$: we denote it $H_S(z_l,f_i)$.
+Then, we calculate for each sensor $z_l$ the cubic polynomial spline interpolation of the transfer functions $H_R(z_k,j)$ measured at all
+the other instrumented locations $\{z_k\}, k\in \{1 ... n\}, k \neq l$: we denote it $H_S(z_l,j)$.
+The cubic spline interpolation is a piecewise continuous curve, passing through each of the values.
+There is a separate cubic polynomial interpolation for each interval, each with its own coefficients.
+This is for this local aspect that we use this interpolation (other interpolations can also be used), since we want to detect local iregularities.
+Cubic polynomial spline interpolations produce an interpolated function that is continuous through to the second derivative.
 
@@
 \begin{equation}
-E(z_l,f_i) = | H_R(z_l,f_i) - H_S(z_l,f_i) |
+E(z_l,j) = | H_R(z_l,j) - H_S(z_l,j) |
 \end{equation}
 
-We can see this error on the Figure(\ref{interpolation_error}).
+We can see this error on the Figure \ref{interpolation_error}.
 
@@
   \includegraphics[width=0.4\textwidth]{images/interpolation.png}
-  \caption{Interpolation error, from \cite{dilena2015damage}}
+  \caption{Interpolation error}
   \label{interpolation_error}
@@
 \begin{equation}
-E(z_l) = \sqrt{  \sum\limits_{i=1}^N  E^2(z_l,f_i) }
+E(z_l) = \sqrt{  \sum\limits_{j=1}^N  E^2(z_l,j) }
 \label{error}
@@
 
-\subsection{Interpolation}
-
-We have to calculate for each sensor $z_l$ and for each considered frequency $f_i$ the cubic polynomial spline interpolation of the transfer function $H_R(z_k,f_i)$.
-The cubic spline interpolation is a piecewise continuous curve, passing through each of the values.
-There is a separate cubic polynomial interpolation for each interval, each with its own coefficients.
-This is for this local aspect that we use this interpolation, since we want to detect local iregularities.
-Cubic polynomial spline interpolations produce an interpolated function that is continuous through to the second derivative.
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.25\textwidth]{images/interpolation_spline.png}
-  \caption{Cubic spline interpolation}
-  \label{spline}
-\end{figure}
-
-With this interpolation, we can calculate the error as it is described previously.
-
 \subsection{Threshold}
@@
 Thus, we can have different values of the error interpolation for a same state.
-Heowever, the distributions of the erros for a same state is close to a gaussian distribution.
-The problem is that the distributions for a undamaged and a damaged states can be near.
+The distributions of the erros for a state is close to a gaussian distribution.
+The problem is that the distributions for an undamaged and a damaged states can be near.
 
-So that means once have to determine a threshold $E_T$, such as $ \Delta E(z_l)$ must be taller than $E_T$ to have a high probability of identification of a damage at location $z_l$.
-Indeed, as we can see in the Figure (\ref{proba}), the curves which represent the fact to have a damage or not have a share area: if the interpolation error $ \Delta E(z_l)$ is in this area, one can commit two errors:
+For a decision that an interpolation error belongs to the healthy or damaged state, once have to determine a threshold $E_T$, such as $ \Delta E(z_l)$ must be taller than $E_T$ to have a high probability of identification of a damage at location $z_l$.
+Indeed, as we can see in the Figure \ref{proba}, the curves which represent the fact to have a damage or not have a share area: if the interpolation error $ \Delta E(z_l)$ is in this area, one can commit two errors:
 \begin{itemize}
-\item if it is in the area $P_f(z_l)$ under the graph of $p_{E,0}(z_l)$, once can detect a damage since there isn't one (false alarm).
-\item if it is in the area $P_m(z_l)$ under the graph of $p_{E,d}(z_l)$, once can not detect a damage since there is one (missing alarm).
+\item if it is in the red area (FP), once can detect a damage since there isn't one (false alarm).
+\item if it is in the green area (FN), once can not detect a damage since there is one (missing alarm).
 \end{itemize}
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{images/explication_FP.png}
-  \caption{Probabilities of false and missing alarm, from \cite{dilena2015damage}}
+  \includegraphics[width=0.4\textwidth]{images/gaussiennes.png}
+  \caption{Probabilities of false and missing alarm}
   \label{proba}
@@
 
-In our experiences, we measure the number of true/false positives and negatives. The figure(\ref{TFPN}) present the notations used for the number of true/false positives and negatives.
+In our experiences, we measure the number of true/false positives and negatives. The Figure \ref{TFPN} present the notations used for the number of true/false positives and negatives.
 
@@
 While we have worked on the implementation of the original method, we have observed the theoretical FRF to see if the FRF interpolation method worked on that.
-We noticed that the following method is better than the interpolation method (compute the interpolation error, then compute a difference) to detect damaged on the eigenvectors:
+We noticed that the following procedure may magnify irregularities of the FRF:
 \begin{itemize}
-\item first, compute the difference between the eigenvectors
+\item first, compute the difference between the FRF
 \item second, compute the interpolation error on this difference
@@
 
-Figure(\ref{theodiff}) shows the difference betweem the two FRF, and we can see the loss of spatial regularity (damage at position 7).
-In comparaison with the Figure(\ref{theo}), we can see here there is only one iregularity: the fact to compute the difference before the interpolation erase iregularity when they are in the two states.
+Figure \ref{theodiff} shows the difference betweem the two FRF, and we can see the loss of spatial regularity (damage at position 7).
+In comparison with the Figure \ref{theo}, we can see here there is only one iregularity: the fact to compute the difference before the interpolation erase iregularity when they are in the two states.
 With the initial method, they are also erase when we compute the difference between the interpolation errors.
@@
 We have implemented a simulation to obtain the data used to check the methods of localization. To explain it, we detail here the following system we used for our experiences: $n$ masses, connected
-through springs and dampers. We denote the masses $\{m_i\}_{i=1}^n$, the springs stifness $\{k_i\}_{i=1}^n$ and the dampers $\{c_i\}_{i=1}^n$ (see Figure (\ref{springs})).
+through springs and dampers. We denote the masses $\{m_i\}_{i=1}^n$, the springs stifness $\{k_i\}_{i=1}^n$ and the dampers $\{c_i\}_{i=1}^n$ (see Figure \ref{springs}).
 
@@
 
-Figure (\ref{frf_freq}) presents results of the FRF on the simulation data: here is the curve of the FRF of one sensor, against frequencies.
+Figure \ref{frf_freq} presents results of the FRF on the simulation data: here is the curve of the FRF of one sensor, against frequencies.
 We can see peaks which are at the natural frequencies of the system, but there is one of these frequencies which not present a peak.
@@
 
-Figure(\ref{damage30}) presents the results of the localization of a damage of 30\% between sensors 6 and 7, without noise.
+Figure \ref{damage30} presents the results of the localization of a damage of 30\% between sensors 6 and 7, without noise.
 It shows the percent of detection of a damage against its position.
@@
 
-Figure(\ref{detect}) presents the percent of detection of a damage between sensors 6 and 7 against the damage percent (a single damage is always simulated on sensor 7).
+Figure \ref{detect} presents the percent of detection of a damage between sensors 6 and 7 against the damage percent (a single damage is always simulated on sensor 7).
 We can see here that below 5\% of damage, none of the methods detect the damage more than 50\% of the time, but we can see that B is the best: at 10\% of damage, it reach 90\% of detection, while the others are below 30\%.
@@
 
-Figure(\ref{fp}) presents the percent of false positives against the damage percent.
+Figure \ref{fp} presents the percent of false positives against the damage percent.
 Here, R is the best: around 2\% of false positives regardless of the percent of damage, while the others are between 5\% and 25\%.
@@
 
-Figure (\ref{damage30noise}) presents the results of the localization of a damage of 30\% between sensors 6 and 7, where noise (5\%) has been add at the measurement.
+Figure \ref{damage30noise} presents the results of the localization of a damage of 30\% between sensors 6 and 7, where noise (5\%) has been add at the measurement.
 We can see that results are similar that without noise.
@@
 
-However, we can see on Figure(\ref{detect_noise}) that the rate of true positives is impacted by the noise: the G and BD methods reach 100\% of detection at 20\% of damage and the R and BL methods reach it at 40\% of damage.
+However, we can see on Figure \ref{detect_noise} that the rate of true positives is impacted by the noise: the G and BD methods reach 100\% of detection at 20\% of damage and the R and BL methods reach it at 40\% of damage.
 
@@
 
-Figure (\ref{pred}) shows the predictive positive factor. We can see that the R method is the best.
+Figure \ref{pred} shows the predictive positive factor. We can see that the R method is the best.
 
@@
 
-Figure (\ref{pred_neg}) shows the predictive negative factor with this method. We can see that all the method reach 1 at 30\% of damage, and are a factor higher than 0.9 for small damages.
+Figure \ref{pred_neg} shows the predictive negative factor with this method. We can see that all the method reach 1 at 30\% of damage, and are a factor higher than 0.9 for small damages.
 \begin{figure}[h!]
@@
 
-Figure (\ref{detect_max}) shows the results of this method. We can see that all the false positives are eliminated.
+Figure \ref{detect_max} shows the results of this method. We can see that all the false positives are eliminated.
 
-Figure (\ref{pred_max}) shows the predictive factor with this method. We can see that all the method reach 1 at 30\% of damage. That is what you wanted to obtain with this method.
+Figure \ref{pred_max} shows the predictive factor with this method. We can see that all the method reach 1 at 30\% of damage. That is what you wanted to obtain with this method.
 
@@
 
-Figure (\ref{pred_neg_max}) shows the predictive negative factor with this method.
-We can see that this factor is similar at the factor for the initial methods.
-It could be worst, but it's not the case.
+Figure \ref{pred_neg_max} shows the predictive negative factor with this method. We can see that this factor is similar at the factor for the initial methods. It could be worst, but it's not the case.
 
@@
 
-Figure (\ref{beam_curve}) shows two FRF, one for the undamaged state and the second for the damaged one, at a fixed frequency. We can easily see there is an irregularity at the sensor 4.
+Figure \ref{beam_curve} shows two FRF, one for the undamaged state and the second for the damaged one, at a fixed frequency. We can easily see there is an irregularity at the sensor 4.
 
@@
 
-Figure (\ref{beam_error}) shows the computed error. We can see that there are only two sensors with a positiv error, which are the sensors 4 and 5. Thus, the localization is good.
+Figure \ref{beam_error} shows the computed error. We can see that there are only two sensors with a positiv error, which are the sensors 4 and 5. Thus, the localization is good.
 
@@
 
-We shows in Figure(\ref{quant}) the computed error, in percent of the threshold. We can see that its evolution is linear against the damage percent.
+We shows in Figure \ref{quant} the computed error, in percent of the threshold. We can see that its evolution is linear against the damage percent.
 It could permit to quantify the damage.

### 2017-04-14 rapport/paper.tex
MAJ paper

@@
 
-We have implemented a simulation to obtain the data used to check the methods of localization. To explain it, we detail here the following system we used for our experiences: $n$ masses, connected
-through springs and dampers. We denote the masses $\{m_i\}_{i=1}^n$, the springs stifness $\{k_i\}_{i=1}^n$ and the dampers $\{c_i\}_{i=1}^n$ (see Figure \ref{springs}).
+We have implemented a simulation to obtain the data used to analyse the methods of localization. To explain it, we detail here the following system we used for our experiments: $n$ masses, connected
+through springs and dampers. We denote the masses $\{m_i\}_{i=1}^n$, the springs stiffness $\{k_i\}_{i=1}^n$ and the dampers $\{c_i\}_{i=1}^n$ (see Figure \ref{springs}).
 
@@
 
-For the simulation, we use the discrete-time state-space model (Equation (\ref{discrete})). First, we needed the matrices $M, C, K$. In this case, the matrices $M$ and $K$ are given by:
+For the simulation, we use the discrete-time state-space model (Equation (\ref{discrete})). First, we establish the matrices $M, C, K$. In this case, the matrices $M$ and $K$ are given by:
 \begin{equation}
@@
 impossible to assemble the damping matrix C in the same way as M and K.
-Thus, we do the same thing that in practical situations: we consider that we are in the case of Rayleigh, i.e. a linear combination of the mass and stiffness matrix:
+Thus,we consider Rayleigh damping, i.e. a linear combination of the mass and stiffness matrix:
 \begin{equation}
@@
 
-With this matrices, we can calculate the matrices $A_c, B_c, C_c$ and $D_c$. To calculate the matrices $A, B$, we have to know the
+With these matrices, we can calculate the matrices $A_c, B_c, C_c$ and $D_c$. To calculate the matrices $A_d, B_d$, we have to define the
 sampling period $\Delta t$. We need the frequencies of the system, because we have to respect the Nyquist–Shannon sampling theorem.
-To determine the Nyquist frequency (here, it is the taller frequency of the system), we calculate the eigenvalues of $A_c$.
-Indeed, we have the link between the eigenvalues $\{\lambda_i\}_{i=1}^n$ and the frequencies of the system $\{f_i\}_{i=1}^n$:
+To determine the Nyquist frequency which needs to be larger than the frequencies of the system, we calculate the eigenvalues of $A_c$.
+Indeed, we have the link between the eigenvalues $\{\lambda_j\}_{j=1}^n$ and the frequencies of the system $\{f_j\}_{j=1}^n$:
 \begin{equation}
-\lambda_i = - \omega_i \xi_i \pm i \omega_i \sqrt{1 - \xi_i^2}
+\lambda_j = - \omega_j \xi_j \pm i \omega_j \sqrt{1 - \xi_j^2}
 \end{equation}
-where $\omega_i = 2 \pi f_i$ and $\xi_i$ is the damping ratio.
+where $\omega_j = 2 \pi f_j$ and $\xi_j$ is the damping ratio.
 
@@
 We can see that:\\
-$|\lambda_i| = \sqrt{\omega_i^2 \xi_i^2 + \omega_i^2 (1 - \xi_i^2)} = \omega_i$
+$|\lambda_j| = \sqrt{\omega_j^2 \xi_j^2 + \omega_j^2 (1 - \xi_j^2)} = \omega_j$
 \end{remark}
@@
 \begin{equation}
-\Delta t = 2 \times max_{i \in \{1 ... n\} } f_i
+\Delta t = 2 \times max_{j \in \{1 ... n\} } f_j
 \end{equation}
 
-So we can calculate the matrices $A, B$ and make the simulation with the discrete-time state-space model (Equation (\ref{discrete})). To simulate the forces $f_k$, we use a white noise.
+So we can calculate the matrices $A_d, B_d$ and make the simulation with the discrete-time state-space model (Equation (\ref{discrete})). To simulate the forces $f_k$, we use a white noise.
 
@@
 We put a sensor on each mass.
-For the damaged state, we lower the stifness of the spring between sensors 6 and 7.
+For the damaged state, we lower the stiffness of the spring between sensors 6 and 7.
 The values of the FRF on the figures are the norm of the complex FRF values.
@@
 
-To test the localization, we have to make a threshold for each sensor.
-We want that a computed error bigger than the threshold on one sensor is equivalent to have a damage on this sensor.
-With the FRF interpolation method, we have compute two thresholds from 100 experiments with the undamaged state.
+To test the localization, we compute a threshold for each sensor.
+Then, an interpolation error above this threshold indicates damage.
+With the FRF interpolation method, we have computed two thresholds from 100 experiments with the undamaged state.
 The first is the error just below the maximum of the 100 errors computed.
-The second is computed from the statistics of the 100 errors computed: we suppose that the probability of the error follow a normal distribution, and we choose the threshold at 95\% of this distribution.
+The second is computed from the statistics of the 100 errors computed: we suppose that the error follows a normal distribution, and we choose the threshold at 95\% of this distribution.
 
@@
 
-To disting the two methods with the two thresholds, we denote them with the color initials: the first one DB, the second one G, the third one R and the last one B.
+To distinguish the two methods with the two thresholds, we denote them with the color initials: the first one DB, the second one G, the third one R and the last one B.
 
@@
 
-Figure \ref{detect} presents the percent of detection of a damage between sensors 6 and 7 against the damage percent (a single damage is always simulated on sensor 7).
+Figure \ref{detect} presents the percent of detection of a damage between sensors 6 and 7 against the damage extent (a single damage is always simulated on sensor 7).
 We can see here that below 5\% of damage, none of the methods detect the damage more than 50\% of the time, but we can see that B is the best: at 10\% of damage, it reach 90\% of detection, while the others are below 30\%.

### 2017-04-18 rapport/paper.tex
MAJ paper

@@
 Figure \ref{frf_freq} presents results of the FRF on the simulation data: here is the curve of the FRF of one sensor, against frequencies.
-We can see peaks which are at the natural frequencies of the system, but there is one of these frequencies which not present a peak.
-
-Remake figure.
+We can see peaks which are at the natural frequencies of the system.
 
@@
   \centering
-  \includegraphics[width=0.3\textwidth]{images/persensor1.png}
-  \caption{FRF of one sensor (ten in total), against frequencies}
+  \includegraphics[width=0.3\textwidth]{images/frf_one_sensor.png}
+  \caption{FRF of one sensor against frequencies}
   \label{frf_freq}
+\end{figure}
+
+Figure \ref{frf_sensors} presents results of the FRF for all the sensors at one frenquency.
+Curves aren't as regular as the theoretical FRF, but we can see clearly the iregularity between sensors 6 and 7 (there is 10\% of damage here).
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.3\textwidth]{images/frf_one_frequency.png}
+  \caption{FRF for one frequency against sensors}
+  \label{frf_sensors}
 \end{figure}
@@
 
-Figure \ref{pred} shows the predictive positive factor. We can see that the R method is the best.
+Figure \ref{pred} shows the predictive positive and negative factors.
+For the positive one, we can see that the R method is the best.
+For the negative one, we can see that all the method reach 1 at 30\% of damage, and are a factor higher than 0.9 for small damages.
 
@@
   \includegraphics[width=0.4\textwidth]{images/pred.png}
-  \caption{Predictive factor}
+  \includegraphics[width=0.4\textwidth]{images/pred_neg.png}
+  \caption{Predictive positive and negative factors}
   \label{pred}
@@
 
-Figure \ref{pred_neg} shows the predictive negative factor with this method. We can see that all the method reach 1 at 30\% of damage, and are a factor higher than 0.9 for small damages.
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.4\textwidth]{images/pred_neg.png}
-  \caption{Predictive negative factor}
-  \label{pred_neg}
-\end{figure}
+%Figure \ref{pred_neg} shows the predictive negative factor with this method. 
+%\begin{figure}[h!]
+%  \centering
+%  \caption{Predictive negative factor}
+%  \label{pred_neg}
+%\end{figure}
 
@@
 
-Figure \ref{pred_max} shows the predictive factor with this method. We can see that all the method reach 1 at 30\% of damage. That is what you wanted to obtain with this method.
-
 \begin{figure}[h!]
@@
   \includegraphics[width=0.4\textwidth]{images/pred_max.png}
-  \caption{Predictive factor}
+  \includegraphics[width=0.4\textwidth]{images/pred_neg_max.png}
+  \caption{Predictive positive and negative factors with elimination of false positives}
   \label{pred_max}
@@
 
-Figure \ref{pred_neg_max} shows the predictive negative factor with this method. We can see that this factor is similar at the factor for the initial methods. It could be worst, but it's not the case.
+Figure \ref{pred_max} shows the predictive factors with this method.
+For the positive one, we can see that all the method reach 1 at 30\% of damage.
+That is what you wanted to obtain with the elimination of the false positives.
+For the negative one, we can see that this factor is similar at the factor for the initial methods.
 
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.4\textwidth]{images/pred_neg_max.png}
-  \caption{Predictive negative factor}
-  \label{pred_neg_max}
-\end{figure}
-
-We have here improved the methods, because we eliminate the false positives. The only requirement is to have a detection method.
+We have here improved the methods, because we eliminate the false positives.
+The only requirement is to have a detection method.
+We can notice that all the methods are perfect with damage extent higher than 30\%: in this case, the methods always have a correct localization.
 
@@
 
-In this paper, we presented the structure heatlh monitoring and a state of the art for this.
+In this paper, we presented the structure health monitoring and a state of the art for this.
 Then we detailed one of the methods, the FRF interpolation method, and some physical models.
-Last, we presented our simulation with a sping-mass system and our results with the implementation of the FRF interpolation method.
+Last, we presented our simulation and our results with the implementation of the FRF interpolation method, and analized them.
 
-%\appendices
-%\section{One appendix}
-%some text for the appendix.
+%nombre de capteurs, fréquences à considérer
+We have seen that the FRF interpolation method works, and we proposed a method for eliminate the false positives, and improve its performance.
+But we have seen that under 10\% of damage, this method doesn't detect damages all the time.
+To improve the method on that, a study of the considered frequencies could be usefull.
+Indeed, we have considered all the frequencies under the maximal frequency of the structure here.
+A selection of the frequencies could permit to detect damages under 10\% extent.
 
-% use section* for acknowledgement
-%\section*{Acknowledgment}
-%The authors would like to thank...
+Another way to study is the impact of the number of sensors on the efficiency of the method.
+Here, we were placed in the ideal case where there is a sensor on each mass.
+For practice cases, the efficiency of the method with less sensors (for example, one sensor for two masses) should be studied.
 
-%\begin{thebibliography}{1}
-%
-%\bibitem{IEEEhowto:kopka}
-%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-%
-%\end{thebibliography}
-
-\nocite{*}
+%\nocite{*}
 \printbibliography

### 2017-04-18 code_solo/display_frf.py

@@ -20,10 +20,10 @@ import random
 ################################################
 
 
-CAPTVALUE = 5
+CAPTVALUE = 20
 SAMPLVALUE = 10000
-DAMAGED_SENSOR = []#must be a list
-DAMAGE = 0# % of damage
+DAMAGED_SENSOR = [7]#must be a list
+DAMAGE = 10# % of damage
 
 pos = [ k for k in range(CAPTVALUE) ]
 z = [ 0 for k in range(CAPTVALUE) ]
@@ -239,15 +239,17 @@ def frf_multiple_sensors(typ,acc):
 ###########################     Display   #################################################
 ###########################################################################################
 
-def printPerSensor(res):
+def printPerSensor(res,res2):
     n = len(res)
     for i in range(n):
-        plt.plot(np.absolute(res[i]))
-        plt.xlabel("Frequencies (Hz)")
-        plt.ylabel("FRF")
-        plt.title("Sensor " + str(i))
-        plt.legend()
-        plt.show()
+    	if i > 22:
+		    plt.plot(np.absolute(res[i]),label="Undamaged")
+		    plt.plot(np.absolute(res2[i]), label="Damaged")
+		    plt.xlabel("Frequencies (Hz)")
+		    plt.ylabel("FRF")
+		    plt.title("Frequency " + str(i))
+		    plt.legend()
+		    plt.show()
 
 
 
@@ -258,7 +260,8 @@ def printPerSensor(res):
 def experience():
 	_, _, acc = simulation(0, [ [0 for k in range(2*n) ] ])
 	frf, acc = frf_multiple_sensors(1, acc)
-	printPerSensor(np.transpose(frf))
+	damaged, acc = frf_multiple_sensors(2, acc)
+	printPerSensor(frf,damaged)
 
 
 

### 2017-04-19 rapport/paper.tex
corrected paper

@@
 
-It is of interest to detect damage in infrastructure as quickly as possible whether
- for the potential life-safety or economic impact.
-Such detection requires industries to perform some form of SHM.
+Detecting damage in infrastructure as quickly as possible is needed
+ for potential life-safety or economic impact.
+Such detection requires industries to perform some form of automated SHM.
 
@@
 Traditional methods of damage detection based on visual inspections or experimental techniques such as radiography
- or ultrasound allow to obtain detailed information about a local damage state but requires to know the area where it is located (and hope for easy access).
-These techniques may be costly, taking a long time to be performed and impractical to detect damage in large urban areas.
- Furthermore, they may fail if damage is not visibly evident. This is why other global methods automated
- and based on sensor measurements were developed.
+ or ultrasound allow to obtain detailed information about a local damage state but requires to know the area where it is located (and the hope of an easy access).
+These techniques may be costly, take a long time to be performed and are impractical to detect damage in large urban areas.
+ Furthermore, they may fail if damage is not visible because it is not yet critical. This is why other global automated methods
+ and based on sensor were developed.
 
@@
 Here, a FE model isn't necessary, only recorded data are analyzed.
- In these methods, the damage parameter $D$ is the variation of a damage feature $d$ between the inspection $I$ and the reference $R$ configurations: %Damage-sensitive features are extracted from data and their changes used to identify damage in the structures so the damage parameter D in these method is the variation of the damage feature f between the inspection I and the reference R configurations.
+ In these methods, the damage parameter $D$ is the variation of a damage $d$ between the inspection $I$ and the reference $R$: %Damage-sensitive features are extracted from data and their changes used to identify damage in the structures so the damage parameter D in these method is the variation of the damage feature f between the inspection I and the reference R configurations.
 % référence TOWARDS EXTRACTION OF VIBRATION-BASED DAMAGE INDICATORS
@@
 We can see there is a loss of regularity at the position 7 for the damaged state.
-We can also see there is an iregularity at the position 2, but here the two states have the same iregularity, so it's not a loss of regularity compared to the reference state.
+We can also see there is an irregularity at the position 2, but here the two states have the same irregularity, so it's not a loss of regularity compared to the reference state.
 
@@
 There is a separate cubic polynomial interpolation for each interval, each with its own coefficients.
-This is for this local aspect that we use this interpolation (other interpolations can also be used), since we want to detect local iregularities.
+This is for this local aspect that we use this interpolation (other interpolations can also be used), since we want to detect local irregularities.
 Cubic polynomial spline interpolations produce an interpolated function that is continuous through to the second derivative.
@@
 Thus, we can have different values of the error interpolation for a same state.
-The distributions of the erros for a state is close to a gaussian distribution.
+The distributions of the errors for a state is close to a Gaussian distribution.
 The problem is that the distributions for an undamaged and a damaged states can be near.
@@
 
-Now, to denote corect detection (or no detection), we will use the terms true positives and negatives, to denote missing alarms we will use false negatives and for false alarms, we will use false positives.
+Now, to denote correct detection, we will use the terms true positives and negatives, to denote missed alarms we will use false negatives and for false alarms, we will use false positives.
 
@@
 
-Figure \ref{theodiff} shows the difference betweem the two FRF, and we can see the loss of spatial regularity (damage at position 7).
-In comparison with the Figure \ref{theo}, we can see here there is only one iregularity: the fact to compute the difference before the interpolation erase iregularity when they are in the two states.
+Figure \ref{theodiff} shows the difference between the two FRF, and we can see the loss of spatial regularity (damage at position 7).
+In comparison with the Figure \ref{theo}, we can see here there is only one irregularity: the fact to compute the difference before the interpolation erase irregularity when they are in the two states.
 With the initial method, they are also erase when we compute the difference between the interpolation errors.
@@
   \includegraphics[width=0.3\textwidth]{images/theodiff60.png}
-  \caption{Difference betweem theoretical FRF of undamaged and damage states}
+  \caption{Difference between theoretical FRF of undamaged and damage states}
   \label{theodiff}
@@
 \item Compute the difference between the FRF of reference and the FRF of the studied state, for each frequency
-\item Compute the interpolation error of these differencies
+\item Compute the interpolation error of these differences
 \item Compute the sum of the interpolation errors at each frequency
@@
 
-Figure \ref{frf_sensors} presents results of the FRF for all the sensors at one frenquency.
-Curves aren't as regular as the theoretical FRF, but we can see clearly the iregularity between sensors 6 and 7 (there is 10\% of damage here).
+Figure \ref{frf_sensors} presents results of the FRF for all the sensors at one frequency.
+Curves aren't as regular as the theoretical FRF, but we can see clearly the irregularity between sensors 6 and 7 (there is 10\% of damage here).
 
@@
 
-With the noise, we can so do two observations: first, the FRF interpolation method has a better localization for small damages than the FRF difference method, second,  the FRF difference method has a better false positives rate than the FRF interpolation method.
+With the noise, we can do two observations: first, the FRF interpolation method has a better localization for small damages than the FRF difference method, second,  the FRF difference method has a better false positives rate than the FRF interpolation method.
 
@@
 
-Figure \ref{beam_error} shows the computed error. We can see that there are only two sensors with a positiv error, which are the sensors 4 and 5. Thus, the localization is good.
+Figure \ref{beam_error} shows the computed error. We can see that there are only two sensors with a positive error, which are the sensors 4 and 5. Thus, the localization is good.
 
@@
 Then we detailed one of the methods, the FRF interpolation method, and some physical models.
-Last, we presented our simulation and our results with the implementation of the FRF interpolation method, and analized them.
+Last, we presented our simulation and our results with the implementation of the FRF interpolation method, and analyzed them.
 
@@
 But we have seen that under 10\% of damage, this method doesn't detect damages all the time.
-To improve the method on that, a study of the considered frequencies could be usefull.
+To improve the method on that, a study of the considered frequencies could be useful.
 Indeed, we have considered all the frequencies under the maximal frequency of the structure here.

### 2017-04-24 rapport/paper.tex
MAJ paper

@@
  namely the FRF interpolation method \cite{dilena2015damage}.
-Our contribution is the development of a simulator to obtain acceleration measurement of different structures, a proposition of a variant of the FRF interpolation method, and a statistical analysis of the two methods.
+%Our contribution is the development of a simulator to obtain acceleration measurement of different structures, a proposition of a variant of the FRF interpolation method, and a statistical analysis of the two methods.
+Our contribution is a statistical evaluation of the method. This led to a proposition of a variant of the FRF interpolation method, and both methods were analyzed in extensive simulations.
 
@@
 \cite{limongelli2016towards}.
-Here, a FE model isn't necessary, only recorded data are analyzed.
+Here, a FE model is not necessary, only recorded data are analyzed.
  In these methods, the damage parameter $D$ is the variation of a damage $d$ between the inspection $I$ and the reference $R$: %Damage-sensitive features are extracted from data and their changes used to identify damage in the structures so the damage parameter D in these method is the variation of the damage feature f between the inspection I and the reference R configurations.
@@
 The FRF is evaluated at $s = i \omega$, with $\omega$ the pulsation.
-In practice, we want to calculate the FRF of the system, for each sensor localization.
+In practice, we want to calculate the FRF of the system, for each sensor location.
 The FRF is calculated for each sensor location and each frequency $\omega_j = \frac{2\pi}{\Delta t} \frac{j}{N}$.
@@
 We can see there is a loss of regularity at the position 7 for the damaged state.
-We can also see there is an irregularity at the position 2, but here the two states have the same irregularity, so it's not a loss of regularity compared to the reference state.
+We can also see there is an irregularity at the position 2, but here the two states have the same irregularity, so it is not a loss of regularity compared to the reference state.
 
@@
 For each sensor, we calculate the Frequency Response Function (FRF) from the acceleration's measures, at certain frequencies
-(which are $\frac{k}{N}, k \in \{0 ... N-1\}$ with $N$ the size of the input and output vectors).
+(which are $\frac{j}{N}, j \in \{0 ... N-1\}$ with $N$ the length of the input and output vectors).
 
@@
 
-Then, we calculate for each sensor $z_l$ the cubic polynomial spline interpolation of the transfer functions $H_R(z_k,j)$ measured at all
+Then, we calculate for each sensor $z_l$ the cubic polynomial spline interpolation from the transfer functions $H_R(z_k,j)$ measured at all
 the other instrumented locations $\{z_k\}, k\in \{1 ... n\}, k \neq l$: we denote it $H_S(z_l,j)$.
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{images/interpolation.png}
-  \caption{Interpolation error}
+  \includegraphics[width=0.4\textwidth]{images/interpolation2.png}
+  \caption{Interpolation error E}
   \label{interpolation_error}
@@
 
-For a decision that an interpolation error belongs to the healthy or damaged state, once have to determine a threshold $E_T$, such as $ \Delta E(z_l)$ must be taller than $E_T$ to have a high probability of identification of a damage at location $z_l$.
-Indeed, as we can see in the Figure \ref{proba}, the curves which represent the fact to have a damage or not have a share area: if the interpolation error $ \Delta E(z_l)$ is in this area, one can commit two errors:
+For a decision that an interpolation error belongs to the healthy or damaged state, a threshold $E_T$ has to be determined, such as $ \Delta E(z_l)$ must be taller than $E_T$ to have a high probability of identification of a damage at location $z_l$.
+Indeed, as we can see in the Figure \ref{proba}, the curves which represent the fact to have a damage or not may share an area: if the interpolation error $ \Delta E(z_l)$ is in this area, one can commit two errors:
 \begin{itemize}
-\item if it is in the red area (FP), once can detect a damage since there isn't one (false alarm).
-\item if it is in the green area (FN), once can not detect a damage since there is one (missing alarm).
+\item if it is in the red area (FN), a damage is present but not detected (false alarm).
+\item if it is in the green area (FP), a damage is detected while there is actually no damage (missing alarm).
 \end{itemize}
@@
 
-In our experiences, we measure the number of true/false positives and negatives. The Figure \ref{TFPN} present the notations used for the number of true/false positives and negatives.
+In our experiments, we measure the number of true/false positives and negatives. The Figure \ref{TFPN} present the notations used for the number of true/false positives and negatives.
 
@@
 $\frac{TP}{TP + FP}$ and $\frac{TN}{TN + FN}$.
-The first correspond to the probability that there is a damage when we detect one, and the second correspond to the probability there isn't any damage when we detect nothing.
+The first correspond to the probability that there is a damage when we detect one, and the second correspond to the probability there is not any damage when we detect nothing.
 A good method has the two factors near to 1.
@@
 
-Now, we have the sampling period:
+Now, we have the sampling period $\Delta t$ which is given by:
 \begin{equation}
-\Delta t = 2 \times max_{j \in \{1 ... n\} } f_j
+\frac{1}{\Delta t} \geq 2 \times max_{j \in \{1 ... n\} } f_j
 \end{equation}
@@
 \begin{itemize}
-\item in dark blue: results of the FRF interpolation method with a threshold at 99\% of the reference errors
-\item in green: results of the FRF interpolation method with a threshold at 95\% of the reference distribution
-\item in red: results of the FRF difference method with a threshold at 99\% of the reference errors
-\item in blue : results of the FRF difference method with a threshold at 95\% of the reference distribution
+\item in blue (continuous line): results of the FRF interpolation method with a threshold at 99\% of the reference errors
+\item in blue (dashes): results of the FRF interpolation method with a threshold at 95\% of the reference distribution
+\item in red (continuous line): results of the FRF difference method with a threshold at 99\% of the reference errors
+\item in red (dashes): results of the FRF difference method with a threshold at 95\% of the reference distribution
 \end{itemize}
 
-To distinguish the two methods with the two thresholds, we denote them with the color initials: the first one DB, the second one G, the third one R and the last one B.
+To distinguish the two methods with the two thresholds, we denote them as follows: the first one I99, the second one I95, the third one D99 and the last one D95.
 
@@
 Figure \ref{detect} presents the percent of detection of a damage between sensors 6 and 7 against the damage extent (a single damage is always simulated on sensor 7).
-We can see here that below 5\% of damage, none of the methods detect the damage more than 50\% of the time, but we can see that B is the best: at 10\% of damage, it reach 90\% of detection, while the others are below 30\%.
-However, at 15\% of damage, it's DB and G which are the best, with 100\% of detection.
-B reaches 100\% of detection at 20\% of damage, and R reaches it at 30\% of damage.
-Here, R seems to be the worst.
+We can see here that below 5\% of damage, none of the methods detect the damage more than 50\% of the time, but we can see that D95 is the best: at 10\% of damage, it reach 90\% of detection, while the others are below 30\%.
+However, at 15\% of damage, it is I95 which is the best, with 99\% of detection.
+I99 and D95 reach 100\% of detection at 20\% of damage, and D99 reaches it at 30\% of damage.
+Here, D99 seems to be the worst.
 
@@
 Figure \ref{fp} presents the percent of false positives against the damage percent.
-Here, R is the best: around 2\% of false positives regardless of the percent of damage, while the others are between 5\% and 25\%.
+Here, D99 is the best: around 2\% of false positives regardless of the percent of damage, while the others are between 5\% and 25\%.
 
@@
 
-However, we can see on Figure \ref{detect_noise} that the rate of true positives is impacted by the noise: the G and BD methods reach 100\% of detection at 20\% of damage and the R and BL methods reach it at 40\% of damage.
+However, we can see on Figure \ref{detect_noise} that the rate of true positives is impacted by the noise: the I99 and I95 methods reach 100\% of detection at 20\% of damage and the D99 and D95 methods reach it at 40\% of damage.
 
@@
 
-For the false positives rate, we can notice that the R method is always the best, but the BL method is better than without noise.
+For the false positives rate, we can notice that the D99 method is always the best, but the D95 method is better than without noise.
 
@@
 Figure \ref{pred} shows the predictive positive and negative factors.
-For the positive one, we can see that the R method is the best.
+For the positive one, we can see that the D99 method is the best.
 For the negative one, we can see that all the method reach 1 at 30\% of damage, and are a factor higher than 0.9 for small damages.
@@
 
-We can see that the predictive negative factor isn't bad, but the positive one can be better.
+We can see that the predictive negative factor is not bad, but the positive one can be better.
 To improve it, we must have less false positives.
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{images/detect_max_10percent.png}
-  \caption{}
+  \includegraphics[width=0.4\textwidth]{images/detect_max_30percent.png}
+  \caption{Damage detection rate for a damage (30\%) between sensors 6 and 7, with elimination of false positives}
   \label{detect_max}
@@
 For the negative one, we can see that this factor is similar at the factor for the initial methods.
+Here, the method with the best results is the I95 method.
 
@@
   \includegraphics[width=0.4\textwidth]{images/poutre_curve2.png}
-  \caption{}
+  \caption{FRF for undamaged and damage states of the beam at one frequency, against sensors}
   \label{beam_curve}
@@
   \includegraphics[width=0.4\textwidth]{images/poutre_error.png}
-  \caption{}
+  \caption{Interpolation error with the beam}
   \label{beam_error}
@@
   \includegraphics[width=0.4\textwidth]{images/quantification.png}
-  \caption{}
+  \caption{Error (in percent of the threshold)}
   \label{quant}
@@
 
-In this paper, we presented the structure health monitoring and a state of the art for this.
-Then we detailed one of the methods, the FRF interpolation method, and some physical models.
+In this paper, we presented the structural health monitoring and a state of the art for this.
+Then we detailed one of the methods, the FRF interpolation method, and the underlying physical models.
 Last, we presented our simulation and our results with the implementation of the FRF interpolation method, and analyzed them.

### 2017-04-24 code_solo/data/detect.py

@@ -21,10 +21,10 @@ for e in error:
 	gauss_inv += [ t_gauss_inv[DAMAGED_SENSOR] ]
 
 
-plt.plot(error, maxi, label = 'Maxi')
-plt.plot(error, gauss, label = 'Gauss')
-plt.plot(error, maxi_inv, label = 'Maxi inv')
-plt.plot(error, gauss_inv, label = 'Gauss inv')
+plt.plot(error,maxi, "b", label = "I99")
+plt.plot(error,gauss, "b--", label = "I95")
+plt.plot(error,maxi_inv, "r", label = "D99")
+plt.plot(error,gauss_inv, "r--", label = "D95")
 plt.xlabel("Percent of damage")
 plt.ylabel("Percent of localization")
 plt.legend()

### 2017-04-24 code_solo/data/detect_noise.py

@@ -31,13 +31,13 @@ for e in error:
 	gauss_inv += [ tp(t_gauss_inv) ]
 
 
-plt.plot(error, maxi, label = 'Maxi')
-plt.plot(error, gauss, label = 'Gauss')
-plt.plot(error, maxi_inv, label = 'Maxi inv')
-plt.plot(error, gauss_inv, label = 'Gauss inv')
+plt.plot(error,maxi, "b", label = "I99")
+plt.plot(error,gauss, "b--", label = "I95")
+plt.plot(error,maxi_inv, "r", label = "D99")
+plt.plot(error,gauss_inv, "r--", label = "D95")
 plt.xlabel("Percent of damage")
 plt.ylabel("Percent of localization")
-plt.title("Noise: " + str(NOISE))
+#plt.title("Noise: " + str(NOISE))
 plt.legend()
 plt.show()
 

### 2017-04-24 code_solo/data/fp.py

@@ -32,10 +32,10 @@ for e in error:
 	gauss_inv += [ fp(t_gauss_inv) ]
 
 
-plt.plot(error, maxi, label = 'Maxi')
-plt.plot(error, gauss, label = 'Gauss')
-plt.plot(error, maxi_inv, label = 'Maxi inv')
-plt.plot(error, gauss_inv, label = 'Gauss inv')
+plt.plot(error,maxi, "b", label = "I99")
+plt.plot(error,gauss, "b--", label = "I95")
+plt.plot(error,maxi_inv, "r", label = "D99")
+plt.plot(error,gauss_inv, "r--", label = "D95")
 plt.xlabel("Percent of damage")
 plt.ylabel("Percent of false positif")
 plt.legend()

### 2017-04-24 code_solo/data/fp_noise.py

@@ -34,10 +34,10 @@ for e in error:
 	gauss_inv += [ fp(t_gauss_inv) ]
 
 
-plt.plot(error, maxi, label = 'Maxi')
-plt.plot(error, gauss, label = 'Gauss')
-plt.plot(error, maxi_inv, label = 'Maxi inv')
-plt.plot(error, gauss_inv, label = 'Gauss inv')
+plt.plot(error,maxi, "b", label = "I99")
+plt.plot(error,gauss, "b--", label = "I95")
+plt.plot(error,maxi_inv, "r", label = "D99")
+plt.plot(error,gauss_inv, "r--", label = "D95")
 plt.xlabel("Percent of damage")
 plt.ylabel("Percent of false positif")
 plt.legend()

### 2017-04-24 code_solo/data/quantification.py

@@ -25,12 +25,12 @@ for DAMAGE in damage:
 	q1_inv += [max(d1_inv[DAMAGED_SENSOR],d1_inv[DAMAGED_SENSOR-1])]
 	q2_inv += [max(d2_inv[DAMAGED_SENSOR],d2_inv[DAMAGED_SENSOR-1])]
 
-plt.plot(damage, q1, label = 'Maxi')
-plt.plot(damage, q2, label = 'Gauss')
-plt.plot(damage, q1_inv, label = 'Maxi inv')
-plt.plot(damage, q2_inv, label = 'Gauss inv')
+plt.plot(damage, q1, "b", label = "I99")
+plt.plot(damage, q2, "b--", label = "I95")
+plt.plot(damage, q1_inv, "r", label = "D99")
+plt.plot(damage, q2_inv, "r--", label = "D95")
 plt.xlabel("Percent of damage")
-plt.ylabel("difference")
+plt.ylabel("Error divided by the threshold")
 plt.title("Quantification")
 plt.legend()
 plt.show()

### 2017-04-24 code_solo/display_frf.py

@@ -245,7 +245,7 @@ def printPerSensor(res,res2):
     	if i > 22:
 		    plt.plot(np.absolute(res[i]),label="Undamaged")
 		    plt.plot(np.absolute(res2[i]), label="Damaged")
-		    plt.xlabel("Frequencies (Hz)")
+		    plt.xlabel("Sensors")
 		    plt.ylabel("FRF")
 		    plt.title("Frequency " + str(i))
 		    plt.legend()
